---
title: "Pollock life-history parameters for MYAS project"
author: "Hans Gerritsen, Katie Thomas"
date: "26 November 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
```

## MYDAS

The MYDAS project <https://github.com/laurieKell/mydas> requires realistic life-history parameters for each of the case-study stocks. By default these are obtained from <http://www.fishbase.org> but the quality of these parameters is difficult to judge. For Pollack the MI has a reasonable amount of data available from surveys, observer trips and port sampling. Age data are available for the landings data for 2016 and 2017 and for a number of surveys.

```{r, message=FALSE, warning=FALSE}
#First load the required libraries
library(ggplot2)
library(dplyr)
library(tidyr)

# and the data (see pollack data extraction.R)
load('pollack.RData')
```

## Length frequency of the landings
```{r}
len1 <- len %>% group_by(lenCm=lenCls/10) %>% summarise(lenNum=sum(lenNum))
ggplot(len1) + geom_point(aes(lenCm,lenNum))
```

The largest observed fish is `r max(len$lenCls/10)` cm. That can tell us something about Linf. If growth flattens off in the older fish, you would expect the largest fish to be a couple of standard deviations above Linf, so you wouldnt expect Linf to be less than, say 80cm.

Note that there are some fish below 30cm. It turns out that these are all from a single sample; could well be species mis-identification.

## Length-frequency by gear

```{r}
len1 <- subset(len,!SampleHeaderID%in%c(9487,9478)) %>% group_by(len=floor(lenCls/20)*2+1,gear) %>% summarise(lenNum=sum(lenNum))
len1 <- len1 %>% group_by(gear) %>% mutate(lenSum=sum(lenNum))
ggplot(subset(len1,gear!='OTH'),aes(len,lenNum/lenSum,col=gear)) + geom_point() + geom_line()
```

Most of the landings are from gillnets, other gears seem to catch relatively more fish below 50cm suggesting the gillnets may have a higher L50 for gear selectivity. (or they operate in areas where smaller fish are not available) There is no obvious difference in the selectivity of the larger fish (with gillnets you expect a dome-shaped selection). Perhaps otter trawls and seines catch a few more fish >70 relative to gillnets.

There is also the issue of availability; the younger fish simply do not seem to be available to the commercial fishery. Beam trawls seem to catch the smallest pollack.


## Biological data
We have aged fish from the landings in 2016-17, from the IAMS (anglerfish) surveys in 2016-17, a couple from IBES (beam trawl) 2016-17 and from IGFS (ibts) in 2016-17. Also some individual weights and maturity from other IGFS surveys.

```{r}
bio %>% group_by(dataType,dataSource) %>% summarise(
  total=length(age),aged=sum(age>0,na.rm=T),
  sex=sum(sex%in%c('F','M')),
  mat=sum(matStage>0),
  wt=sum(indWt>0))
```


##Growth

```{r}
#Before we fit growth curves, we need account for the time of year when the fish were caught; we don't treat the ages as integers but use the week in which they were caught to approximate the proportion of the year that has passed since their nominal birthday on 1 January.
bio$yearpart <- bio$week/52
```

Fitting a VBGF to the raw age data gives the parameters below. Note that there may be some bias due to length-stratified sampling.

```{r}
#(code from <http://derekogle.com/fishR/examples/oldFishRVignettes/VonBertalanffy.pdf>)
bio1 <- with(subset(bio,age>0),data.frame(tl=lenCls/10,age=age+yearpart,dataSource,year,sex))
svTypical <- list(Linf=100,K=0.3,t0=-1.8)
vbTypical <- tl~Linf*(1-exp(-K*(age-t0)))
fitTypical <- nls(vbTypical,data=bio1,start=svTypical)
par <- c(summary(fitTypical)$parameters[,'Estimate'])
par
```

These parameters are very close to those given by fishbase (Linf=85.6,k=0.19,t0=0) except for t0. The fishbase parameters do not fit very well, because of the difference in t0.

```{r}
ggplot(data=bio1) + geom_point(aes(age,tl)) +
  stat_function(fun = function(age) par[1]*(1-exp(-par[2]*(age-par[3]))),aes(col='fitted'),lwd=1.25) + 
  stat_function(fun = function(age) 85.6*(1-exp(-0.19*(age-0))),aes(col='fishbase'),lwd=1.25) +
  xlim(-1,15) + ylim(0,90)
```

Conclusion: do not use the fishbase parameters but those based on MI data: Linf = `r round(par[1],1)`; k = `r round(par[2],2)`; t = `r round(par[3],2)`

## Length-weight

```{r,eval=F}
#The length-weight data are pretty clean. The weights are converted to live weight in grams. Some very small fish need to be removed
ggplot(subset(bio,indWt>0)) + geom_point(aes(lenCls/10,indWt)) + coord_trans(x="log10", y="log10")
ggplot(subset(bio,indWt>100)) + geom_point(aes(lenCls/10,indWt)) + coord_trans(x="log10", y="log10")
```

```{r}
#Fit a linear model
lw <- with(subset(bio,indWt>100), lm(log(indWt)~log(lenCls/10)))
lw
a <- exp(lw$coefficients[1])
b <- lw$coefficients[2]
```

Compare MI data to fishbase

```{r}
fishbase <- data.frame(a=c(0.00413,0.00613,0.0076,0.01006,0.0107),
                       b=c(3.21,3.115,3,2.993,2.966),
                       area=c('Biscay','Channel','France','UK','N sea'))

with(subset(bio,indWt>100),plot(lenCls/10,indWt,cex=0.5))
lngt <- seq(0,100,by=0.1)
wt <- a*lngt^b
lines(lngt,wt,col=6,lwd=3)

for(i in 1:nrow(fishbase)){
  wt <- fishbase$a[i]*lngt^fishbase$b[i]
  lines(lngt,wt,lwd=1,col=i)
}
legend('topleft',legend=fishbase$area,lwd=1,col=1:5,title='Fishbase')
legend('top',legend='MI data',lwd=3,col=6)
```

The data from France in fishbase looks wrong; this may be gutted weight? The MI data seems as good as any of the others. 

Conclusion: the suggested final length-weight parameters are: a = `r round(a,4)`; b = `r round(b,2)`

## Maturity
There seems to be an increasing number of mature fish up to 60cm when all data is included

```{r}
bio$mature <- as.numeric(bio$matStage>2)
bio2 <- subset(bio,matStage%in%(1:8))  %>% group_by(len=round(lenCls/100)*10) %>% summarise(pm=sum(mature)/length(mature))
ggplot(bio2) + geom_point(aes(len,pm))
```

But it turns out that all the immature fish are from the Q4 surveys. At that time of year it is difficult to  distinguish virgin from recovered fish. The data from the start of the year (spawning time) suggests nearly 100% mature fish in the catches

```{r}
bio2 <- subset(bio,matStage%in%(1:8))  %>% group_by(len=round(lenCls/100)*10,Q1=week<20) %>% summarise(pm=sum(mature)/length(mature))
ggplot(bio2) + geom_point(aes(len,pm,col=Q1))
```

```{r,eval=F}
#Looking at maturity by age does not tell us anything useful
bio2 <- subset(bio,matStage%in%(1:8))  %>% group_by(age,Q1=week<20) %>% summarise(pm=sum(mature)/length(mature))
ggplot(bio2) + geom_point(aes(age,pm,col=Q1))
```

Conclusion: all fish caught in the spring surveys are mature; immature fish may not be available to the surveys. The assumed age of first maturity is 3. (Is this right Katie?)

## Total mortality and selectivity
If we apply the age length key data to the length frequency data we can get the numbers-at-age in the landings. We can then use this to see how quick they die from one age to the next. This is a rough measure of the total mortality (Z). If you substract the natural mortality from this, you get a ballpark figure of F.

```{r}
lan1 <- lan %>% group_by(Year,Age=AgeLength) %>% summarise(CatchNum=sum(NumberCaught))
g <- ggplot(lan1,aes(Age,log(CatchNum),col=factor(Year))) + geom_point()
lan2 <- lan %>% group_by(Age=AgeLength) %>% summarise(CatchNum=sum(NumberCaught)/2,MeanWt=mean(MeanWeight,na.rm=T))
zmod <- lm(log(CatchNum)~Age,data=subset(lan2,Age>4 & Age<10))
a <- zmod$coefficients[1]
b <- zmod$coefficients[2]
g + stat_function(fun = function(Age) a+Age*b,aes(col='Z')) 
```

The slope in the plot above is fitted over the average landings numbers at ages 5 to 9 in the two years. The slope is `r round(b,2)` which suggests that F might be in the ballbark of `r round(-b,2)-0.2`, which is pretty high; quite possibly above Fmsy

The other nice thing about estimating Z is that you can extrapolate Z over the younger ages to see how many you would expect if selectivity and Z were the same for all ages:

```{r}
lan2$pred <- predict(zmod,newdata=lan2)
ggplot(lan2,aes(Age,log(CatchNum)/pred)) + geom_point() + xlim(0,7) + ylim(0,1.3)
```

Conclusion: it looks like the age at 50% selectivity is somewhere between 2 and 3.

## Thompson-Bell yield-per recruit
You can do a rough yield per recruit using the approach by Thompson and Bell (1934). For now assuming M=0.2, kife-edge maturity at age 3 and selectivity as above.

```{r}
# age classes
age <- 2:10
# natural mortality
M <- 0.2 
# proportion mature
PM <- c(0,1,1,1,1,1,1,1,1)
# catch weight
cw <- lan2$MeanWt[match(age,lan2$Age)]
# selectivity
s <- (log(lan2$CatchNum)/lan2$pred)[match(age,lan2$Age)]
s[5:9] <- 1 # assume full selectivity for ages 6+


Y=NULL
SSB=NULL
fRange=seq(0,1,by=0.01)
for(f in fRange){
  Nt=1000 #starting popolation at t=1
  for(t in 2:9)
    Nt[t]=Nt[t-1]*exp(-s[t-1]*f-M)
  CN=Nt*(1-exp(-s*f-M))*s*f/(s*f+M)
  Y=c(Y,sum(CN*cw))
  SSB=c(SSB,sum(Nt*cw*PM))
}
plot(fRange,Y,type='l',xlab='F',ylab='Yield per Recruit',lwd=3,xlim=c(0,1.1))
lines(fRange,max(Y)*SSB/max(SSB),lty=2)
legend('topright',c('YPR','SSB'),lty=1:2,lwd=c(3,1),bg='white')

Fmax=fRange[Y==max(Y)]
arrows(Fmax,10,Fmax,max(Y),length=0.1)
text(Fmax,0,paste('Fmax=',Fmax,''))

slope=Y[2:length(fRange)]-Y[1:length(fRange[-1])]
slope0.1=0.1*slope[1]
F0.1=fRange[abs(slope-slope0.1)==min(abs(slope-slope0.1))]
Y0.1=Y[fRange==F0.1]
arrows(F0.1,10,F0.1,Y0.1,length=0.1)
text(F0.1,0,paste('F0.1=',F0.1,''))

```

F01 can be used as a proxy for Fmsy. The F=Z-0.2 estimate of `r round(-b,2)-0.2` is well above that. However F0.1 is quite conservative and F is below Fmax. The YPR is very flat-topped.


## Summary
Growth parameters: Linf = `r round(par[1],1)`; k = `r round(par[2],2)`; t = `r round(par[3],2)`

Length-weight parameters: a = `r round(exp(lw$coefficients[1]),4)`; b = `r round(lw$coefficients[2],2)`

Maturity: knife edge at age 3 (?)

Selectivity: A50 between ages 2 and 3

Z: `r round(-b,2)`

F01: `r F0.1`
