---
title: "Turbot life-history parameters for MYAS project"
author: "Hans Gerritsen"
date: "26 November 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
```

## MYDAS

The MYDAS project <https://github.com/laurieKell/mydas> requires realistic life-history parameters for each of the case-study stocks. By default these are obtained from <http://www.fishbase.org> but the quality of these parameters is difficult to judge. For Pollack the MI has a reasonable amount of data available from surveys, observer trips and port sampling. Age data are available for the landings data for 2016 and 2017 and for a number of surveys.

## Data extraction
First load the required libraries
```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)

# and the data (see turbot data extraction.R)
load('turbot.RData')
```


## Fishbase
```{r}
load(url("https://github.com//fishnets//fishnets//blob//master//data//fishbase-web//fishbase-web.RData?raw=True"))
lh=subset(fb,species=="Psetta maxima")
names(lh)[c(14:17)]=c("l50","l50min","l50max","a50")
lh=lh[,c("species","linf","k","t0","a","b","a50","l50","l50min","l50max","country","sex")]
lh[is.na(lh["l50"]),"l50"]=(lh[is.na(lh["l50"]),"l50min"]+lh[is.na(lh["l50"]),"l50max"])/2
lh=lh[,-(9:10)]
lh[lh$t0>=0,"t0"]=NA
apply(lh[,2:8],2,mean,na.rm=T)
```

## Growth
The MI have no age data for turbot. The fishbase data are quite variable but some of that can be explained by differences in growth between males and females. I wouldnt trust L50<60 for females, or L50<45 for males (we do get males at least as large as 60cm).

```{r,fig.height=7}
lh$label <- paste(lh$sex,lh$country)
lh$col <- rainbow(nrow(lh))
plot(NA,xlim=c(0,20),ylim=c(0,80),xlab='age',ylab='length')
for(i in 1:nrow(lh)){
  lines(seq(0,20,0.01),lh$linf[i]*(1-exp(-lh$k[i]*(seq(0,20,0.01)-lh$t0[i]))),col=as.numeric(lh$sex[i]),lty=i)
}
legend('bottomright',legend=lh$label,lty=1:nrow(lh),col=as.numeric(lh$sex),ncol=2)
```

What if we subset the data only for the north-east Atlantic:

```{r,fig.height=7}
lh1 <- subset(lh,country%in%c('France','Germany','UK','Netherlands'))
lh1$label <- paste(lh1$sex,lh1$country)
lh1$col <- rainbow(nrow(lh1))
plot(NA,xlim=c(0,20),ylim=c(0,80),xlab='age',ylab='length')
for(i in 1:nrow(lh1)){
  lines(seq(0,20,0.01),lh1$linf[i]*(1-exp(-lh1$k[i]*(seq(0,20,0.01)-lh1$t0[i]))),col=as.numeric(lh1$sex[i]),lty=i)
}
legend('bottomright',legend=lh1$label,lty=1:nrow(lh1),col=as.numeric(lh1$sex),ncol=2)
```

We still have male linf < 45 and female <60, lets remove those too:

```{r,fig.height=7}
lh1 <- subset(lh,country%in%c('France','Germany','UK','Netherlands'))
lh1a <- subset(lh1,sex=='F' & linf>60)
lh1b <- subset(lh1,sex=='M' & linf>45)
lh1 <- rbind(lh1a,lh1b)

lh1$label <- paste(lh1$sex,lh1$country)
lh1$col <- rainbow(nrow(lh1))
plot(NA,xlim=c(0,20),ylim=c(0,80),xlab='age',ylab='length')
for(i in 1:nrow(lh1)){
  lines(seq(0,20,0.01),lh1$linf[i]*(1-exp(-lh1$k[i]*(seq(0,20,0.01)-lh1$t0[i]))),col=as.numeric(lh1$sex[i]),lty=i)
}
lines(seq(0,20,0.01),mean(lh1[,2],na.rm=T)*(1-exp(-mean(lh1[,3],na.rm=T)*(seq(0,20,0.01)-mean(lh1[,4],na.rm=T)))),col=3,lwd=3)
legend('bottomright',legend=c(lh1$label,'Mean'),lty=c(1:nrow(lh1),1),col=c(as.numeric(lh1$sex),3),lwd=c(rep(1,nrow(lh1)),3),ncol=2)
```

This looks quite reasonable. The mean growth parameters of the remaining data are: Linf = `r round(mean(lh1[,2],na.rm=T),1)`, k = `r round(mean(lh1[,3],na.rm=T),2)` and t0 = `r round(mean(lh1[,4],na.rm=T),1)`.

If we want sex-specific growth parameters, the female means are:  Linf = `r round(mean(lh1a[,2],na.rm=T),1)`, k = `r round(mean(lh1a[,3],na.rm=T),2)` and t0 = `r round(mean(lh1a[,4],na.rm=T),1)`.

And the males:
 Linf = `r round(mean(lh1b[,2],na.rm=T),1)`, k = `r round(mean(lh1b[,3],na.rm=T),2)` and t0 = `r round(mean(lh1b[,4],na.rm=T),1)`.


## Length frequency of the landings
```{r}
len1 <- len %>% group_by(lenCls) %>% summarise(lenNum=sum(lenNum))
ggplot(len1) + geom_point(aes(lenCls,lenNum))
```

The largest fish is `r max(len$lenCls/10)` cm. That can tell us something about Linf. If growth levels off in the older fish, you would expect the largest fish to be a couple of standard deviations above Linf, so you wouldnt expect Linf to be less than, say 60cm.


## Biological data
The MI has no age data but quite a few observations of sex, maturity and individual weight:
```{r}
bio %>% group_by(dataType,dataSource) %>% summarise(
  total=length(age),aged=sum(age>0,na.rm=T),
  sex=sum(sex%in%c('F','M')),
  mat=sum(matStage>0),
  wt=sum(indWt>0))
```

## Growth by sex
We have no age data but might be worth looking at sex to see if they grow/die at different rates

```{r}
bio2 <- subset(bio,sex%in%c('F','M'))  %>% group_by(len=round(lenCls/50)*50) %>% summarise(sr=sum(sex=='F')/length(sex))
ggplot(bio2) + geom_point(aes(len,sr)) + ylim(0,1)
```

Yes. All large turbot are females, that means that either the males die before they get big or that they grow slower or stop growing sooner.

## Length-weight
```{r, eval=F}
#The length-weight data need a bit of tyding. The weights are converted to live weight in grams.
ggplot(subset(bio,indWt>0)) + geom_point(aes(lenCls/10,indWt)) + coord_trans(x="log10", y="log10")
```

Fit a linear model
```{r}
lw <- with(subset(bio,indWt>50 & lenCls<710), lm(log(indWt)~log(lenCls/10)))
lw
a <- exp(lw$coefficients[1])
b <- lw$coefficients[2]
```

Compare this to fishbase

```{r,fig.height=7}
fishbase <- subset(lh,a>0 & b>0)

with(subset(bio,indWt>50),plot(lenCls/10,indWt,cex=0.5))
lngt <- seq(0,100,by=0.1)
wt <- a*lngt^b
lines(lngt,wt,col=6,lwd=3)

for(i in 1:2){
  wt <- fishbase$a[i]*lngt^fishbase$b[i]
  lines(lngt,wt,lwd=1,col=i)
}
legend('topleft',legend=paste(fishbase$country,fishbase$sex)[1:2],lwd=1,col=1:2,title='Fishbase')
legend('top',legend='MI data',lwd=3,col=6)
```

French data dont look so good. Lets just use the MI data.

Conclusion: the suggested final length-weight parameters are: a = `r round(a,5)`; b = `r round(b,2)`

## Maturity
All data

```{r}
bio$mature <- as.numeric(as.numeric(as.character(bio$matStage))>2)
bio2 <- subset(bio,as.numeric(as.character(matStage))%in%(1:8))  %>% group_by(len=round(lenCls/100)*10,sex) %>% summarise(pm=sum(mature)/length(mature))
ggplot(bio2,aes(len,pm,col=sex)) + geom_point() + geom_line()
```

You get different results in spring, compared to Q4, it is probably only possible to tell the difference between virgin and spent in spring. But not much data. Best guess: L50 around 30cm. Maybe best just to use fishbase

```{r}
bio$mature <- as.numeric(as.numeric(as.character(bio$matStage))>2)
bio2 <- subset(bio,as.numeric(as.character(matStage))%in%(1:8))  %>% group_by(len=round(lenCls/100)*10,Q1=week<20) %>% summarise(pm=sum(mature)/length(mature),count=length(mature))
subset(bio2,Q1)
ggplot(bio2,aes(len,pm,col=Q1)) + geom_point() + geom_line()
```


## Summary
Growth parameters: Average from fishbase seems reasonable after removing outliers and data from Med and Baltic but note difference between male and female.

Both sexes: Linf = `r round(mean(lh1[,2],na.rm=T),1)`, k = `r round(mean(lh1[,3],na.rm=T),2)` and t0 = `r round(mean(lh1[,4],na.rm=T),1)`.

Female only:  Linf = `r round(mean(lh1a[,2],na.rm=T),1)`, k = `r round(mean(lh1a[,3],na.rm=T),2)` and t0 = `r round(mean(lh1a[,4],na.rm=T),1)`.

Male only: Linf = `r round(mean(lh1b[,2],na.rm=T),1)`, k = `r round(mean(lh1b[,3],na.rm=T),2)` and t0 = `r round(mean(lh1b[,4],na.rm=T),1)`.


Length-weight parameters: a = `r round(exp(lw$coefficients[1]),5)`; b = `r round(lw$coefficients[2],2)`

Maturity: 30cm? Fishbase is probably better.


