---
title: "Advice Rule"
subtitle: "XSA MP"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{FLife}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
github_document:
    mathjax: TRUE
tags: FLife
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(cache     =TRUE,
               cache.path="../cache/mse/mp-xsa",
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=10,
               fig.width =8,
               fig.path  ="../tex/mp-xsa-")

options(digits=3)

iFig=0
```
```{r pkgs}
library(ggplot2)
library(reshape)
library(plyr)
library(dplyr)
library(FLCore)
library(ggplotFL)

library(FLAssess)
library(FLXSA)
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat=file.path(dirMy,"data")

xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =1.0, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =10, 
                         tspower= 0,
                         vpa    =FALSE)

xsa=function(om,pg=10,ctrl=xsaControl){
  stk=setPlusGroup(om,pg)
  idx=FLIndex(index=stock.n(stk))
  range(idx)[c("plusgroup","startf","endf")]=c(pg,0.1,.2)
  
  xsa=stk+FLXSA(stk,idx,control=ctrl,diag.flag=FALSE)
  
  xsa}

xsaCtrl=list()
```

```{r, xsa-brill}
load(file.path(dirDat,"brill.RData"))

range(om)[c("minfbar","maxfbar")]=ceiling(mean(lh["a1"]))

xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =0.3, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =10, 
                         tspower= 3,
                         vpa    =FALSE)

om=window(iter(om,1:20),start=25,end=70)
mp=xsa(om,ctrl=xsaControl)

plot(FLStocks(list("xsa"=mp,"om"=om)))

xsaCtrl["brill"]=xsaControl
save(xsaCtrl,file=file.path(dirDat,"xsaCtrl"),compress="xz")
```

**Figure `r iFig=iFig+1; iFig`.** Cross test for brill.


```{r, xsa-turbot}
load(file.path(dirDat,"turbot.RData"))

range(om)[c("minfbar","maxfbar")]=ceiling(mean(lh["a1"]))

xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =0.3, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =10, 
                         tspower= 3,
                         vpa    =FALSE)

om=window(iter(om,1:20),start=25,end=70)
mp=xsa(om,ctrl=xsaControl)

plot(FLStocks(list("xsa"=mp,"om"=om)))

xsaCtrl["turbot"]=xsaControl
save(xsaCtrl,file=file.path(dirDat,"xsaCtrl"),compress="xz")
```

**Figure `r iFig=iFig+1; iFig`.** Cross test for turbot.


```{r, xsa-ray}
load(file.path(dirDat,"ray.RData"))

range(om)[c("minfbar","maxfbar")]=ceiling(mean(lh["a1"]))

xsaControl=FLXSA.control(tol    =1e-09, maxit   =250, 
                         min.nse=0.3,   fse     =1.0, 
                         rage   =3,     qage    =10, 
                         shk.n  =!TRUE,  shk.f   =TRUE, 
                         shk.yrs=4,     shk.ages=5, 
                         window =6,     tsrange =5, 
                         tspower=3,
                         vpa    =FALSE)

om=window(om,start=25,end=73)
mp=xsa(iter(om,1:10),ctrl=xsaControl,pg=20)

plot(FLStocks(list("xsa"=mp,"om"=om)))

xsaCtrl["ray"]=xsaControl
save(xsaCtrl,file=file.path(dirDat,"xsaCtrl"),compress="xz")
```

**Figure `r iFig=iFig+1; iFig`.** Cross test for ray.


```{r, xsa-pollack}
load(file.path(dirDat,"pollack.RData"))

range(om)[c("minfbar","maxfbar")]=ceiling(mean(lh["a1"]))

xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =0.3, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =6,     tsrange =5, 
                         tspower= 3,
                         vpa    =FALSE)

om=window(iter(om,1:20),start=25,end=70)
mp=xsa(iter(om,1:20),ctrl=xsaControl)

plot(FLStocks(list("xsa"=mp,"om"=om)))

xsaCtrl["pollack"]=xsaControl
save(xsaCtrl,file=file.path(dirDat,"xsaCtrl"),compress="xz")
```

**Figure `r iFig=iFig+1; iFig`.** Cross test for pollack.


```{r, xsa-sprat}
load(file.path(dirDat,"sprat.RData"))

range(om)[c("minfbar","maxfbar")]=ceiling(mean(lh["a1"]))

xsaControl=FLXSA.control(tol    =1e-09, maxit   =50, 
                         min.nse=0.3,   fse     =0.3, 
                         rage   =0,     qage    =8, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=5,     shk.ages=5, 
                         window =10,    tsrange =5, 
                         tspower= 0,
                         vpa    =FALSE)

om=window(iter(om,1:20),start=25,end=70)
mp=xsa(iter(om,1:20),ctrl=xsaControl)

plot(FLStocks(list("xsa"=mp,"om"=om)))

xsaCtrl["sprat"]=xsaControl
save(xsaCtrl,file=file.path(dirDat,"xsaCtrl"),compress="xz")
```

**Figure `r iFig=iFig+1; iFig`.** Cross test for sprat.


```{r, xsa-lobster}
load(file.path(dirDat,"lobster.RData"))

range(om)[c("minfbar","maxfbar")]=ceiling(mean(lh["a1"]))

xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =0.5, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =5, 
                         tspower= 3,
                         vpa    =FALSE)

om=window(iter(om,1:20),start=25,end=70)
mp=xsa(iter(om,1:20),ctrl=xsaControl)

plot(FLStocks(list("xsa"=mp,"om"=om)))

xsaCtrl["lobster"]=xsaControl
save(xsaCtrl,file=file.path(dirDat,"xsaCtrl"),compress="xz")
```

**Figure `r iFig=iFig+1; iFig`.** Cross test for lobster.


```{r, xsa-razors}
load(file.path(dirDat,"razor.RData"))

range(om)[c("minfbar","maxfbar")]=ceiling(mean(lh["a1"]))

xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =0.5, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =5, 
                         tspower= 3,
                         vpa    =FALSE)

om=window(iter(om,1:20),start=25,end=70)
mp=xsa(iter(om,1:20),ctrl=xsaControl)

plot(FLStocks(list("xsa"=mp,"om"=om)))

xsaCtrl["razors"]=xsaControl
save(xsaCtrl,file=file.path(dirDat,"xsaCtrl"),compress="xz")
```

**Figure `r iFig=iFig+1; iFig`.** Cross test for razor.

```{r, xsa-fwd,eval=FALSE}
registerDoParallel(4)

load(file.path(dirDat,"turbot.RData"))
om=window(om,start=25)

xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =1.0, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =10, 
                         tspower= 0,
                         vpa    =FALSE)

xsafwd=foreach(assYr=seq(75,40,-5), 
              .combine=list,
              .multicombine=TRUE,
              .packages=c("FLCore","FLAssess","FLXSA","FLasher","FLBRP","plyr")) %dopar%{

    mp =xsa(window(om,end=assYr,ctrl=xsaControl))
    sr =fmle(as.FLSR(mp,model="bevholt"),control=list(trace=FALSE))
    mp =fwdWindow(mp,end=assYr+10,FLBRP(mp))
          
    fwd(mp,catch=catch(om)[,assYr+0:10],sr=sr)
    }

xsafwd=as(xsafwd,"FLStocks")

theme_set(theme_bw())

names(xsafwd)=seq(75,40,-5)
plot(xsafwd)+
  guides(col=guide_legend(title="Assessment\n Year"))
```

**Figure `r iFig=iFig+1; iFig`.** Retrospective cross test


```{r,eval=FALSE}
theme_set(theme_bw())

plot(iter(xsafwd,67))+
  guides(col=guide_legend(title="Assessment\n Year"))
```

**Figure `r iFig=iFig+1; iFig`.** Single retrospective cross test


\newpage
## Session Info

```{r}
sessionInfo()
```

## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLife:  `r packageVersion('FLife')`
* FLBRP:  `r packageVersion('FLBRP')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}