---
title: "FLife"
subtitle: "Figs"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---


```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="../tex/figs",
               cache.path="../cache")

iFig=0
iTab=0
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat=file.path(dirMy,"data")
```


```{r, pkgs}
library(ggplot2)
library(plyr)
library(dplyr)
library(reshape)
library(GGally)

library(FLCore)
library(FLBRP)
library(FLasher)
library(ggplotFL)
library(FLife)

theme_set(theme_bw(base_size=20))
```

```{r}
source('/home/laurence/Desktop/sea++/mydas/project/R/fbSmry.R')

my_smooth <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_point(...,size=.5)+
    geom_smooth(...,method="lm",se=FALSE)}

my_density <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_density(...,lwd=1)}

```

```{r om-data}
source('/home/laurence/Desktop/sea++/mydas/project/R/fbSmry.R')

load(url("https://github.com//fishnets//fishnets//blob//master//data//fishbase-web//fishbase-web.RData?raw=True"))

spp=read.csv("/home/laurence/Desktop/sea++/mydas/project/R/shiny/data/Fishdata.csv")
spp=spp[!duplicated(spp[,"Binomial"]),]

spp=subset(spp,spp$Environment%in%names(table(spp$Environment)[c(3,4,6,7,8)]))$Binomial

grps=ac(unique(read.csv("/home/laurence/Desktop/sea++/mydas/project/R/shiny/data/Fishdata.csv")[,5]))
grps=subset(fb,species%in%spp)
grps=fbSmry(grps)

all=fbSmry(fb)
dat=model.frame(all[[1]][,"mean"])
dat=dat[!is.na(dat$l50),]

dat$species=ac(dat$iter)
dat=merge(dat,fb[!duplicated(fb$species),c("species","habit")])
dat=dat[dat$habit%in%names(table(dat$habit))[c(3:4,6:8)],]
dat$habit=as.factor(ac(dat$habit))

dat=dat[!is.na(dat$l50)|!is.na(dat$linf)|!is.na(dat$k),]

dat=transform(dat,winf=log(a*linf^b),
                  linf=log(linf),
                  k   =log(k),
                  l50 =log(l50))

gis=read.csv("/home/laurence/Desktop/sea++/mydas/project/papers/FLife/inputs/gislason-et-al-2010.csv",sep="\t")
```

```{r fb}
ggpairs(dat[,c(2,3,4,12,8,11)],mapping = ggplot2::aes(col=habit), 
        upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
        lower = list(continuous = wrap(my_smooth)),
        diag=list(continuous=wrap(my_density,alpha=0.5)),
        title = "")+
  theme(legend.position ="none",
        panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        axis.text.x      =element_text(angle=90),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Life history relationships from Fishbase.

```{r m, fig.height=6,fig.width=6}
names(gis)[5:6]=c("Temperature","Length")
ggpairs(log(gis[,c(2,6,7:8,5)]),   
        upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
        lower = list(continuous = wrap(my_smooth)),
        diag=list(continuous=wrap(my_density,alpha=0.5)),
        title = "")+
  theme(legend.position ="none",
        panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        axis.text.x      =element_text(angle=90),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** M from Gislason.

\newpage
## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLasher:   `r packageVersion('FLasher')`
* FLife:     `r packageVersion('FLife')`
* ggplotFL:  `r packageVersion('ggplotFL')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
```

