---
title: "Pareto Multi-objective Trade-offs"
subtitle: "Turbot VoI"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="../tex/scenarios-",
               cache.path="cache/scenarios/")

iFig=0
iTab=0
```
```{r, dir}  
dirOM ="/home/laurence/Desktop/sea++/mydas/project/tasks/task4/data"
dirRes="/home/laurence/Desktop/sea++/mydas/project/papers/pareto/data"
```

```{r, pkgs}
library(ggplot2)
library(plyr)
library(dplyr)
library(reshape)

library(FLCore)
library(FLBRP)
library(FLasher)
library(ggplotFL)
library(FLife)
library(randtests)

library(mydas)
```
```{r}
library(doParallel)
library(foreach)

cl=makeCluster(3)
registerDoParallel(cl)
```

```{r, OMscen}
nits=500

scen=expand.grid(nyr    =c(3,5,7)[2],
                 cv     =c(0.1,0.2,0.3)[2],
                 spp    ="turbot",
                 ctrl   =1:9,
                 stringsAsFactors=FALSE)

mseStart=c("brill"=54,"turbot"=54,"ray"=60,"pollack"=56,
           "sprat"=52,"razor"=54, "lobster"=57)

### Random variaton for control
controls=list()
set.seed(123456)
for (j in 1:12){
    controls[[j]]=rbind(FLPar(k1   =runif(nits, 0.0, 1.5)),
                        FLPar(k2   =runif(nits, 0.0, 1.5)),
                        FLPar(gamma=rep(1, nits)))}
controls=FLPars(controls)

set.seed(1233)
srDev=FLife:::rlnoise(nits,FLQuant(0,dimnames=list(year=1:105)),.3,b=0.0)
```

```{r, pm, eval=FALSE}
## Get summary stats
source('~/Desktop/sea++/mydas/pkg/R/smryStat.R')
source('~/Desktop/sea++/mydas/pkg/R/omOut.R')

```{r, figScatter1}
load(file.path(dirRes,"scenarios-turbot-pareto.RData"))
load(file.path(dirRes,"scenarios-turbot-pm.RData"))
```

```{r}
ggplot(pm)+
    geom_point(aes(safety,yield,col=yieldAav),size=1)+
    geom_point(aes(safety,yield),data=pareto,fill="red",col="darkred",shape=23)+
    theme_bw()+theme(legend.position="bottom")+
    xlab("Safety")+ylab(expression(Yield:MSY))+
    guides(col=guide_legend(title="AAV in Yield",size=2))+facet_grid(nyr~cv)
```
**Figure `r iFig=iFig+1; iFig`.** 

```{r}
ggplot(pm)+
    geom_point(aes(kobe,yield,col=yieldAav),size=1)+
    geom_point(aes(kobe,yield),data=pareto,fill="red",col="darkred",shape=23)+
    theme_bw()+theme(legend.position="bottom")+
    xlab("Kobe")+ylab(expression(Yield:MSY))+
    guides(col=guide_legend(title="AAV in Yield",size=2))+facet_grid(nyr~cv)
```
**Figure `r iFig=iFig+1; iFig`.** 

```{r}
ggplot(pm)+
    geom_point(aes(blim,yield,col=yieldAav),size=1)+
    geom_point(aes(blim,yield),data=pareto,fill="red",col="darkred",shape=23)+
    theme_bw()+theme(legend.position="bottom")+
    xlab(expression(B[lim]))+ylab(expression(Yield:MSY))+
    guides(col=guide_legend(title="AAV in Yield",size=2))+
    facet_grid(nyr~cv)
```
**Figure `r iFig=iFig+1; iFig`.** 


```{r}
ks=ddply(subset(pareto,blim>0.2&blim<0.2001),.(nyr,cv), with,
     data.frame(k1=mean(k1),k2=mean(k2),
                safety=mean(safety),kobe=mean(kobe),blim=mean(blim),
                yield=mean(yield),yieldAav=mean(yieldAav)))
round(ks,3)
save(ks,file=file.path(dirRes,"ks.RData"))
```



```{r, figBlim, fig.height=6}
ggplot(melt(pareto[,c("k1","k2","nyr","cv","safety")],id=c("nyr","cv","safety")))+
  geom_point(aes(value,safety,col=variable))+
  theme_bw()+theme(legend.position="bottom")+
  ylab("Safety")+xlab("Control Value")+
  guides(col=guide_legend(title="Control",size=2))+
  scale_colour_manual(values=c("red","black"))+    
  facet_grid(nyr~cv)
```

**Figure `r iFig=iFig+1; iFig`.** 

```{r, figKobe, fig.height=6}
ggplot(melt(pareto[,c("k1","k2","nyr","cv","kobe")],id=c("nyr","cv","kobe")))+
  geom_point(aes(value,kobe,col=variable))+
  theme_bw()+theme(legend.position="bottom")+
  ylab("Kobe")+xlab("Control Value")+
  guides(col=guide_legend(title="Control",size=2))+
  scale_colour_manual(values=c("red","black"))+    
  facet_grid(nyr~cv)
```

**Figure `r iFig=iFig+1; iFig`.** 

```{r, figYield, fig.height=6}
ggplot(melt(pareto[,c("k1","k2","nyr","cv","yield")],id=c("nyr","cv","yield")))+
  geom_point(aes(value,yield,col=variable))+
  theme_bw()+theme(legend.position="bottom")+
  ylab(expression(Yield:MSY))+xlab("Control Value")+
  guides(col=guide_legend(title="Control",size=2))+
  scale_colour_manual(values=c("red","black"))+    
  facet_grid(nyr~cv)
```

**Figure `r iFig=iFig+1; iFig`.** 

```{r, figYieldAav, fig.height=6}
ggplot(melt(pareto[,c("k1","k2","nyr","cv","yieldAav")],id=c("nyr","cv","yieldAav")))+
  geom_point(aes(value,1-yieldAav,col=variable))+
  theme_bw()+theme(legend.position="bottom")+
  ylab("AAV in Yield")+xlab("Control Value")+
  guides(col=guide_legend(title="Control",size=2))+
  scale_colour_manual(values=c("red","black"))+    
  facet_grid(nyr~cv)
```

**Figure `r iFig=iFig+1; iFig`.** 


```{r, mse, eval=FALSE}
## Run MSE
load(file.path(dirRes,"ks.RData"))

set.seed(1233)
srDev=FLife:::rlnoise(nits,FLQuant(0,dimnames=list(year=1:105)),.3,b=0.0)
              
scenD<-foreach(i=seq(dim(ks)[1]), 
              .combine=rbind,
              .multicombine=TRUE,
              .export=c("dirRes","dirOM","ks","srDev","mseStart"),
              .packages=c("plyr","dplyr","reshape","ggplot2","FLCore","ggplotFL",
                          "FLasher","FLBRP","FLife","mydas")) %dopar%{
    
      fn<-function(cv,nyr,k1,k2){
          source('~/Desktop/sea++/mydas/pkg/R/mseSBTD.R')
          spp="turbot"
          load(file.path(dirRes,paste("base-",spp,".RData",sep="")))
                      
          set.seed(1235)
          uDev =FLife:::rlnoise(500,FLQuant(0,dimnames=list(year=1:105)),cv,b=0.0)

          ctrl=propagate(rbind(FLPar(k1   =k1),
                               FLPar(k2   =k2),
                               FLPar(gamma=1)),nits)
          
          mse=mseSBTD(om,eq,
                      control=ctrl,
                      srDev  =srDev,uDev=uDev,
                      start  =mseStart[spp]+1,end=mseStart[spp]+46,
                      nyrs   =nyr)
                              
          save(mse,file=file.path(dirRes,paste("ranD-final-",
                                spp,"-",cv,"-",nyr,".RData",sep="")))
           
          cbind(nyr=nyr,cv=cv)}
    
  with(ks[i,], fn(cv,nyr,k1,k2))}
```

```{r, mse2}
sm<-foreach(i=seq(dim(ks)[1]), 
              .combine=rbind,
              .multicombine=TRUE,
              .export=c("dirRes","dirOM","ks","srDev","mseStart"),
              .packages=c("plyr","dplyr","reshape","ggplot2","FLCore","ggplotFL",
                          "FLasher","FLBRP","FLife","randtests")) %dopar%{
    
     source('~/Desktop/sea++/mydas/pkg/R/smryStat.R')
     source('~/Desktop/sea++/mydas/pkg/R/omOut.R')
                     
     fn<-function(cv,nyr){
          spp="turbot"
          load(file.path(dirRes,paste("base-",spp,".RData",sep="")))
                      
          load(file.path(dirRes,paste("ranD-final-",
                          spp,"-",cv,"-",nyr,".RData",sep="")))
          mse=window(mse,start=mseStart[spp]+1,end=mseStart[spp]+40)
          res=transform(omSmry(mse,eq,lh),
                 iter=factor(iter,level=ac(sort(as.numeric(ac(unique(iter)))))))
          res=transform(res,year=year-mseStart[spp])
          pm =ddply(res,.(iter), smryStat)
                    
          pm}
    
  with(ks[i,], cbind(cv=cv,nyr=nyr,fn(cv,nyr)))}

save(sm,file=file.path(dirRes,"sm.RData"))
```

```{r}
ggplot(melt(sm[,c("safety","blim","kobe.n","yield","yieldAav","cv","nyr")],
            id=c("cv","nyr")))+
  geom_boxplot(aes(x=as.character(cv),y=value))+
  theme_bw()+
  facet_grid(variable~nyr,scale="free")
```


\newpage
## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLasher:   `r packageVersion('FLasher')`
* FLife:     `r packageVersion('FLife')`
* ggplotFL:  `r packageVersion('ggplotFL')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
```
