---
title: "Grid empd"
subtitle: "Razors"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---
  
```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="tex/grid-",
               cache.path="cache/grid/")

iFig=0
iTab=0
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task4"  
dirDat=file.path(dirMy,"data")
```
```{r, pkgs}
library(ggplot2)
library(plyr)

library(FLCore)
library(ggplotFL)
```


```{r, brill}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/constD-brill.RData")  
brill=FLStocks("k1=0; k2=0"=mse)
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-brill-1.RData")
brill["k1=0.5; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-brill-2.RData")
brill["k1=0.5; k2=1.0"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-brill-3.RData")
brill["k1=1.0; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-brill-4.RData")
brill["k1=1.0; k2=1.0"]=mse
brill=FLStocks(llply(brill,window,end=101))
plot(brill)
```

**Figure `r iFig=iFig+1; iFig`** Time series for brill of empirical HCR ran with different values of K1 & K2

```{r, turbot}             
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/constD-turbot.RData")  
turbot=FLStocks("k1=0; k2=0"=mse)
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-turbot-1.RData")
turbot["k1=0.5; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-turbot-2.RData")
turbot["k1=0.5; k2=1.0"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-turbot-3.RData")
turbot["k1=1.0; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-turbot-4.RData")
turbot["k1=1.0; k2=1.0"]=mse
turbot=FLStocks(llply(turbot,window,end=101))
plot(turbot)
```

**Figure `r iFig=iFig+1; iFig`** Time series for turbot of empirical HCR ran with different values of K1 & K2

```{r, pollack}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/constD-pollack.RData")
pollack=FLStocks("k1=0; k2=0"=mse)  
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-pollack-1.RData")
pollack["k1=0.5; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-pollack-2.RData")
pollack["k1=0.5; k2=1.0"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-pollack-3.RData")
pollack["k1=1.0; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-pollack-4.RData")
pollack["k1=1.0; k2=1.0"]=mse
pollack=FLStocks(llply(pollack,window,start=56,end=103))
plot(pollack)
```

**Figure `r iFig=iFig+1; iFig`** Time series for pollack of empirical HCR ran with different values of K1 & K2

```{r, sprat}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/constD-sprat.RData")
sprat=FLStocks("k1=0; k2=0"=mse)
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-sprat-1.RData")
sprat["k1=0.5; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-sprat-2.RData")
sprat["k1=0.5; k2=1.0"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-sprat-3.RData")
sprat["k1=1.0; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-sprat-4.RData")
sprat["k1=1.0; k2=1.0"]=mse
sprat=FLStocks(llply(sprat,window,end=99))
plot(sprat)
```

**Figure `r iFig=iFig+1; iFig`** Time series for sprat of empirical HCR ran with different values of K1 & K2

```{r, ray}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/constD-ray.RData")
ray=FLStocks("k1=0; k2=0"=mse)
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-ray-1.RData")
ray["k1=0.5; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-ray-2.RData")
ray["k1=0.5; k2=1.0"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-ray-3.RData")
ray["k1=1.0; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-ray-4.RData")
ray["k1=1.0; k2=1.0"]=mse
ray=FLStocks(llply(ray,window,start=60,end=104))
plot(ray)
```

**Figure `r iFig=iFig+1; iFig`** Time series for ray of empirical HCR ran with different values of K1 & K2

```{r, razor}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/constD-razor.RData")
razor=FLStocks("k1=0; k2=0"=mse)
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-razor-1.RData")
razor["k1=0.5; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-razor-2.RData")
razor["k1=0.5; k2=1.0"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-razor-3.RData")
razor["k1=1.0; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-razor-4.RData")
razor["k1=1.0; k2=1.0"]=mse
razor=FLStocks(llply(razor,window,end=101))
plot(razor)
```

**Figure `r iFig=iFig+1; iFig`** Time series for razor of empirical HCR ran with different values of K1 & K2

```{r, lobster}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/constD-lobster.RData")
lobster=FLStocks("k1=0; k2=0"=mse)
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-lobster-1.RData")
lobster["k1=0.5; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-lobster-2.RData")
lobster["k1=0.5; k2=1.0"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-lobster-3.RData")
lobster["k1=1.0; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-lobster-4.RData")
lobster["k1=1.0; k2=1.0"]=mse
lobster=FLStocks(llply(lobster,window,end=104))
plot(lobster)
```

**Figure `r iFig=iFig+1; iFig`** Time series for lobster of empirical HCR ran with different values of K1 & K2

\newpage
## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLasher:   `r packageVersion('FLasher')`
* FLife:     `r packageVersion('FLife')`
* ggplotFL:  `r packageVersion('ggplotFL')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
```

