---
title: "Grid empd"
subtitle: "Razors"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---
  
```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="tex/grid-",
               cache.path="cache/grid/")

iFig=0
iTab=0
```
```{r, dir}
dirMy="/home/laurence/Desktop/Dropbox/mydasOMs"
#dirMy="/ichec/home/users/laurie"
dirDat=file.path(dirMy,"data")
dirRes=file.path(dirMy,"results")
```
```{r, pkgs}
library(ggplot2)
library(plyr)

library(FLCore)
library(ggplotFL)
```


```{r, brill}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/constD-brill.RData")  
brill=FLStocks("k1=0; k2=0"=mse)
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-brill-1.RData")
brill["k1=0.5; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-brill-2.RData")
brill["k1=0.5; k2=1.0"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-brill-3.RData")
brill["k1=1.0; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-brill-4.RData")
brill["k1=1.0; k2=1.0"]=mse
brill=FLStocks(llply(brill,window,end=101))
plot(brill)
```

**Figure `r iFig=iFig+1; iFig`** Time series for brill of empirical HCR ran with different values of K1 & K2

```{r, turbot}             
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/constD-turbot.RData")  
turbot=FLStocks("k1=0; k2=0"=mse)
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-turbot-1.RData")
turbot["k1=0.5; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-turbot-2.RData")
turbot["k1=0.5; k2=1.0"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-turbot-3.RData")
turbot["k1=1.0; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-turbot-4.RData")
turbot["k1=1.0; k2=1.0"]=mse
turbot=FLStocks(llply(turbot,window,end=101))
plot(turbot)
```

**Figure `r iFig=iFig+1; iFig`** Time series for turbot of empirical HCR ran with different values of K1 & K2

```{r, pollack}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/constD-pollack.RData")
pollack=FLStocks("k1=0; k2=0"=mse)  
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-pollack-1.RData")
pollack["k1=0.5; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-pollack-2.RData")
pollack["k1=0.5; k2=1.0"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-pollack-3.RData")
pollack["k1=1.0; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-pollack-4.RData")
pollack["k1=1.0; k2=1.0"]=mse
pollack=FLStocks(llply(pollack,window,start=56,end=103))
plot(pollack)
```

**Figure `r iFig=iFig+1; iFig`** Time series for pollack of empirical HCR ran with different values of K1 & K2

```{r, sprat}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/constD-sprat.RData")
sprat=FLStocks("k1=0; k2=0"=mse)
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-sprat-1.RData")
sprat["k1=0.5; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-sprat-2.RData")
sprat["k1=0.5; k2=1.0"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-sprat-3.RData")
sprat["k1=1.0; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-sprat-4.RData")
sprat["k1=1.0; k2=1.0"]=mse
sprat=FLStocks(llply(sprat,window,end=99))
plot(sprat)
```

**Figure `r iFig=iFig+1; iFig`** Time series for sprat of empirical HCR ran with different values of K1 & K2

```{r, ray}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/constD-ray.RData")
ray=FLStocks("k1=0; k2=0"=mse)
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-ray-1.RData")
ray["k1=0.5; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-ray-2.RData")
ray["k1=0.5; k2=1.0"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-ray-3.RData")
ray["k1=1.0; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-ray-4.RData")
ray["k1=1.0; k2=1.0"]=mse
ray=FLStocks(llply(ray,window,start=60,end=104))
plot(ray)
```

**Figure `r iFig=iFig+1; iFig`** Time series for ray of empirical HCR ran with different values of K1 & K2

```{r, razor}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/constD-razor.RData")
razor=FLStocks("k1=0; k2=0"=mse)
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-razor-1.RData")
razor["k1=0.5; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-razor-2.RData")
razor["k1=0.5; k2=1.0"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-razor-3.RData")
razor["k1=1.0; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-razor-4.RData")
razor["k1=1.0; k2=1.0"]=mse
razor=FLStocks(llply(razor,window,end=101))
plot(razor)
```

**Figure `r iFig=iFig+1; iFig`** Time series for razor of empirical HCR ran with different values of K1 & K2

```{r, lobster, eval=FALSE}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/constD-lobster.RData")
lobster=FLStocks("k1=0; k2=0"=mse)
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-lobster-1.RData")
lobster["k1=0.5; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-lobster-2.RData")
lobster["k1=0.5; k2=1.0"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-lobster-3.RData")
lobster["k1=1.0; k2=0.5"]=mse
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/gridD-lobster-4.RData")
lobster["k1=1.0; k2=1.0"]=mse
lobster=FLStocks(llply(lobster,window,end=104))
plot(lobster)
```

```{r, smry}
fn<-function(om){
  as.data.frame(FLQuants(om, 
          "ssb" = function(x) ssb(x)%/%refpts( eq)["msy","ssb"], 
          "f" =   function(x) fbar(x)%/%refpts(eq)["msy","harvest"], 
          "rec" = function(x) rec(x)%/%refpts( eq)["msy","rec"], 
          "catch"=function(x) landings(x)%/%refpts(eq)["msy","yield"]))}

load(file.path(dirDat,"brill.RData"))
smry=cbind(spp="brill",ldply(brill,fn))

load(file.path(dirDat,"turbot.RData"))
smry=rbind(smry,cbind(spp="turbot",ldply(turbot,fn)))

load(file.path(dirDat,"pollack.RData"))
smry=rbind(smry,cbind(spp="pollack",ldply(pollack,fn)))

load(file.path(dirDat,"ray.RData"))
smry=rbind(smry,cbind(spp="ray",ldply(ray,fn)))

load(file.path(dirDat,"sprat.RData"))
smry=rbind(smry,cbind(spp="sprat",ldply(sprat,fn)))
```


```{r, smry-plot, fig.height=8,fig.width=12}
smry=subset(smry,qname!="rec")
smry$spp  =factor(smry$spp,  level=c("ray","pollack","turbot","brill","sprat"))
smry$qname=factor(smry$qname,level=c("catch","ssb","f"))

ggplot(ddply(smry,.(spp,year,qname,.id), with, quantile(data,na.rm=TRUE)))+
  geom_ribbon(aes(year,ymin=`25%`,ymax=`75%`,fill=.id),alpha=0.2)+
  geom_path(aes(year,`50%`,col=.id))+
  facet_grid(qname~spp,scale="free")+
  theme(legend.position="bottom")
```

```{r, smry-plot-2, fig.height=8,fig.width=12}
ggplot(ddply(smry,.(spp,year,qname,.id), with, quantile(data,na.rm=TRUE)))+
  geom_ribbon(aes(year,ymin=`25%`,ymax=`75%`,fill=.id),alpha=0.2)+
# geom_path(aes(year,`50%`,col=.id))+
  geom_path(aes(year,data,col=.id,group=paste(iter,.id,spp,qname)),linetype="23",data=subset(smry,iter%in%c(12)))+
  facet_grid(qname~spp,scale="free")+
  theme(legend.position="bottom")
```

```{r}
source('~/Desktop/sea++/mydas/pkg/R/smryStat.R')
source('~/Desktop/sea++/mydas/pkg/R/omOut.R')
```

```{r}
minMax<-function(x,na.rm=TRUE) (x-min(x,na.rm=na.rm))/diff(range(x,na.rm=na.rm))
mseStart=c("brill"=54,"turbot"=54,"ray"=60,"pollack"=56,"sprat"=52,"razor"=54,"lobster"=57)


library(FLife)
library(reshape)

process=function(spp,ctrl,start,
                 dirDat="/home/laurence/Desktop/Dropbox/mydasOMs/data",
                 dirRes="/home/laurence/Desktop/Dropbox/mydasOMs/results"){
    
  load(file.path(dirDat,paste(spp,".RData",sep="")))
  load(file.path(dirDat,"dCtrl.RData"))
  load(file.path(dirRes,paste("ranD-",spp,"-",ctrl,".RData",sep="")))
  
  res=transform(omSmry(mse,eq,lh),
                iter=factor(iter,level=ac(sort(as.numeric(ac(unique(iter)))))))
  ctl=transform(model.frame(control[[ctrl]]),
                iter=factor(iter,level=ac(sort(as.numeric(ac(iter))))))
  res=transform(res,year=year-start)
  pm =ddply(res,.(iter), smryStat)
  pm=merge(ctl,pm,by="iter")
  pm}

scen=expand.grid(spp    =c("brill",   "turbot",   "ray",   "pollack",   "sprat"),
                 control=1:12,
                 stringsAsFactors=FALSE)

pm=mdply(scen,function(spp,control) process(spp,control,mseStart[spp]))
save(pm,file="/home/laurence/Desktop/Dropbox/mydasOMs/results/pm.RData",compress="xz")

dt=transform(pm,k1=cut(k1,breaks=seq(0,1,0.1)),
                k2=cut(k2,breaks=seq(0,1,0.1)))

dt2=ddply(dt,.(spp,k1,k2), with, 
                   data.frame(kobe  =mean(kobe.n),
                              safety=mean(safety),
                              yield =mean(yield),
                              aav   =(mean(1-yieldAav))))
dt3=melt(dt2,id=c("k1","k2","spp"))
dt4=ddply(dt3,.(variable,spp), transform, value=minMax(value))

dt4$spp  =factor(dt4$spp,     level=c("ray","pollack","turbot","brill","sprat"))
dt4$qname=factor(dt4$variable,level=c("safety","kobe","yield","aav"))
```

```{r}
library(RPostgreSQL)
library(DBI)

drv  =dbDriver("PostgreSQL")

conLK=dbConnect(drv, 
                host    ='wklife.csrzweaa3tbm.eu-west-2.rds.amazonaws.com',
                dbname  ='wklife',
                port    =5432,
                user    ='mydas',
                password='Yes_Meski')
dbListTables(conLK)
dbWriteTable(conLK, "randgridpm", value=pm, append=FALSE,overwrite=TRUE,row.names=FALSE)

save(smry,file="/home/laurence/Desktop/Dropbox/pm.RData")
save(smry,file="/home/laurence/Desktop/Dropbox/smry.RData")
```

```{r, grid}
library(dplyr)  

mycol=rev(c("navy","blue","cyan","lightcyan","yellow","red","red4"))
ggplot(dt4)+
  geom_tile(aes(k1,k2,fill=value))+
  scale_fill_gradientn(colours=mycol)+
  facet_grid(spp~variable)

dt2=ddply(dt,.(spp,k1,k2), transmute, 
                   u1 =mean(kobe.n)/45,
                   u2 =mean(yield),
                   u3 =mean(safety),
                   u4 =mean(kobe.n)+mean(yield)+mean(safety)+mean(1-yieldAav))

dt2=transform(dt2,u2=u1*u2,u3=u1*u2*u3,u4=u1*u2*u3*u4)
dt3=melt(dt2,id=c("k1","k2","spp"))
dt4=ddply(dt3,.(variable,spp), transform, value=minMax(value))

dt4$spp  =factor(dt4$spp,     level=c("ray","pollack","turbot","brill","sprat"))
dt4$qname=factor(dt4$variable,level=c("safety","kobe","yield","aav"))
```

```{r, grid-2}
ggplot(aes(as.numeric(k1),as.numeric(k2),z=value),data=dt4)+  
  geom_tile(aes(k1,k2,fill=value))+
  scale_fill_gradientn(colours=mycol)+
  facet_grid(spp~variable)
```

```{r}
library(akima)

t=ddply(pm,.(spp), with, {
  t=interp(k1,k2,z=yield,xo=seq(0,1,.05),yo=seq(0,1,.02),duplicate="mean")
  cbind(expand.grid(x=t$x,y=t$y),z=c(t$z))})

ggplot(aes(x,y,z=z),data=t)+
  geom_tile(aes(x,y,fill=z))+
  scale_fill_gradientn(colours=mycol)+
#stat_contour(aes(colour= ..level..),breaks=seq(0,1,.1))+
  facet_wrap(~spp,ncol=2)
```

geom_density2d()
\newpage
## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLasher:   `r packageVersion('FLasher')`
* FLife:     `r packageVersion('FLife')`
* ggplotFL:  `r packageVersion('ggplotFL')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
```

