---
title: "Pareto Multi-objective Trade-offs"
subtitle: "Turbot Base Case"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="../tex/base-",
               cache.path="cache/base/")

iFig=0
iTab=0
```
```{r, dir}  
dirOM ="/home/laurence/Desktop/sea++/mydas/project/tasks/task4/data"
dirRes="/home/laurence/Desktop/sea++/mydas/project/papers/pareto/data"
```

```{r, pkgs}
library(ggplot2)
library(plyr)
library(dplyr)
library(reshape)

library(FLCore)
library(FLBRP)
library(FLasher)
library(ggplotFL)
library(FLife)
library(randtests)

library(mydas)

library(GGally)
```
```{r}
library(doParallel)
library(foreach)

cl=makeCluster(3)
registerDoParallel(cl)
```

```{r, OMscen}
nits=500

scen=expand.grid(nyr    =c(3,5,7),
                 cv     =c(0.1,0.2,0.3),
                 spp    ="turbot",
                 ctrl   =1:9,
                 stringsAsFactors=FALSE)

mseStart=c("brill"=54,"turbot"=54,"ray"=60,"pollack"=56,
           "sprat"=52,"razor"=54, "lobster"=57)

### Random variaton for control
controls=list()
set.seed(123456)
for (j in 1:12){
    controls[[j]]=rbind(FLPar(k1   =runif(nits, 0.0, 1.5)),
                        FLPar(k2   =runif(nits, 0.0, 1.5)),
                        FLPar(gamma=rep(1, nits)))}
controls=FLPars(controls)

set.seed(1233)
srDev=FLife:::rlnoise(nits,FLQuant(0,dimnames=list(year=1:105)),.3,b=0.0)
```
```{r, OM, eval=FALSE}
## Dont run every time
genTime<-function(object,f=0){
  
     object@fbar=object@fbar[,1]%=%f
     n=stock.n(object)[,1]
     
     apply(stock.wt(object)%*%n%*%ages(stock.wt(object)),6,sum)%/%
     apply(stock.wt(object)%*%n,6,sum)}

load(file.path(dirOM,"turbot.RData"))

lh=apply(lh,1,median)
eq=lhEql(lh,spwn=0)
om=as(eq,"FLStock")

gTime=round(mean(genTime(eq)))

eq@fbar=refpts(eq)["msy","harvest"]%*%FLQuant(c(rep(.1,19),
                                              seq(.1,2,length.out=30),
                                              seq(2,1.0,length.out=gTime)[-1],
                                              rep(1.0,61)))[,1:105]

om=as(eq,"FLStock")
om=fwd(propagate(om,500),fbar=fbar(om)[,-1],sr=eq,residuals=srDev)

save(lh,eq,om,file=file.path(dirRes,"base-turbot.RData"),compress="xz")
```


```{r, mseRand, eval=FALSE}
## Run MSE with random control
ranD<-foreach(i=seq(dim(scen)[1]), 
              .combine=rbind,
              .multicombine=TRUE,
              .export=c("dirRes","dirOM","scen","srDev","controls","mseStart"),
              .packages=c("plyr","dplyr","reshape","ggplot2","FLCore","ggplotFL",
                          "FLasher","FLBRP","FLife","mydas")) %dopar%{
    
      fn<-function(iSpp,iCtrl,cv,nyr){
          load(file.path(dirRes,paste("base-",iSpp,".RData",sep="")))
                              
          set.seed(1235)
          uDev =FLife:::rlnoise(500,FLQuant(0,dimnames=list(year=1:105)),cv,b=0.0)
                      
          mse=mseSBTD(om,eq,
                      control=controls[[iCtrl]],
                      srDev  =srDev,uDev=uDev,
                      start  =mseStart[iSpp]+1,end=mseStart[iSpp]+46,
                      nyrs   =nyr)
                              
          save(mse,file=file.path(dirRes,paste("base-ranD-",
                          iSpp,"-",iCtrl,"-",cv,"-",nyr,".RData",sep="")))
                              
          data.frame(spp=iSpp,control=iCtrl,cv=cv,nyr=nyr)}
    
  with(scen[i,], fn(spp,ctrl,cv,nyr))}
```

```{r, pm, eval=FALSE}
## Get summary stats
source('~/Desktop/sea++/mydas/pkg/R/smryStat.R')
source('~/Desktop/sea++/mydas/pkg/R/omOut.R')

pm=mdply(scen,function(spp,ctrl,nyr,cv,
                       start=80,end=100){
  
  load(file.path(dirRes,"base-turbot.RData"))
  load(file.path(dirRes,paste("base-ranD-",
                          spp,"-",ctrl,"-",cv,"-",nyr,".RData",sep="")))

  mse=window(mse,start=start,end=end)
  res=transform(omSmry(mse,eq,lh),
                iter=factor(iter,level=ac(sort(as.numeric(ac(unique(iter)))))))
  res=transform(res,year=year-start)
  pm =ddply(res,.(iter), smryStat)
  pm=merge(pm,transform(model.frame(controls[[ctrl]]),
                iter=factor(iter,level=ac(sort(as.numeric(ac(iter)))))),
           by="iter")
  pm})

pm$kobe    =pm$kobe.n/40
pm$yieldAav=(1-pm$yieldAav)

save(pm,file=file.path(dirRes,"base-turbot-pm.RData"))
```

```{r, svr}
library(caret)
library(ggplot2)
library(mco)
library(kernlab)

fitSvr=function(dat, target, predictors, tuneLength=5){
  
  ctrl=caret::trainControl(
    method ="repeatedcv",
    repeats=5)
  
  print(paste(target, "~", predictors, sep=" "))
  
  svrFit = caret::train(
    as.formula(paste(target, "~", predictors, sep=" ")),
      data      =dat,
    method    ='svmRadial',
    tuneLength=tuneLength,
    trControl =ctrl,
    metric    ="MAE")
  
  return(svrFit)}

svrFn=function(ind,svr1,svr2){
  ind         =t(data.frame(ind))
  prediction1 =predict(svr1,ind)
  prediction2 =predict(svr2,ind)
  result      =c(prediction1, prediction2)
  
  return(result)}

svrFn2=function(ind,...)
    laply(list(...), function(x) predict(x,t(data.frame(ind))))
```

```{r, pareto, eval=FALSE}
load(file.path(dirRes,"base-turbot-pm.RData"))

predictors='k1 + k2'
rewards=c('yield','yieldAav','kobe','safety','blim','plim')

svr=mlply(rewards,function(x) fitSvr(pm, x, predictors,
                                     tuneLength=10)$finalModel)
names(svr)=rewards

pareto=mco::nsga2(fn=svrFn2, svr[[1]],svr[[2]], svr[[3]],svr[[4]],
                  idim=2, odim=4, 
                  lower.bounds=rep(0.0, 2),upper.bounds=rep(1.5, 2), 
                  popsize=1000, generations=100, cprob=0.9)

save(pareto,svr,file=file.path(dirRes,"base-turbot-pareto.RData"))

pm=subset(pm,plim>=0.95)

svr95=mlply(rewards[-6],function(x) fitSvr(pm, x, predictors,
                                     tuneLength=10)$finalModel)
names(svr95)=rewards[-6]

pareto95=mco::nsga2(fn=svrFn2, svr95[[1]],svr95[[2]],svr95[[4]],
                  idim=2, odim=3, 
                  lower.bounds=rep(0.0, 2),upper.bounds=rep(1.5, 2), 
                  popsize=1000, generations=100, cprob=0.9)

save(pareto95,svr95,file=file.path(dirRes,"base-turbot-pareto95.RData"))
```
```{r,eval=FALSE}
# Looked pairwise at objectives, dont run
rwds   =mdply(seq(length(rewards)-1), function(x)
         data.frame(x=rewards[x],y=rewards[-seq(x)],stringsAsFactors=FALSE))[,-1]

paretos=mdply(rwds,function(x,y,svr){
  print(paste(x,y))
  pareto=mco::nsga2(fn=svrFn2, svr[[x]],svr[[y]],
                           idim=2, odim=2, 
                           lower.bounds=rep(0.0, 2),upper.bounds=rep(1.5, 2), 
                           popsize=1000, generations=100, cprob=0.9)
  dat=data.frame(par=pareto$par,value=pareto$value)
  names(dat)=c("k1","k2","x","y")
  cbind(xvar=x,yvar=y,dat)},svr=svr)

save(paretos,svr,file=file.path(dirRes,"base-turbot-paretos.RData"))
```

```{r}
load(file.path(dirRes,"base-turbot-pm.RData"))

ggplot(pm)+
  geom_point(aes(ftar,btar),size=1)
```

```{r, figScatter1}
load(file.path(dirRes,"base-turbot-pm.RData"))
load(file.path(dirRes,"base-turbot-pareto.RData"))

dat=data.frame(par=pareto$par,value=pareto$value)
names(dat)=c("k1","k2",rewards)

ggplot(pm)+
  geom_point(aes(kobe,yield),size=1)+
  geom_point(aes(kobe,yield),data=dat,fill="red",col="darkred",shape=23)+
  theme_bw()+theme(legend.position="bottom")+
  xlab("plim")+ylab(expression(Yield:MSY))+
  guides(col=guide_legend(title="AAV in Yield",size=2))
```

**Figure `r iFig=iFig+1; iFig`.** 

```{r, figScatter2}
ggplot(pm)+
  geom_point(aes(blim,yield,col=yieldAav),size=1)+
  geom_point(aes(blim,yield),data=dat,fill="red",col="darkred",shape=23)+
  theme_bw()+theme(legend.position="bottom")+
  xlab(expression(B[lim]))+ylab(expression(Yield:MSY))+
  guides(col=guide_legend(title="AAV in Yield",size=2))
```

**Figure `r iFig=iFig+1; iFig`.** 

```{r, figScatter3}
ggplot(transform(pm,kobe=kobe.n/40))+
  geom_point(aes(kobe,yield,col=yieldAav),size=1)+
  geom_point(aes(kobe,yield),data=dat,fill="red",col="darkred",shape=23)+
  theme_bw()+theme(legend.position="bottom")+
  xlab("Kobe")+ylab(expression(Yield:MSY))+
  guides(col=guide_legend(title="AAV in Yield",size=2))
```

**Figure `r iFig=iFig+1; iFig`.** 

```{r, figBlim, fig.height=6}
ggplot(melt(dat[,c("k1","k2","safety")],id="safety"))+
  geom_point(aes(safety,value,col=variable))+
  theme_bw()+theme(legend.position="bottom")+
  xlab("Safety")+ylab("Control Value")+
  guides(col=guide_legend(title="Control",size=2))+
  scale_colour_manual(values=c("red","black"))
```

**Figure `r iFig=iFig+1; iFig`.** 

```{r, figKobe, fig.height=6}
ggplot(melt(dat[,c("k1","k2","kobe")],id="kobe"))+
  geom_point(aes(kobe,value,col=variable))+
  theme_bw()+theme(legend.position="bottom")+
  xlab("Kobe")+ylab("Control Value")+
  guides(col=guide_legend(title="Control",size=2))+
  scale_colour_manual(values=c("red","black"))
```

**Figure `r iFig=iFig+1; iFig`.** 

```{r, figYield, fig.height=6}
ggplot(melt(dat[,c("k1","k2","yield")],id="yield"))+
  geom_point(aes(value,yield,col=variable))+
  theme_bw()+theme(legend.position="bottom")+
  ylab(expression(Yield:MSY))+xlab("Control Value")+
  guides(col=guide_legend(title="Control",size=2))+
  scale_colour_manual(values=c("red","black"))
```

**Figure `r iFig=iFig+1; iFig`.** 

```{r, figYieldAav, fig.height=6}
ggplot(melt(dat[,c("k1","k2","yieldAav")],id="yieldAav"))+
  geom_point(aes(1-yieldAav,value,col=variable))+
  theme_bw()+theme(legend.position="bottom")+
  xlab("AAV in Yield")+ylab("Control Value")+
  guides(col=guide_legend(title="Control",size=2))+
  scale_colour_manual(values=c("red","black"))
```

**Figure `r iFig=iFig+1; iFig`.** 



```{r, mse, eval=FALSE}
## Run MSE
iSpp="turbot"
load(file.path(dirOM,paste(iSpp,"2.RData",sep="")))
                              
set.seed(1235)
uDev =FLife:::rlnoise(500,FLQuant(0,dimnames=list(year=1:105)),cv,b=0.0)
              
control=rbind(FLPar(k1   =rep(0.6,nits)),
              FLPar(k2   =rep(1.5,nits)),
              FLPar(gamma=rep(1, nits)))

mse=mseSBTD(om,eq,
            control=control,
            srDev  =srDev,uDev=uDev,
            start  =mseStart[iSpp]+1,end=mseStart[iSpp]+46,
            nyrs   =nyr)
                            
save(mse,file=file.path(dirRes,"base-turbot-mse.RData"))
```

```{r, msePm}
source('~/Desktop/sea++/mydas/pkg/R/smryStat.R')
source('~/Desktop/sea++/mydas/pkg/R/omOut.R')

start=1
end  =40
spp  ="turbot"
  
load(file.path(dirRes,"base-turbot.RData"))
load(file.path(dirRes,"base-turbot-mse.RData"))
mse=window(mse,start=mseStart[spp]+start,end=mseStart[spp]+end)
res=transform(omSmry(mse,eq,lh),
                iter=factor(iter,level=ac(sort(as.numeric(ac(unique(iter)))))))
res=transform(res,year=year-start)
pm =ddply(res,.(iter), smryStat)

pm$kobe    =pm$kobe.n/40

save(pm,file=file.path(dirRes,"base-turbot-mse-pm.RData"))
```

```{r}
load(file.path(dirRes,"base-turbot-mse-pm.RData"))

ggplot(melt(pm[,c("safety","blim","kobe","yield","yieldAav")]))+
  geom_boxplot(aes(x=variable,y=value))+
  theme_bw()
```


\newpage
## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLasher:   `r packageVersion('FLasher')`
* FLife:     `r packageVersion('FLife')`
* ggplotFL:  `r packageVersion('ggplotFL')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
```
