---
title: "k!"
subtitle: "Turbot v Brill Case Study"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
github_document: 
   mathjax: TRUE 
---

# Introduction


# Objectives


# Results

**Figure `r iFig=1;iFig `** 

**Figures `r iFig=iFig+1; iFig`**

**Table `r iTab=1`**.
 
# Discussion and Conclusions


`r iFig=0; iTab=0 `


# Figures
```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =8, 
               fig.height=8,
               cache     =TRUE, 
               fig.path  ="../tex/figs-",
               cache.path="cache/figs/")

iFig=0
iTab=0
```
```{r, dir}  
dirOM ="/home/laurence/Desktop/sea++/mydas/project/data/OM"
dirRes="/home/laurence/Desktop/sea++/mydas/project/papers/pareto/data"
```

```{r, pkgs}
library(ggplot2)
library(plyr)
library(dplyr)
library(reshape)

library(FLife)
library(mydas)
```

```{r, OM}
load(file.path(dirOM,"turbot.RData"))
turbot=list(om=om,eq=eq,prior=prior,lh=lh,obs=omSmry(om,eq,lh))

load(file.path(dirOM,"brill.RData"))
brill=list(om=om,eq=eq,prior=prior,lh=lh,obs=omSmry(om,eq,lh))
```


```{r}
plot(FLStocks(Brill=brill$om,Turbot=turbot$om))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`.** Comparison of turbot and brill Operating Models.

```{r}
plot(FLStocks(Brill=iter(brill$om,1),Turbot=iter(turbot$om,1)))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`.** Comparison of turbot and brill Operating Models for 1 iteration, note that recruitment deviates are the same across iterations.

```{r}
eq=rbind(cbind(Stock="Brill", model.frame(FLQuants(iter(brill$eq,1), 
                                    "fbar","rec","ssb","catch"),drop=TRUE)),
         cbind(Stock="Turbot",model.frame(FLQuants(iter(turbot$eq,1),
                                    "fbar","rec","ssb","catch"),drop=TRUE)))
```

```{r}
ggplot(eq)+geom_line(aes(ssb,rec,col=Stock))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`.** Comparison of turbot and brill stock recruitment relationships.


```{r}
ggplot(eq)+geom_line(aes(fbar,catch,col=Stock))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`.** Comparison of turbot and brill production functions.

```{r}
ts=rbind(cbind(Stock="Turbot",
               model.frame(FLQuants(turbot$om[,ac(60:100)],"rec","ssb"),drop=T)),
         cbind(Stock="Brill", 
               model.frame(FLQuants(brill$om[ ,ac(60:100)],"rec","ssb"),drop=T)))

ccf=ddply(ts,.(Stock,iter), with, {res=ccf(rec,ssb,plot=FALSE,lag.max=5);
                                   data.frame(lag=res$lag,ccf=res$acf)})
ccf$lag=factor(ccf$lag,levels=unique(ccf$lag))
ggplot(ccf)+
  geom_boxplot(aes(x=lag,y=ccf))+
  facet_grid(Stock~.)+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Cross correlation between SSB and recruitment, i.e. brill is driven by recruitment from 1 to 2 years and turbot by 4 years previously.


```{r}
ccf=ddply(subset(rbind(cbind(Stock="Brill", brill$obs),
                       cbind(Stock="Turbot",turbot$obs)),year%in%20:60),
          .(Stock,iter), with, 
          {res=ccf(fbar,sln,plot=FALSE,lag.max=5);
                                     data.frame(lag=res$lag,ccf=res$acf)})
ccf$lag=factor(ccf$lag,levels=unique(ccf$lag))
ggplot(ccf)+
  geom_boxplot(aes(x=lag,y=ccf))+
  facet_grid(Stock~.)+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Cross correlation between F and length, i.e. brill length is driven by current F and turbot by 4-5 years previously.


```{r}
rule<-function(y, x, nominator=2, denominator=3){
    two   =mean(subset(x,year%in%(y-seq(nominator)  +1))$ssb)
    three =mean(subset(x,year%in%(y-seq(denominator)+1))$ssb)
    two/three}
```


```{r}
rT=ddply(turbot$obs, .(iter), with, mdply(data.frame(y=40:80), rule,
                                         x=data.frame(year=year,ssb=ssb)))
ggplot(rT)+geom_boxplot(aes(ac(y),V1))
```

**Figure `r iFig=iFig+1; iFig`.** r for turbot.


```{r}
rB=ddply(brill$obs, .(iter), with, mdply(data.frame(y=40:80), rule,
                                         x=data.frame(year=year,ssb=ssb)))

ggplot(rB)+geom_boxplot(aes(ac(y),V1))
```
**Figure `r iFig=iFig+1; iFig`.** r for brill.


```{r}
D<-function(n,x) 
  mdply(data.frame(t=n:length(x)), 
        function(t) data.frame(slope=lm(x[t-seq(n)+1]~seq(n))$coefficients[2]))
                       
P<-function(now=1:2,then=1:3,x) 
  mdply(data.frame(t=max(now,then):length(x)), 
        function(t) mean(x[t-now+1])/mean(x[t-then+1]))

P2<-function(now,ref,x) 
  mdply(data.frame(t=max(now,then):length(x)), 
        function(t) mean(x[t-now+1])/mean(x[t-then+1]))
```

```{r}
library(ROCS)
der3=ddply(obs,.(iter), with, D(n=3,x=ssb))
der5=ddply(obs,.(iter), with, D(n=5,x=ssb))
der7=ddply(obs,.(iter), with, D(n=7,x=ssb))
```



\newpage
## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLasher:   `r packageVersion('FLasher')`
* FLife:     `r packageVersion('FLife')`
* ggplotFL:  `r packageVersion('ggplotFL')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
```
