---
title: "Proxy $MSY$ Reference Points for data poor stocks"
subtitle: "Power of length based indicators to detect overfishing."
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    pdf_document:
       includes:
            in_header: header.tex 
---


```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =6, 
               fig.height=6,
               cache     =TRUE, 
               fig.path  ="../tex/roc-",
               cache.path="cache/roc/",
               dev       =c("pdf","png"))

iFig=0
iTab=0
```

\newpage
```{r, pkgs} 
library(FLCore)
library(FLBRP)
library(FLasher)
library(FLife)
library(mydas)
library(ggplotFL)

library(plyr)
library(dplyr)
library(reshape)
library(GGally)

library(popbio)

library(LBSPR)
library(spatstat)
```

```{r, lh-params}
## Read in parameters from fishbase
load(url("https://github.com//fishnets//fishnets//blob//master//data//fishbase-web//fishbase-web.RData?raw=True"))

## lh
lh=subset(fb,species%in%c("Pollachius pollachius","Psetta maxima",
                          "Scophthalmus rhombus","Raja clavata",
                          "Sprattus sprattus","Sprattus sprattus sprattus")) 

names(lh)[c(14:17)]=c("l50","l50min","l50max","a50")
lh=lh[,c("species","linf","k","t0","a","b","a50","l50","l50min","l50max")]

lh[is.na(lh["l50"]),"l50"]=(lh[is.na(lh["l50"]),"l50min"]+lh[is.na(lh["l50"]),"l50max"])/2
lh=lh[,-(9:10)]

# Add extra parameters for pollack
lh[lh$t0>=0,"t0"]=NA
lh=rbind(lh[1,],lh)
lh[1,-c(1,7:8)]=c(84.6,0.19,-0.94,0.01017,2.98)
lh[1,"l50"]=0.72*lh[1,"linf"]^0.93

lh=transform(lh,l50linf=l50/linf)

fctr=ddply(lh,.(species),with,mean(linf))
fctr=as.character(fctr[order(fctr$V1),"species"])

lh$species=factor(as.character(lh$species),levels=fctr)
```

```{r, cor}
cor=cor(model.frame(lh)[,c("linf","k","l50","t0","a","b","l50linf")],
        use="pairwise.complete.obs")

my_smooth <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_point(...,size=.5)+
    geom_smooth(...,method="lm",se=FALSE)}

my_density <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_histogram(...,lwd=1)}

theme_set(theme_bw(base_size=20))

ggpairs(transform(lh[,c(1:3,8,6)],linf=log(linf),k=log(k),l50=log(l50)),
          mapping = ggplot2::aes(color=species),
          lower = list(continuous = wrap(my_smooth)),
          diag=list(continuous=wrap(my_density,alpha=0.2)),
          title = "")+
  theme(legend.position ="none",
        panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.x      =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

```{r, lhs}
lhs=dlply(lh,.(species), with, {
  
    res=lhPar(FLPar(
                   linf =mean(linf,na.rm=T),
                   k    =mean(k,   na.rm=T),
                   t0   =mean(t0,  na.rm=T),
                   l50  =mean(l50, na.rm=T),
                   a    =mean(a,   na.rm=T),
                   b    =mean(b,   na.rm=T)))
          
     res=rbind(res,FLPar(lopt =2/3*mean(res["linf"])))
     # also Linf*(3/(3+M/K)) 
     res=rbind(res,FLPar(lmega=1.1*mean(res["lopt"])))
     res})

save(lhs,  
     file="/home/laurence/Desktop/sea++/mydas/project/papers/ROC/data/lhs.RData")
```

```{r, oms}
f=FLQuant(c(rep(0.1,60),seq(0.1,2.5,length.out=40)[-40],
            seq(2.5,1,length.out=11),rep(1,20)))

nits=100
set.seed(234)
srDev=rlnoise(nits,f%=%0,0.3,0)

oms=llply(lhs, function(x,f,srDev){
  eq      =lhEql(x)
  fbar(eq)=f%*%refpts(eq)["msy","harvest"]
  
  ##check fmsy is estimated
  if (any(is.na(refpts(eq)["msy","harvest"])))
    fbar(eq)[,,,,,is.na(refpts(eq)["msy","harvest"])]=
      f%*%refpts(eq)["f0.1","harvest",is.na(refpts(eq)["msy","harvest"])]
  
  om      =propagate(as(eq,"FLStock"),dim(srDev)[6])
  om      =fwd(om,fbar=fbar(eq)[,-1],
               sr=eq,residuals=srDev)
  om},f=f,srDev=srDev)

oms=FLStocks(oms)

msy=ldply(lhs, function(x){
  eq      =lhEql(x)
  model.frame(refpts(eq)["msy",1:4])})

msy=transform(msy,qname=factor(quant,labels=c("Rec","SSB","Catch","F"),
                                      levels=c("rec","ssb","yield","harvest")))
names(msy)[1]="stock"

save(oms,msy,  
     file="/home/laurence/Desktop/sea++/mydas/project/papers/ROC/data/oms.RData")
```


\newpage
\blandscape

```{r, ts, fig.height=6, fig.width=12}
p=plot(FLStocks(llply(oms, window,start=50))) 
p$data=transform(merge(p$data,msy,by=c("qname","stock")),data=data/msy)
p$qname=factor(p$qname,levels=c("F","Rec","SSB","Catch"))
p+facet_grid(qname~stock,scale="free")+
  geom_hline(aes(yintercept=1),col="red",linetype=2)+
  theme_bw()+
  theme(legend.position="none")
```

**Figure `r iFig=iFig+1; iFig`** Time series relative to MSY benchmarks.
\elandscape



\newpage
## Mean length indicators
```{r, alk}
invAlks =llply(lhs,invAlk,cv=0.1)
```


```{r, lfd, fig.width=12, fig.height=6}
lfds=mdply(data.frame(stock=as.character(names(oms)),stringsAsFactors=FALSE), 
           function(stock){
  om=window(oms[[stock]],start=2)
  
  if (any(any(catch.n(om)<0)))
    catch.n(om)[catch.n(om)<0]=0.0
  
  lfd=lenSample(catch.n(om),invAlks[[stock]],nsample=500)
  lfd=transform(melt(lfd),data=value)[,-4]
  lfd=subset(as.data.frame(lfd,drop=TRUE),data>0)
  
  lfd})
```


\newpage
\blandscape

```{r, lf, fig.width=12, fig.height=6}
dat=ddply(subset(lfds,year%in%c(50,100,130)&iter==2),.(stock,year), transform,
          len =len/max(len))
dat$label=c("0.1Fmsy","2.5Fmsy","Fmsy")[factor(dat$year)]
ggplot(dat)+    
  geom_histogram(aes(len,weight=data),binwidth=.05)+
  #geom_vline(aes(xintercept=value,col=variable),data=melt(rln,id="year"))+
  facet_grid(year~stock,scale="free")+
  xlab("Relative Length")+ylab("")+
  scale_color_manual("Indicator",values=rainbow(4))
```
**Figure `r iFig=iFig+1; iFig`.** Simulated length frequencies distributions with indicators.

\elandscape


\newpage
\blandscape
```{r, inds}
source('~/Desktop/sea++/mydas/pkg/R/oemLn.R')
dat=transform(lfds,lopt=laply(lhs,function(x) x["lopt"])[stock])
inds=ddply(dat,.(stock,year,iter), with,
                lenInd(len,data,lopt))

save(inds,  
     file="/home/laurence/Desktop/sea++/mydas/project/papers/ROC/data/inds.RData")
```

```{r, indsTurbot}
quad=data.frame(x=c(50,80, 80, 50,  80,90,90,80, 90,105,105,90, 
                    105,110,110,105, 110,120,120,110), 
                y=rep(c(-Inf,-Inf,Inf,Inf),5),
                f=c(rep("green", 4),rep("amber", 4),rep("red",4),
                    rep("amber2",4),rep("green2",4)))

lind=dlply(subset(inds,year>=50&year<=120),.(stock), with, FLQuants(
                  l95  =as.FLQuant(data.frame(year=year,iter=iter,data=l95) , units="NA"),
                  l25  =as.FLQuant(data.frame(year=year,iter=iter,data=l25),  units="NA"),
                  lmax =as.FLQuant(data.frame(year=year,iter=iter,data=lmax5),units="NA"),
                  pmega=as.FLQuant(data.frame(year=year,iter=iter,data=pmega),units="NA"),
                  lfm  =as.FLQuant(data.frame(year=year,iter=iter,data=lfm),  units="NA"),
                  lbar =as.FLQuant(data.frame(year=year,iter=iter,data=lbar), units="NA")))

p=plot(lind[["Psetta maxima"]])+       
  facet_grid(qname~.,scale="free")+
  geom_polygon(aes(x,y,fill=f),data=quad,alpha=0.2)+
  geom_vline(aes(xintercept=x),data=data.frame(y="2FMSY",x=c( 90,105)),col="red")+
  geom_vline(aes(xintercept=x),data=data.frame(y="2FMSY",x=c( 80,110)),col="orange")+
  scale_fill_manual(values=c("orange","orange","green","green","red","blue"))

p5=p$layers[[5]]
p$layers[[5]]=p$layers[[1]]
p$layers[[1]]=p5  
p
```

**Figure `r iFig=iFig+1; iFig`.** Lfm time series of indicators compared to $F:F_{MSY}$, vertical lines indicate 1 (green), 1.5 (orange) and 2 (red) times $F_{MSY}$.



\elandscape

```{r, sa, eval=FALSE}
#load("/home/laurence/Desktop/sea++/mydas/project/papers/ROC/data/lhs.RData")

library(LBSPR)
#source('~/Desktop/sea++/mydas/pkg/R/lbspr.R')

lhs=FLPars(llply(lhs,function(x) rbind(x[1:20],popdyn(x)["mk"])))

lfds$stock=as.character(lfds$stock)

flqs=dlply(lfds, .(stock), with, {
        len=as.FLQuant(data.frame(len =len,
                                  year=as.numeric(as.character(year)),
                                  iter=as.numeric(as.character(iter)),
                                  data=value))
        len=len[order(as.numeric(dimnames(len)[[1]])),
                order(as.numeric(dimnames(len)[[2]]))]
        
        len[is.na(len)]=0
        len})
```

```{r, eval=FALSE}
lbs=mdply(data.frame(stock=names(flqs),stringsAsFactors=FALSE), function(stock)
     lbspr(flqs[[stock]],lhs[[stock]]))
```

```{r, eval=FALSE}
lbs=list("Sprattus sprattus sprattus"=lbspr(flqs[["Sprattus sprattus sprattus"]],lhs[["Sprattus sprattus sprattus"]]))
```

```{r, eval=FALSE}
lbs["Scophthalmus rhombus"]=lbspr(flqs[["Scophthalmus rhombus"]],lhs[["Scophthalmus rhombus"]])
```

```{r, eval=FALSE}
lbs["Psetta maxima"]=lbspr(flqs[["Psetta maxima"]],lhs[["Psetta maxima"]])
```

```{r, eval=FALSE}
lbs["Pollachius pollachius"]=lbspr(flqs[["Pollachius pollachius"]],lhs[["Pollachius pollachius"]])
```

```{r, eval=FALSE}
lbs["Raja clavata"]=lbspr(flqs[["Raja clavata"]],lhs[["Raja clavata"]])
```

```{r, eval=FALSE}
fm =FLQuants(llply(lbs[-1], function(x) x[["fm"]]))
names(fm) =names(lbs)
plot(fm)
```

```{r, eval=FALSE}
spr=FLQuants(llply(lbs[-1], function(x) x[["spr"]]))
names(spr)=names(lbs)
plot(spr)
```

```{r, eval=FALSE}
#source('~/Desktop/sea++/mydas/pkg/R/roc.R')

ind=subset(inds[,-6],year%in%70:100)
ind=transform(ind,overfished=!(as.numeric(year)%in%90:105))
ind=melt(ind[,-2],id=c("stock","iter","overfished"))
ind=ddply(ind,.(stock,variable),with, mydas:::roc(overfished,value))

ggplot(ind)+ 
  geom_line(aes(FPR,TPR,group=variable,col=as.character(variable)))+
  geom_line(aes(x,y),data.frame(x=seq(0,1,0.01),y=seq(0,1,0.01)))+
  xlab("False Negative Rate")+ylab("True Positive Rate")+
  #scale_color_manual("Indicator",values=rainbow(5))+
  theme_bw(12)+
  theme(legend.position="bottom")+
  facet_wrap(~stock)
```

\newpage
## Length Frequencies

\newpage
## Receiver Operating Characteristics

### Detection of overfishing


**Figure `r iFig=iFig+1; iFig`.** ROC curve of the three indicators of overfishing, points indicate the optimum value of the indicator.

### Detection of recovery


```{r, eval=FALSE}
source('~/Desktop/sea++/mydas/pkg/R/roc.R')

lhs=llply(lhs, function(x){ x["sel2"]=5000; x})

oms=llply(lhs, function(x,f,srDev){
  eq      =lhEql(x)
  fbar(eq)=f%*%refpts(eq)["msy","harvest"]
  
  ##check fmsy is estimated
  if (any(is.na(refpts(eq)["msy","harvest"])))
    fbar(eq)[,,,,,is.na(refpts(eq)["msy","harvest"])]=
      f%*%refpts(eq)["f0.1","harvest",is.na(refpts(eq)["msy","harvest"])]
  
  om      =propagate(as(eq,"FLStock"),dim(srDev)[6])
  om      =fwd(om,fbar=fbar(eq)[,-1],
               sr=eq,residuals=srDev)
  om},f=f,srDev=srDev)


lfds=mdply(data.frame(stock=names(oms)), function(stock){
  
  om=window(oms[[stock]],start=2)
  
  if (any(any(catch.n(om)<0)))
    catch.n(om)[catch.n(om)<0]=0.0
  
  lfd=lenSample(catch.n(om),invAlks[[stock]],nsample=500)
  lfd=transform(melt(lfd),data=value)[,-4]
  lfd=subset(as.data.frame(lfd,drop=TRUE),data>0)
  
  lfd})

dat=transform(lfds,lopt=laply(lhs,function(x) x["lopt"])[stock])
inds=ddply(dat,
           .(stock,year,iter), with,
                lenInd(len,data,lopt[1]))
ind2=subset(inds[,-6],year%in%70:100)
ind2=transform(ind2,overfished=!(as.numeric(year)%in%90:105))
ind2=melt(ind2[,-2],id=c("stock","iter","overfished"))
ind2=ddply(ind2,.(stock,variable),with, roc(overfished,value))

ind.=rbind(cbind(sel="flat",ind2),
           cbind(sel="Maturity",ind))
```



\newpage
\blandscape

```{r, echo=FALSE, fig.height=8, fig.width=12, eval=FALSE}
dat=ddply(subset(lfds,year%in%c(40,100,130)&iter==2),.(stock,year), transform,
          len =len/max(len))
ggplot(dat)+    
  geom_histogram(aes(len,weight=data),binwidth=.05)+
  #geom_vline(aes(xintercept=value,col=variable),data=melt(rln,id="year"))+
  facet_grid(year~stock,scale="free")+
  xlab("Relative Length")+ylab("")+
  scale_color_manual("Indicator",values=rainbow(4))
```

**Figure `r iFig=iFig+1; iFig`.** Simulated length frequencies distributions with indicators.

\elandscape

```{r, echo=FALSE, eval=FALSE}
ggplot(ind.)+ 
  geom_line(aes(FPR,TPR,linetype=sel,col=variable))+
  geom_line(aes(x,y),data.frame(x=seq(0,1,0.01),y=seq(0,1,0.01)))+
  xlab("False Negative Rate")+ylab("True Positive Rate")+
  #scale_color_manual("Indicator",values=rainbow(5))+
  theme_bw(12)+
  theme(legend.position="bottom")+
  facet_wrap(~stock,ncol=2)
```
**Figure `r iFig=iFig+1; iFig`.**

```{r, eval=FALSE}
ind2=subset(inds[,-6],year%in%105:114)
ind2=transform(ind2,overfished=(as.numeric(year)%in%110:114))
ind2=melt(ind2[,-2],id=c("stock","iter","overfished"))
ind2=ddply(ind2,.(stock,variable),with, roc(overfished,value))

ind.=rbind(cbind(sel="flat",ind2),
           cbind(sel="Maturity",ind))

ggplot(ind.)+ 
  geom_line(aes(FPR,TPR,linetype=sel,col=variable))+
  geom_line(aes(x,y),data.frame(x=seq(0,1,0.01),y=seq(0,1,0.01)))+
  xlab("False Negative Rate")+ylab("True Positive Rate")+
  #scale_color_manual("Indicator",values=rainbow(5))+
  theme_bw(12)+
  theme(legend.position="bottom")+
  facet_wrap(~stock,ncol=2)
```
**Figure `r iFig=iFig+1; iFig`.**


```{r}
inds=mdply(dimnames(design)[[1]][1:29], function(x) {
  load(paste("/home/laurence/Desktop/sea++/mydas/project/papers/ROC/data/sims/catch/ind",x,"RData",sep="."))
  ind=subset(ind[,-5],year%in%70:100)
  ind=transform(ind,overfished=!(as.numeric(year)%in%90:100))
  ind=melt(ind[,-1],id=c("iter","overfished"))
  ind=ddply(ind,.(variable),with, mydas:::roc(overfished,value))
  
  cbind(scen=x,ind)})[,-1]

indc=cbind(Fisheries="Independent",design[inds$scen,],inds)

inds=mdply(dimnames(design)[[1]][1:29], function(x) {
  load(paste("/home/laurence/Desktop/sea++/mydas/project/papers/ROC/data/sims/stock/ind",x,"RData",sep="."))
  ind=subset(ind[,-5],year%in%70:100)
  ind=transform(ind,overfished=!(as.numeric(year)%in%90:100))
  ind=melt(ind[,-1],id=c("iter","overfished"))
  ind=ddply(ind,.(variable),with, mydas:::roc(overfished,value))
  
  cbind(scen=x,ind)})[,-1]

inds=cbind(Fisheries="Dependent",design[inds$scen,],inds)

inds=rbind(inds,indc)
rm(indc)
```

```{r}
ggplot(subset(inds,Stock="Psetta maxima"&CV==0.3&Fisheries=="Independent"))+
  geom_path(aes(FPR,TPR,col=ac(s)))+
  geom_line(aes(x,y),data=data.frame(x=0:1,y=0:1))+
  facet_grid(variable~Fisheries)+
  scale_color_manual("Steepness",values=c("red","blue"))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Turbot example.

```{r}
ggplot(subset(inds,Stock="Psetta maxima"&CV==0.3))+
  geom_path(aes(FPR,TPR,col=ac(s)))+
  geom_line(aes(x,y),data=data.frame(x=0:1,y=0:1))+
  facet_grid(variable~Fisheries)+
  scale_color_manual("Steepness",values=c("red","blue"))+
  theme_bw()
```


```{r, eval=FALSE}
lbs=mdply(seq(dim(design)[1])[-c(22,30,65,70,73,76,79,82:105)], function(x) {
  load(paste("/home/laurence/Desktop/sea++/mydas/project/papers/ROC/data/sims/lb",x,"RData",sep="."))
  ind=as.data.frame(lb[["fm"]],drop=T)
  ind=subset(ind,year%in%70:100)
  ind=transform(ind,overfished=!(as.numeric(year)%in%90:100))
  ind=melt(ind,id=c("iter","year","overfished"))
  ind=ddply(ind,.(variable),with, mydas:::roc(overfished,value))
  
  cbind(sen=x,ind)})[,-1]

inds=cbind(design[as.character(inds$sen),],inds)

rows=dimnames(subset(design,Stock=="Psetta maxima"))[[1]]

inds=mdply(data.frame(i=rows,stringsAsFactors=FALSE),  function(i) {
  fl=paste("/home/laurence/Desktop/sea++/mydas/project/papers/ROC/data/sims/catch/ind",i,"RData",sep=".")
  if (!file.exists(fl)) return(NULL)
  load(fl)
  ind=subset(ind[,-5],year%in%70:100)
  ind=transform(ind,overfished=!(as.numeric(year)%in%90:100))
  ind=melt(ind[,-1],id=c("iter","overfished"))
  ind=ddply(ind,.(variable),with, mydas:::roc(overfished,value))
  
  cbind(sen=i,ind)})[,-1]

inds=cbind(design[as.numeric(as.character(inds$sen)),],inds)

ggplot(subset(inds,variable!="pmega"))+
  geom_path(aes(FPR,TPR,group=sen,colour=as.character(s)))+
  geom_line(aes(x,y),data=data.frame(x=c(0,1),y=c(0,1)))+
  facet_wrap(~variable,ncol=2)+
  theme_bw()+
  theme(legend.position="bottom")+
  scale_colour_manual("Steepness",values=c("red","blue"))

ggplot(subset(inds,variable%in%c("lfm","lbar")))+
  geom_path(aes(FPR,TPR,group=sen,colour=as.character(variable)))+
  geom_line(aes(x,y),data=data.frame(x=c(0,1),y=c(0,1)))+
  facet_wrap(sel2~s,ncol=2)+
  theme_bw()+
  theme(legend.position="bottom")+
  scale_colour_manual("Indicator", values=c("red","blue"))

tab=ddply(inds,.(sen,variable), with, { 
  best=max(TPR*(1-FPR))==TPR*(1-FPR);   
  data.frame(TPR=TPR[best],FPR=FPR[best],reference=reference[best])})

ggplot(tab)+
         geom_histogram(aes(reference))+
         facet_wrap(~variable,scale="free",ncol=2)+
  theme_bw()+
  xlab("Decision Threshold")+xlab("Count")
```

\newpage 
# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
``` 

