---
title: "Selection of Stock Assessment Methods and Proxy Reference Points for use in Management Procedures"
subtitle: "Comparison of Proxies with MSY Reference Points"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

## Power of proxy reference points and indicators to detect overfishing

+ **Question:** What assumptions are the most important in i) determining stock dynamics and ii) the power of proxies reference points to detect stock status?  In particular    
  - Which potential indicators and proxy reference points are the most robust? i.e. have high power to detect overfishing; and  
  - What are the benefits of reducing uncertainty?
    
    
+ **Methods** Simulate a range of stock dynamics
   - Project for different levels of constant F relative to $F_{MSY}$ and summarise scenarios by clustering on the
      - Expected dynamics i.e. reference points and proxies; and  
      - Time series, i.e. frequency spectrum
   - Run scenarios with an increasing trend in F that leads to overfishing, then implement a recovery plan that brings fishing to the $F_{MSY}$ level then screen potential empirical MPs by
  - Generating length, catch and CPUE indicators using an OEM
  - Compare indicators to OM, both trends and status relative to reference points using Reciever Operating Characteristics (ROCs)
  - Compare to model based indicators by fitting indices using LBSPR, SRA and a biomass dynamic model then evaluate using ROC and compare with empirical indicators

## MP tuning    

+ **Methods** Run scenarios with an increasing trend in F that leads to overfishing, then implement a recovery plan that brings fishing to the $F_{MSY}$ level then screen potential empirical MPs by
  - Generating length, catch and CPUE indicators using an OEM
  - Fit indices using LBSPR, SRA and a biomass dynamic model
  - Compare indicators to OM, both trends and status relative to reference points using Reciever Operating Characteristics (ROCs)

+ **Analysis**  Compare indicators to OM, both trends and status relative to reference points using Reciever Operating Characteristics (ROCs)
  - Calculate MSY reference points and proxies
  - Generate indicators relative to reference points
  - Evaluate the power of the various indicators to detect stock status using Reciever Operating Characteristics
    
+ Receiver Operating Characteristics for parameter tuning
  - Chose best HCR parameters
  - Run MSE

## Prediction Skill

+ Screen model based MPs
  - Perform 1,2,3, step ahead projections using LBSPR, SRA and a biomass dynamic model
  - Use MASE to identify assessment models with prediction skill

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="tex/",
               cache.path="cache/")

iFig=0
iTab=0
```
```{r, pkgs} 
library(FLCore)
library(FLBRP)
library(FLasher)
library(FLife)
library(mydas)
library(popbio)

library(ggplotFL)
library(scales)
library(plyr)
library(dplyr)
library(reshape)
library(grid)
library(reshape)
library(popbio)
library(magrittr)
library(broom)
library(GGally)
```

```{r, parallel, eval=FALSE}
library(doParallel)
library(foreach)

cl=makeCluster(3)
registerDoParallel(cl)
```

```{r, funcs}
refcase<-function(params,f,srDev,
                  burn=20,
                  m="gislason",
                  fbar=srDev%=%1){

  ##set up equilibrium object
  if ("numeric"%in%is(f))
    f=FLPar(f=array(f,c(1,length(f))))
    
  ## need to add interactions for f and par
  if (dim(params)[2]>1&dim(f)[2]>1){
    npar=dim(params)[2]
    params=as(mdply(seq(dim(f)[2]), with, 
                    cbind(model.frame(params)))[,-c(1,dim(params)[1]+2)],"FLPar")
    f  =rep(c(f),each=npar)
    f  =FLPar(array(f,c(1,length(f))))
    }
  
  eql=lhEql(params,m=m)
  
  ## convert to FLStock with constant F
  eq=eql

  fbar(eq)=fbar
  mlt=FLPar(f=array(c(f)*c(eq@refpts["msy","harvest"]),
                         c(1,length(c(f)*c(eq@refpts["msy","harvest"])))))
  fbar(eq)=fbar(eq)%*%mlt
  
  stk=fwd(as(eq,"FLStock"),fbar=fbar(eq)[,-1],
          sr=eq,residuals=srDev)
  
  ## Summary stats
  srr=model.frame(FLQuants(eql,"ssb"=ssb,"rec"=rec),drop=TRUE)
  srp=model.frame(FLQuants("rp"=setPlusGroup(stock.n(eq)[,1]*stock.wt(eq)[,1]*eq@mat[,1],12)),drop=T)
  ts =model.frame(FLQuants(stk,"ssb"=ssb,"biomass"=stock,"rec"=rec,"catch"=catch,
                               "dev"=function(x) propagate(srDev,dim(x)[6])),drop=T)
  
  ts=subset(ts,year>burn)
  ts$year=ts$year-burn

  ind=omSmry(stk,eql,params)

  key=cbind(model.frame(params),f=c(f))
  
  list(srr=srr,srp=srp,ts=ts,ind=ind,key=key)}
```

```{r, refcase, eval=FALSE}
par=propagate(lhPar(FLPar(linf=100,s=.9)),16)
dat=expand.grid(bg=c(3,3.1),sel3=c(5000,5),s=c(0.75,0.9),k=c(0.1653,0.1653*2))

par["bg"]  =dat$bg
par["sel3"]=dat$sel3
par["s" ]  =dat$s
par["k" ]  =dat$k

f  =FLPar(f=array(c(0.1,1,3),c(1,3)))

set.seed(234)
srDev=rlnoise(1,FLQuant(0,dimnames=list(year=1:1021)),0.3,0)
gis.1=refcase(par,f,srDev)
m2.1 =refcase(par,f,srDev,m=function(...) 0.2)

set.seed(234)
srDev=rlnoise(1,FLQuant(0,dimnames=list(year=1:1021)),0.3,0.6)
gis.2=refcase(par,f,srDev)
m2.2 =refcase(par,f,srDev,m=function(...) 0.2)

set.seed(234)
srDev=rlnoise(1,FLQuant(0,dimnames=list(year=1:1021)),0.5)
gis.3=refcase(par,f,srDev)
m2.3 =refcase(par,f,srDev,m=function(...) 0.2)

ts=rbind(
  cbind(CV=0.3,AR=0.0,deviates="0.3",M="Gislason",merge(gis.1$key,gis.1$ts,by="iter")),
  cbind(CV=0.3,AR=0.0,deviates="0.3",M="0.2",     merge( m2.1$key, m2.1$ts,by="iter")),
  cbind(CV=0.3,AR=0.6,deviates="0.3",M="Gislason",merge(gis.2$key,gis.2$ts,by="iter")),
  cbind(CV=0.3,AR=0.6,deviates="0.3",M="0.2",     merge( m2.2$key, m2.2$ts,by="iter")),
  cbind(CV=0.5,AR=0.0,deviates="0.3",M="Gislason",merge(gis.3$key,gis.3$ts,by="iter")),
  cbind(CV=0.5,AR=0.0,deviates="0.3",M="0.2",     merge( m2.3$key, m2.3$ts,by="iter")))

srr=rbind(
  cbind(CV=0.3,AR=0.0,deviates="0.3",M="Gislason",merge(gis.1$key,gis.1$srr,by="iter")),
  cbind(CV=0.3,AR=0.0,deviates="0.3",M="0.2",     merge( m2.1$key, m2.1$srr,by="iter")),
  cbind(CV=0.3,AR=0.6,deviates="0.3",M="Gislason",merge(gis.2$key,gis.2$srr,by="iter")),
  cbind(CV=0.3,AR=0.6,deviates="0.3",M="0.2",     merge( m2.2$key, m2.2$srr,by="iter")),
  cbind(CV=0.5,AR=0.0,deviates="0.3",M="Gislason",merge(gis.3$key,gis.3$srr,by="iter")),
  cbind(CV=0.5,AR=0.0,deviates="0.3",M="0.2",     merge( m2.3$key, m2.3$srr,by="iter")))

srp=rbind(
  cbind(CV=0.3,AR=0.0,deviates="0.3",M="Gislason",merge(gis.1$key,gis.1$srp,by="iter")),
  cbind(CV=0.3,AR=0.0,deviates="0.3",M="0.2",     merge( m2.1$key, m2.1$srp,by="iter")),
  cbind(CV=0.3,AR=0.6,deviates="0.3",M="Gislason",merge(gis.2$key,gis.2$srp,by="iter")),
  cbind(CV=0.3,AR=0.6,deviates="0.3",M="0.2",     merge( m2.2$key, m2.2$srp,by="iter")),
  cbind(CV=0.5,AR=0.0,deviates="0.3",M="Gislason",merge(gis.3$key,gis.3$srp,by="iter")),
  cbind(CV=0.5,AR=0.0,deviates="0.3",M="0.2",     merge( m2.3$key, m2.3$srp,by="iter")))

ind=rbind(
  cbind(CV=0.3,AR=0.0,deviates="0.3",M="Gislason",merge(gis.1$ind,gis.1$srp,by="iter")),
  cbind(CV=0.3,AR=0.0,deviates="0.3",M="0.2",     merge( m2.1$ind, m2.1$srp,by="iter")),
  cbind(CV=0.3,AR=0.6,deviates="0.3",M="Gislason",merge(gis.2$ind,gis.2$srp,by="iter")),
  cbind(CV=0.3,AR=0.6,deviates="0.3",M="0.2",     merge( m2.2$ind, m2.2$srp,by="iter")),
  cbind(CV=0.5,AR=0.0,deviates="0.3",M="Gislason",merge(gis.3$ind,gis.3$srp,by="iter")),
  cbind(CV=0.5,AR=0.0,deviates="0.3",M="0.2",     merge( m2.3$ind, m2.3$srp,by="iter")))

gis.prior=priors(par)
m2.prior =priors(par,eq=lhEql(par,m=function(...) 0.2))

prior=rbind(
  cbind("M"="0.2",      model.frame(gis.prior)),
  cbind("M"="Gislason", model.frame( m2.prior)))

flag=c(par["bg"])==3
bg  =lhEql(par)
refpts(bg)=refpts(bg)["virgin"]
rfs=refpts(bg)
stock.wt(bg)[,,,,,!flag]=stock.wt(bg)[,,,,,flag]
adj=1000/c(computeRefpts(bg)[,"ssb",])

refcase=list(ts=ts,srr=srr,srp=srp,ind=ind,key=gis.1$key,params=par,
             priors=prior,msyCorrect=adj)

save(refcase,
     file=file.path("/home/laurence/Desktop/sea++/mydas/project/papers/mase/data","refcase.RData"),
     compress="xz")
```

# Figures

## MSY reference points and proxies

```{r, lifeHistory}
load("/home/laurence/Desktop/sea++/mydas/project/papers/mase/data/refcase.RData")

priors=transform(refcase[["priors"]],msy=msy*c(refcase$msyCorrect,2))   

ggpairs(model.frame(priors[,c("msy","fmsy","bmsy","r","rc")]),
        #mapping = ggplot2::aes(color=as.character(sel3)),
        lower = list(continuous = wrap(mydas:::my_smooth)),
        diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
        title = "")+
  theme(legend.position ="none",
        panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.x      =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))+
  theme_bw(16)
```


**Figure `r iFig=iFig+1; iFig`.**  Relationship between MSY reference points and population growth rate.


```{r, proxies}
ggpairs(priors[,c("lopt","clmsy","slmsy","mk","fm","spr0","msy","fmsy","bmsy")],
        lower = list(continuous = wrap(mydas:::my_smooth)),
        diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),  
        title = "")+
  theme(legend.position ="none",
        panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.x      =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))+
  theme_bw(16)
```

**Figure `r iFig=iFig+1; iFig`.** Relationship between MSY reference points and their potential proxies.

# Time Series

## AR model.

Spectral density of SSB from a fitted AR model.

```{r}
load("/home/laurence/Desktop/sea++/mydas/project/papers/mase/data/refcase.RData")

ssb=ddply(refcase$ts, .(f,k,M,s,bg,sel3,CV,AR,deviates), with,
          as.data.frame(spec.ar(ssb/mean(ssb),plot=FALSE)[c("freq","spec")]))
ssb=ddply(ssb,       .(f,k,M,s,bg,sel3,CV,AR,deviates), transform,
          spc=spec/max(spec),
          wavelen=1/freq)

ggplot(subset(ssb,wavelen<=100))+
  geom_line(aes(wavelen,spc,col=as.character(f),group=paste(AR,f,sel3),
                linetype=as.character(sel3)))+
  xlab("Wave Length")+ylab("")+
  facet_grid(M*s*CV~bg*k)
```

**Figure `r iFig=iFig+1; iFig`.** 

```{r, eval=FALSE}
dt1=cast(ssb,f+k+M+s+bg+sel3+CV+AR+deviates~wavelen,value="spc")

points.matrix=scale(dt1[,10:70])
kclusts <- data.frame(k=4:25) %>% 
  group_by(k) %>% 
  do(kclust=kmeans(points.matrix, .$k, nstart=20,  iter.max=20))

clusters    <- kclusts %>% group_by(k) %>% do(tidy(.$kclust[[1]]))
assignments <- kclusts %>% group_by(k) %>% do(augment(.$kclust[[1]], points.matrix))
clusterings <- kclusts %>% group_by(k) %>% do(glance(.$kclust[[1]]))

ggplot(clusterings, aes(k, tot.withinss)) + 
  geom_line()+
  xlab("Number of Clusters")+ylab("Within SS")+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Identification of the number of clusters, i.e. 10


```{r, eval=FALSE}
dt2=ddply(assignments[,c(1,514)], .(k), with,
             data.frame(ncluster=k,cluster=.cluster,dat))

ggplot(subset(dt2,ncluster%in%seq(4,12,2)), aes(wavelen, spec))+  
  geom_point()+
  facet_grid(cluster~ncluster,scale="free")+ 
  theme_bw()+
  theme(legend.position="none")+
  xlab("Wave Length")+ylab("")
```

**Figure `r iFig=iFig+1; iFig`.** Clusters


```{r, eval=FALSE}
dt3=ddply(subset(dt2,ncluster==10),.(cluster,wavelen), with, data.frame(spec=mean(spec)))

ggplot(dt3, aes(wavelen, spec))+  
  geom_point()+
  facet_grid(cluster~.,scale="free")+ 
  theme_bw()+
  theme(legend.position="none")+
  xlab("Wave Length")+ylab("")
  
```

**Figure `r iFig=iFig+1; iFig`.** Mean spectra by cluster.

```{r, eval=FALSE}
save(assignments,clusterings,dat,dt2,dt3,file="/home/laurence/tmp/tmp.RData")
```

```{r, eval=FALSE}
cls10=unlist(c(subset(assignments,k==10)[,".cluster"]))
dt4  =cbind(refcase$ts,cluster=rep(cls10,each=dim(refcase$ts)[1]/288))

dt4=ddply(dt4,.(f,k,M,s,bg,sel3,CV,AR,deviates,cluster), transform, ssb.=scale(ssb))

ggplot(subset(dt4,year%in%501:600), aes(year, ssb.))+  
  geom_point(size=0.2)+
  geom_smooth(aes(year, ssb.,group=cluster),se=F,span=.1)+
  facet_grid(cluster~.,scale="free")+ 
  theme_bw()+
  theme(legend.position="none")+
  xlab("SSB")+ylab("Year")
  
```


## Fourier Transformations

Fit a fast Fourier transform to SSB, then cluster them to find how many different sets of dynamics exist.  

```{r, eval=FALSE}
dat=ddply(refcase$ts, .(f,k,M,s,bg,sel3,CV,AR,deviates), with, 
          as.data.frame(spec.pgram(ssb/mean(ssb),demean=TRUE,
                                   taper=0,log="no",plot=FALSE)[c("freq","spec")]))
dat=transform(dat,wavelen=1/freq)

ggplot(dat)+
  geom_point(aes(wavelen,spec,col=as.character(f),
                 group=paste(AR,f,sel3),shape=as.character(sel3)))+
  xlab("Wave Length")+ylab("")+
  facet_grid(M*s*CV~bg*k,scale="free")
```

**Figure `r iFig=iFig+1; iFig`.** Results from Fourier transforms


```{r, eval=FALSE}
dt1=cast(dat,f+k+M+s+bg+sel3+CV+AR+deviates~wavelen,value="spec")

points.matrix=scale(dt1[,-seq(9)])
kclusts <- data.frame(k=4:25) %>% 
  group_by(k) %>% 
  do(kclust=kmeans(points.matrix, .$k, nstart=10,  iter.max=20))

clusters    <- kclusts %>% group_by(k) %>% do(tidy(.$kclust[[1]]))
assignments <- kclusts %>% group_by(k) %>% do(augment(.$kclust[[1]], points.matrix))
clusterings <- kclusts %>% group_by(k) %>% do(glance(.$kclust[[1]]))

ggplot(clusterings, aes(k, tot.withinss)) + 
  geom_line()+
  xlab("Number of Clusters")+ylab("Within SS")+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Identification of the number of clusters, i.e. 10

```{r, eval=FALSE}
dt2=ddply(assignments[,c(1,514)], .(k), with,
             data.frame(ncluster=k,cluster=.cluster,dat))

ggplot(subset(dt2,ncluster%in%seq(4,12,2)), aes(wavelen, spec))+  
  geom_point()+
  facet_grid(cluster~ncluster,scale="free")+ 
  theme_bw()+
  theme(legend.position="none")+
  xlab("Wave Length")+ylab("")
```

**Figure `r iFig=iFig+1; iFig`.** Clusters


```{r, eval=FALSE}
dt3=ddply(subset(dt2,ncluster==10),.(cluster,wavelen), with, data.frame(spec=mean(spec)))

ggplot(dt3, aes(wavelen, spec))+  
  geom_point()+
  facet_grid(cluster~.,scale="free")+ 
  theme_bw()+
  theme(legend.position="none")+
  xlab("Wave Length")+ylab("")
  
```

**Figure `r iFig=iFig+1; iFig`.** Mean spectra by cluster.

```{r, eval=FALSE}
save(assignments,clusterings,dat,dt2,dt3,file="/home/laurence/tmp/tmp.RData")
```

```{r, eval=FALSE}
cls10=unlist(c(subset(assignments,k==10)[,".cluster"]))
dt4  =cbind(refcase$ts,cluster=rep(cls10,each=dim(refcase$ts)[1]/288))

dt4=ddply(dt4,.(f,k,M,s,bg,sel3,CV,AR,deviates,cluster), transform, ssb.=scale(ssb))

ggplot(subset(dt4,year%in%501:600), aes(year, ssb.))+  
  geom_point(size=0.2)+
  geom_smooth(aes(year, ssb.,group=cluster),se=F,span=.1)+
  facet_grid(cluster~.,scale="free")+ 
  theme_bw()+
  theme(legend.position="none")+
  xlab("SSB")+ylab("Year")
  
```


# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
```


