---
title: "Stock Assessment Methods and Proxy $MSY$ Reference Points for data limited stocks"
subtitle: "Power of indicators to detect stock status"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

For data poor stocks ICES currently uses MSY proxy reference points as part of a Precautionary Approach to provide advice on the status of the stock and exploitation. 

**Category 3:** stocks are those for which survey-based assessments indicate trends. This  includes  stocks  for  which  survey  indices  (or  other  indicators  of  stock  size  such  as  reliable  fishery-dependent  indices,  e.g. lpue,  cpue,  and  mean  length  in  the  catch)  are  available. While **Category 4:** stocks are those for which only reliable catch data are available 

There are four methods currently approved by ICES for calculation of MSY reference points for category 3 and 4 stocks, namely 

+ Length based indicators 
+ Mean length Z 
+ Length based spawner per recruit; and
+ Surplus Production models

Many approaches to estimation for data-poor fisheries have emerged over the last few decades for example where length data are available methods include Length Based Spawning Potential Ratio (LBSPR), Length-Based Integrated Mixed Effects (LIME), and Length-Based Bayesian (LBB); wWhile where only catch data are available methods include Catch-Maximum Sustainable Yield (Catch-MSY), State-Space Catch-Only Model (SSCOM), Depletion Based Stock Reduhction Analysis (DBSRA), and Simple Stock Synthesis (SSS) an extension of Catch-MSY (CMSY).

In addition there are a number of empirical indicators and reference points that can be used to monitor stock status and trends, **indicators** include

+ $L_{max5\%}$ mean length of largest 5\%
+ $L_{95\%}$ $95^{th}$ percentile
+ $P_{mega}$ Proportion of individuals above $L_{opt} + 10\%$
+ $L_{25\%}$ $25^{th}$ percentile of length distribution
+ $L_{c}$ Length at $50\%$ of modal abundance
+ $L_{mean}$ Mean length of individuals $> L_c$
+ $L_{max_{y}}$ Length class with maximum biomass in catch
+ $L_{mean}$ Meanlength of individuals $> L$

and potential  **reference points** including

+ $L_{opt} = L_{\infty}\frac{3}{3+\frac{M}{K}}$, assuming $M/K = 1.5$ gives $\frac{2}{3}L_{\infty}$
+ $L_{F=M} =  0,75l_c+0.25l_{\infty}$

## MP tuning    

+ **Methods** Run scenarios with an increasing trend in F that leads to overfishing, then implement a recovery plan that brings fishing to the $F_{MSY}$ level then screen potential empirical MPs by
  - Generating length, catch and CPUE indicators using an OEM
  - Fit indices using LBSPR, SRA and a biomass dynamic model
  - Compare indicators to OM, both trends and status relative to reference points using Reciever Operating Characteristics (ROCs)

+ **Analysis**  Compare indicators to OM, both trends and status relative to reference points using Reciever Operating Characteristics (ROCs)
  - Calculate MSY reference points and proxies
  - Generate indicators relative to reference points
  - Evaluate the power of the various indicators to detect stock status using Reciever Operating Characteristics
    
+ Receiver Operating Characteristics for parameter tuning
  - Chose best HCR parameters
  - Run MSE

## Prediction Skill

+ Screen model based MPs
  - Perform 1,2,3, step ahead projections using LBSPR, SRA and a biomass dynamic model
  - Use MASE to identify assessment models with prediction skill

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="tex/indicators",
               cache.path="cache/indicators")

iFig=0
iTab=0
```
```{r, pkgs} 
library(FLCore)
library(FLBRP)
library(FLasher)
library(FLife)
library(mydas)
library(popbio)

library(ggplotFL)
library(scales)
library(plyr)
library(dplyr)
library(grid)
library(reshape)
library(popbio)
library(magrittr)
library(broom)
library(GGally)
library(spatstat)
```

```{r, parallel, eval=FALSE}
library(doParallel)
library(foreach)

cl=makeCluster(3)
registerDoParallel(cl)
```

```{r, params}
par=propagate(lhPar(FLPar(linf=100,s=.9)),16)
dat=expand.grid(bg=c(3,3.1),sel3=c(5000,5),s=c(0.75,0.9),k=c(0.1653,0.1653*2))

par["bg"]  =dat$bg
par["sel3"]=dat$sel3
par["s" ]  =dat$s
par["k" ]  =dat$k

fbar=FLQuant(c(rep(0.1,60),seq(0.1,2,length.out=40)[-40],
               seq(2,1,length.out=11),rep(1,20)))

set.seed(234)
srDev1=rlnoise(500,fbar%=%0,0.3,0)
set.seed(234)
srDev2=rlnoise(500,fbar%=%0,0.3,0.6)
set.seed(234)
srDev3=rlnoise(500,fbar%=%0,0.5)
```

```{r, indicators, eval=FALSE}
foreach(i=seq(dim(par)[2][c(14,16)]),
         .packages =c("reshape","plyr","FLCore","FLBRP","FLasher","FLife",
                      "mydas","popbio"),
         .export = c("srDev1","par","fbar") #ls(globalenv())
        ) %dopar% {

  ## Run and combine indicators
  
#for (i in seq(dim(par)[2])){
  gis.1=mydas:::indicators(iter(par,i),fbar=fbar,srDev=srDev1)
  m2.1 =mydas:::indicators(iter(par,i),fbar=fbar,srDev=srDev1,m=function(...) 0.2)
  
  gis.2=indicators(iter(par,i),fbar=fbar,srDev=srDev2)
  m2.2 =indicators(iter(par,i),fbar=fbar,srDev=srDev2,m=function(...) 0.2)
  
  gis.3=indicators(iter(par,i),fbar=fbar,srDev=srDev3)
  m2.3 =indicators(iter(par,i),fbar=fbar,srDev=srDev3,m=function(...) 0.2)
  
  ind=rbind(
    cbind(CV=0.3,AR=0.0,"i"=i,M="Gislason",gis.1$ind),
    cbind(CV=0.3,AR=0.0,"i"=i,M="0.2",      m2.1$ind),
    cbind(CV=0.3,AR=0.6,i=i,M="Gislason",gis.2$ind),
    cbind(CV=0.3,AR=0.6,i=i,M="0.2",      m2.2$ind),
    cbind(CV=0.5,AR=0.0,i=i,M="Gislason",gis.3$ind),
    cbind(CV=0.5,AR=0.0,i=i,M="0.2",      m2.3$ind))
  
  refs=rbind(
    cbind(CV=0.3,AR=0.0,i=i,M="Gislason",gis.1$refs),
    cbind(CV=0.3,AR=0.0,i=i,M="0.2",      m2.1$refs),
    cbind(CV=0.3,AR=0.6,i=i,M="Gislason",gis.2$refs),
    cbind(CV=0.3,AR=0.6,i=i,M="0.2",      m2.2$refs),
    cbind(CV=0.5,AR=0.0,i=i,M="Gislason",gis.3$refs),
    cbind(CV=0.5,AR=0.0,i=i,M="0.2",      m2.3$refs))
  
  lens=rbind(
    cbind(CV=0.3,AR=0.0,M="Gislason",i=i,
                      model.frame(FLQuants(gis.1[c("ctn","cln")]))[,c(1:2,6:8)]),
    cbind(CV=0.3,AR=0.0,M="0.2",     i=i,
                      model.frame(FLQuants( m2.1[c("ctn","cln")]))[,c(1:2,6:8)]),
    cbind(CV=0.3,AR=0.6,M="Gislason",i=i,
                      model.frame(FLQuants(gis.1[c("ctn","cln")]))[,c(1:2,6:8)]),
    cbind(CV=0.3,AR=0.6,M="0.2",     i=i,
                      model.frame(FLQuants( m2.1[c("ctn","cln")]))[,c(1:2,6:8)]),
    cbind(CV=0.5,AR=0.0,M="Gislason",i=i,
                      model.frame(FLQuants(gis.1[c("ctn","cln")]))[,c(1:2,6:8)]),
    cbind(CV=0.5,AR=0.0,M="0.2",     i=i,
                      model.frame(FLQuants( m2.1[c("ctn","cln")]))[,c(1:2,6:8)]))
  
  save(ind,refs,lens,
     file=file.path("/home/laurence/Desktop/sea++/mydas/project/papers/mase/data/iters",
                    paste(i,".RData",sep="")),
      compress="xz")
  }
```

```{r, adj, eval=FALSE}
## adjust for bg>3 #########################################
# calculate virgin SSB for bg=3 and 3.1 then adjust MSY 
flag=c(par["bg"])==3
bg  =lhEql(par)
refpts(bg)=refpts(bg)["virgin"]
rfs=refpts(bg)
stock.wt(bg)[,,,,,!flag]=stock.wt(bg)[,,,,,flag]
adj=data.frame(M   ="Gislason",
               iter=model.frame(par)[,"iter"],
               adj =1000/c(computeRefpts(bg)[,"ssb",]))

bg  =lhEql(par,m=function(...) 0.2)
refpts(bg)=refpts(bg)["virgin"]
rfs=refpts(bg)
stock.wt(bg)[,,,,,!flag]=stock.wt(bg)[,,,,,flag]
msyAdj=rbind(adj,
          data.frame(M   ="0.2",
               iter=model.frame(par)[,"iter"],
               adj =1000/c(computeRefpts(bg)[,"ssb",])))
```


```{r, combine, eval=FALSE}
load(file.path("/home/laurence/Desktop/sea++/mydas/project/papers/mase/data/iters",
                 paste(1,".RData",sep="")))

refs$lfm=0.75*refs$lc+0.25*refs$linf
  
allInd=ind  
allref=refs
allCtc=lens

for (i in seq(16)[-1]){
  load(file.path("/home/laurence/Desktop/sea++/mydas/project/papers/mase/data/iters",
                 paste(i,".RData",sep="")))

  refs$lfm=0.75*refs$lc+0.25*refs$linf
  allInd=rbind(allInd,ind) 
  allref=rbind(allref,refs) 
  allCtc=rbind(allCtc,lens)
  }

ind=allInd
ref=allref
ctc=allCtc

save(ind,ref,ctc,adj,file="/home/laurence/Desktop/sea++/mydas/project/papers/mase/data/indCat34.RData",compress="xz")
```

```{r, eval=FALSE}
source('~/Desktop/sea++/mydas/pkg/R/indicators.R')
source('~/Desktop/sea++/mydas/pkg/R/oemLn.R')

library(spatstat)

## Matrix with P(len) by age for each set of params
agLs=alk(par)

i=1
load(file.path("/home/laurence/Desktop/sea++/mydas/project/papers/mase/data/iters",
                 paste(i,".RData",sep="")))

refs$lfm=0.75*refs$lc+0.25*refs$linf
  
## FLQuant with catch-at-age
object=FLQuants(dlply(lens,.(CV,AR,M), with, 
               as.FLQuant(data.frame(age=age,year=year,data=ctn,iter=iter))))

## Simulate length frequencies by year
agLs=alk(par)
lfd=lenSample(object[[i]],iter(agLs,i),nsample=500)
lfd=subset(as.data.frame(lfd),data>0)

inds=ddply(lfd, .(year,iter), with, lenInd(len,data,lopt=refs[1,"lopt"]))

refs$lfm=0.75*refs$lc+0.25*refs$linf

rfs=FLQuants(
  clmsy=as.FLQuant(transmute(ind, year=year,iter=iter,data=cln/refs[i,"clmsy"])),
  slmsy=as.FLQuant(transmute(ind, year=year,iter=iter,data=sln/refs[i,"slmsy"])),
  clfm =as.FLQuant(transmute(ind, year=year,iter=iter,data=cln/refs[i,"lfm"])),
  slfm =as.FLQuant(transmute(ind, year=year,iter=iter,data=sln/refs[i,"lfm"])),
  pmega=as.FLQuant(transmute(inds,year=year,iter=iter,data=pmega)),
  l95  =as.FLQuant(transmute(inds,year=year,iter=iter,data=l95/par["linf",1])),
  l25  =as.FLQuant(transmute(inds,year=year,iter=iter,data=l25/par["linf",1])),
  f    =as.FLQuant(transmute(subset(ind,CV==0.3&AR==0&M==0.2&i==1&iter==1),
                           year=year,
                           data=fbar/msy_harvest)))


rln=ddply(subset(lfd,year%in%c(50,60,70,80)), .(year),
              with,lenInd(len,data,lopt=refs[i,"lopt"])[-5])

ggplot(subset(lfd,year%in%c(50,60,70,80)))+
  geom_histogram(aes(len,weight=data))+
  geom_vline(aes(xintercept=value,col=variable),data=melt(rln,id="year"))+
  facet_grid(year~.)+
  xlab("Length (cm)")+ylab("")

plot(rfs)+
  facet_grid(qname~.,scale="free")+
  geom_vline(aes(xintercept=x),data=data.frame(y="2FMSY",x=70),col="red")+
  geom_vline(aes(xintercept=x),data=data.frame(y="2FMSY",x=80),col="green")
```

```{r}
refs[c("l50","lopt","lfm","slmsy","clmsy")]

```

# Figures


**Figure `r iFig=iFig+1; iFig`.** Clusters

    

# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
```


