---
title: "MASE"
subtitle: "Turbot Base Case"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="../tex/base-",
               cache.path="cache/base/")

iFig=0
iTab=0
```
```{r, dir}  
dirOM ="/home/laurence/Desktop/sea++/mydas/project/tasks/task4/data"
dirRes="/home/laurence/Desktop/sea++/mydas/project/papers/mase/data"
```

```{r, pkgs}
library(ggplot2)
library(plyr)
library(dplyr)
library(reshape)

library(FLCore)
library(FLBRP)
library(FLasher)
library(ggplotFL)
library(FLife)
library(randtests)

library(mydas)
library(mpb)
```
```{r}
library(doParallel)
library(foreach)

cl=makeCluster(3)
registerDoParallel(cl)
```
```{r, turbot}
load(file.path(dirOM,"turbot-bd.RData"))

dpl =stock(bd,0.5)%/%params(bd)["k"]
dpl[,ac(c(22:52))]=NA

control(bd)["q1",2:4]=c(100,1000,10000)

sra=fit(bd,dpl)
```


\newpage
## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLasher:   `r packageVersion('FLasher')`
* FLife:     `r packageVersion('FLife')`
* ggplotFL:  `r packageVersion('ggplotFL')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
```
