---
title: "Selection of Stock Assessment Methods and Proxy Reference Points for use in Management Procedures"
subtitle: "Comparison of Proxies with MSY Reference Points"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

## Power of proxy reference points and indicators to detect overfishing

+ **Question:** What assumptions are the most important in i) determining stock dynamics and ii) the power of proxies reference points to detect stock status?  In particular    
  - Which potential indicators and proxy reference points are the most robust? i.e. have high power to detect overfishing; and  
  - What are the benefits of reducing uncertainty?
    
    
+ **Methods** Simulate a range of stock dynamics
   - Project for different levels of constant F relative to $F_{MSY}$ and summarise scenarios by clustering on the
      - Expected dynamics i.e. reference points and proxies; and  
      - Time series, i.e. frequency spectrum
   - Run scenarios with an increasing trend in F that leads to overfishing, then implement a recovery plan that brings fishing to the $F_{MSY}$ level then screen potential empirical MPs by
  - Generating length, catch and CPUE indicators using an OEM
  - Compare indicators to OM, both trends and status relative to reference points using Reciever Operating Characteristics (ROCs)
  - Compare to model based indicators by fitting indices using LBSPR, SRA and a biomass dynamic model then evaluate using ROC and compare with empirical indicators


## Prediction Skill

+ Screen model based MPs
  - Perform 1,2,3, step ahead projections using LBSPR, SRA and a biomass dynamic model
  - Use MASE to identify assessment models with prediction skill

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="tex/",
               cache.path="cache/")

iFig=0
iTab=0
```
```{r, pkgs} 
library(FLCore)
library(FLBRP)
library(FLasher)
library(FLife)
library(mydas)
library(popbio)

library(ggplotFL)
library(scales)
library(plyr)
library(dplyr)
library(reshape)
library(grid)
library(reshape)
library(popbio)
library(magrittr)
library(broom)
library(GGally)
```

```{r, parallel, eval=FALSE}
library(doParallel)
library(foreach)

cl=makeCluster(3)
registerDoParallel(cl)
```

```{r, funcs}
indicators<-function(params,
                     m   ="gislason",
                     f    =1,
                     srDev=FLQuant(rep(1,1021)),
                     fbar  =srDev%=%1){

  ##set up equilibrium object
  if ("numeric"%in%is(f))
    f=FLPar(f=array(f,c(1,length(f))))
    
  ## need to add interactions for f and par
  if (dim(params)[2]>1&dim(f)[2]>1){
    npar=dim(params)[2]
    params=as(mdply(seq(dim(f)[2]), with, 
                    cbind(model.frame(params)))[,-c(1,dim(params)[1]+2)],"FLPar")
    f  =rep(c(f),each=npar)
    f  =FLPar(array(f,c(1,length(f))))
    }
  
  eql=lhEql(params,m=m)
  
  ## convert to FLStock with constant F
  eq=eql

  fbar(eq)=fbar
  mlt=FLPar(f=array(c(f)*c(eq@refpts["msy","harvest"]),
                    c(1,length(c(f)*c(eq@refpts["msy","harvest"])))))
  fbar(eq)=fbar(eq)%*%mlt
  
  stk=fwd(as(eq,"FLStock"),fbar=fbar(eq)[,-1],
          sr=eq,residuals=srDev)
  
  ## Other stuff
  #srr=model.frame(FLQuants(eql,"ssb"=ssb,"rec"=rec),drop=TRUE)
  #srp=model.frame(FLQuants("rp"=setPlusGroup(stock.n(eq)[,1]*stock.wt(eq)[,1]*eq@mat[,1],12)),drop=T)
  #ts =model.frame(FLQuants(stk,"ssb"=ssb,"biomass"=stock,"rec"=rec,"catch"=catch,
  #                             "dev"=function(x) propagate(srDev,dim(x)[6])),drop=T)
  
  ## Summary stats
  ind=omSmry(stk,eql,params)
 
  refs=model.frame(priors(params,eq=lhEql(params,m=m)))
  
  key=cbind(model.frame(params),f=c(f))
  
  list(ind=ind,refs=refs,key=key,
       ctn=catch.n(stk),
       cln=exp(log(catch.wt(stk)%/%params["a"])%/%params["b"]))
       }
```

```{r, indicators, eval=FALSE}
## Run and combine indicators
source('~/Desktop/sea++/mydas/pkg/R/priors.R')
source('~/Desktop/sea++/mydas/pkg/R/omOut.R') 

par=propagate(lhPar(FLPar(linf=100,s=.9)),16)
dat=expand.grid(bg=c(3,3.1),sel3=c(5000,5),s=c(0.75,0.9),k=c(0.1653,0.1653*2))

par["bg"]  =dat$bg
par["sel3"]=dat$sel3
par["s" ]  =dat$s
par["k" ]  =dat$k

f  =FLPar(f=array(c(0.1,1,3),c(1,3)))

set.seed(234)
srDev=rlnoise(1,FLQuant(0,dimnames=list(year=1:1021)),0.3,0)
gis.1=indicators(par,f=f,srDev=srDev)
m2.1 =indicators(par,f=f,srDev=srDev,m=function(...) 0.2)

set.seed(234)
srDev=rlnoise(1,FLQuant(0,dimnames=list(year=1:1021)),0.3,0.6)
gis.2=indicators(par,f=f,srDev=srDev)
m2.2 =indicators(par,f=f,srDev=srDev,m=function(...) 0.2)

set.seed(234)
srDev=rlnoise(1,FLQuant(0,dimnames=list(year=1:1021)),0.5)
gis.3=indicators(par,f=f,srDev=srDev)
m2.3 =indicators(par,f=f,srDev=srDev,m=function(...) 0.2)

ind=rbind(
  cbind(CV=0.3,AR=0.0,M="Gislason",merge(gis.1$key,gis.1$ind,by="iter")),
  cbind(CV=0.3,AR=0.0,M="0.2",     merge( m2.1$key, m2.1$ind,by="iter")),
  cbind(CV=0.3,AR=0.6,M="Gislason",merge(gis.2$key,gis.2$ind,by="iter")),
  cbind(CV=0.3,AR=0.6,M="0.2",     merge( m2.2$key, m2.2$ind,by="iter")),
  cbind(CV=0.5,AR=0.0,M="Gislason",merge(gis.3$key,gis.3$ind,by="iter")),
  cbind(CV=0.5,AR=0.0,M="0.2",     merge( m2.3$key, m2.3$ind,by="iter")))

refs=rbind(
  cbind(CV=0.3,AR=0.0,M="Gislason",merge(gis.1$key[,c("iter","sel3","bg")],gis.1$refs,by="iter")),
  cbind(CV=0.3,AR=0.0,M="0.2",     merge( m2.1$key[,c("iter","sel3","bg")], m2.1$refs,by="iter")),
  cbind(CV=0.3,AR=0.6,M="Gislason",merge(gis.2$key[,c("iter","sel3","bg")],gis.2$refs,by="iter")),
  cbind(CV=0.3,AR=0.6,M="0.2",     merge( m2.2$key[,c("iter","sel3","bg")], m2.2$refs,by="iter")),
  cbind(CV=0.5,AR=0.0,M="Gislason",merge(gis.3$key[,c("iter","sel3","bg")],gis.3$refs,by="iter")),
  cbind(CV=0.5,AR=0.0,M="0.2",     merge( m2.3$key[,c("iter","sel3","bg")], m2.3$refs,by="iter")))

## adjust for bg>3 #########################################
# calculate virgin SSB for bg=3 and 3.1 then adjust MSY 
flag=c(par["bg"])==3
bg  =lhEql(par)
refpts(bg)=refpts(bg)["virgin"]
rfs=refpts(bg)
stock.wt(bg)[,,,,,!flag]=stock.wt(bg)[,,,,,flag]
adj=data.frame(M   ="Gislason",
               iter=model.frame(par)[,"iter"],
               adj =1000/c(computeRefpts(bg)[,"ssb",]))

bg  =lhEql(par,m=function(...) 0.2)
refpts(bg)=refpts(bg)["virgin"]
rfs=refpts(bg)
stock.wt(bg)[,,,,,!flag]=stock.wt(bg)[,,,,,flag]
adj=rbind(adj,
          data.frame(M   ="0.2",
               iter=model.frame(par)[,"iter"],
               adj =1000/c(computeRefpts(bg)[,"ssb",])))
refs=transform(merge(refs,adj,by=c("iter","M"),all.x=T),msy=msy*adj)
    
save(ind,refs,par,
   file=file.path("/home/laurence/Desktop/sea++/mydas/project/papers/mase/data","indicators.RData"),
     compress="xz")
```

# Figures

## MSY reference points and proxies

```{r, lifeHistory}
load("/home/laurence/Desktop/sea++/mydas/project/papers/mase/data/indicators.RData")

ggpairs(model.frame(refs[,c("msy","fmsy","bmsy","r","rc")]),
        #mapping = ggplot2::aes(color=as.character(sel3)),
        lower = list(continuous = wrap(mydas:::my_smooth)),
        diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
        title = "")+
  theme(legend.position ="none",
        panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.x      =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))+
  theme_bw(16)
```


**Figure `r iFig=iFig+1; iFig`.**  Relationship between MSY reference points and population growth rate.


```{r, proxies}
ggpairs(refs[,c("lopt","clmsy","slmsy","mk","fm","spr0","msy","fmsy","bmsy")],
        lower = list(continuous = wrap(mydas:::my_smooth)),
        diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),  
        title = "")+
  theme(legend.position ="none",
        panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.x      =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))+
  theme_bw(16)
```

**Figure `r iFig=iFig+1; iFig`.** Relationship between MSY reference points and their potential proxies.

```{r, len-indicators}
idx=transform(merge(ind,refs[,c("slmsy","clmsy","lopt","iter")]),
              sln=sln/slmsy,cln=cln/clmsy,
              sl50=sln/l50,cl50=cln/l50,
              slopt=sln/lopt,clopt=cln/lopt,
              fmsy=fbar/msy_harvest)[,
          c("f","CV","AR","M","s","k","bg","sel3","fmsy",
            "sln","cln","sl50","cl50","slopt","clopt")]

dat=melt(idx,id=c("f","CV","AR","M","s","k","bg","sel3","fmsy"))

ggplot(dat)+
  geom_boxplot(aes(ac(f),value))+
  geom_hline(aes(yintercept=1),col="red")+
  facet_wrap(~variable,ncol=2)+
  xlab("F times FMSY")+ylab("Ratio with FMSY")
```

# Time Series

## AR model.

Spectral density of SSB from a fitted AR model.

```{r, spec-dense}
load("/home/laurence/Desktop/sea++/mydas/project/papers/mase/data/refcase.RData")

key=0
idx=ddply(refcase$ts, .(f,k,M,s,bg,sel3,CV,AR), with, {
            key<<-key+1
            data.frame(ssb=scale(ssb),year=year,key=key)})
sar=ddply(idx, .(f,k,M,s,bg,sel3,CV,AR), with,
      as.data.frame(spec.ar(ssb,plot=FALSE,demean=TRUE)[c("freq","spec")]))

ggplot(subset(sar,1/freq<=100&bg==3&AR==0))+
  geom_line(aes(1/freq,spec,
                col     =as.character(CV),
                group   =paste(AR,CV,sel3),
                linetype=as.character(sel3)))+
  xlab("Wave Length")+ylab("")+
  facet_grid(f*M~k*s)+
  theme_bw()+
  theme(legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`.** Estimate spectral densities of SSB from AR fits.

```{r, scree}
sfn=ddply(idx,        .(f,k,M,s,bg,sel3,CV,AR), with,
          as.data.frame(spec.pgram(ssb,plot=FALSE,demean=TRUE)[c("freq","spec")]))

mat=cast(sfn,f+k+M+s+bg+sel3+CV+AR~freq,value="spec")

kclusts=data.frame(nclst=1:25) %>% 
  group_by(nclst) %>% 
  do(kclust=kmeans(mat, .$nclst, nstart=20,  iter.max=20))

## scree plot
scree=kclusts %>% group_by(nclst) %>% do(glance( .$kclust[[1]])) 
ggplot(scree, aes(nclst, tot.withinss)) + 
  geom_line()+
  xlab("Number of Clusters")+ylab("Within SS")+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Scree plot to identify number of clusters, i.e. 10


```{r, clusters}
assign=kclusts %>% group_by(nclst) %>% do(tidy(.$kclust[[1]])) 

## time series
key=kclusts %>% group_by(nclst) %>% do(augment(.$kclust[[1]], cbind(mat[,seq(8)],key=seq(288))))
key=transform(key,cluster=factor(.cluster,levels=1:25))[,-11]
idx.=merge(idx,key[,c("key","nclst","cluster")],by="key",all=TRUE)
mn  =ddply(subset(idx.,year%in%501:600&nclst%in%seq(2,6,2)),
                  .(cluster,nclst,year), with, data.frame(mean=mean(ssb)))
ggplot(subset(idx.,nclst%in%seq(2,6,2)&year%in%501:600))+
  geom_line(aes(year,ssb,group=key),col="grey50",size=.1)+
  geom_line(aes(year,mean),col="blue",data=mn)+
  facet_grid(nclst~cluster)+
  xlab("Cluster")+ylab("SSB")+
  scale_x_continuous(breaks=seq(500,600,50))+
  theme_bw()+
  theme(axis.text.x=element_text(angle=45),legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`.** Clusters

    

# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
```


