---
title: "mydas"
subtitle: "Funded by the Irish Exchequer and EMFF 2014-2020"
author: "Laurence Kell, Alex Tidd, Coilin Minto & Maite Pons"
date: "October 5, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo      =FALSE)
```

```{r libraries}
library(grid)
library(png)
```


## Tasks

**Develop MSY reference points** or proxies across the spectrum of data-limited stocks.

<!-- Economic value; Importance; Sensitivity to the impacts of fishing; Available data. -->

**Simulation Framework**, as a number of data-limited methods already exist implement a common framework to compare their performance

**Diagnostics** to assess sensitivity to assumptions and bias. 

**Management Strategy Evaluation** to ensure robustness to uncertainty 

# Simulation Framework

## Life Histories
```{r fig.height=5.5}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/papers/FLife/tex/figsfb-1.png"))
```

## Case Studies
Turbot, Brill, Pollack, Ray, Sprat, Lobster, Razors
 
```{r fig.height=5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/tasks/task4/tex/om/turbot-pairs-1.png"))
```


## Natural Mortality
```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/papers/FLife/tex/figsm-1.png"))
```

## Biology
```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/tasks/task4/tex/om/turbot-vectors-1.png"))
```

## Equilibrium and Reference Points
```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/tasks/task4/tex/om/turbot-eqRun-1.png"))
```

## Operating Model
```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/tasks/task4/tex/om/turbot-ts-1.png"))
```

# Sensitvity Analysis

## Elasticity
Reference Points
```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/R/tex/elas-lorenzen/elasRef-1.png"))
```

## Elasticity
Reference Points
```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/R/tex/elas-lorenzen/elasRef2-1.png"))
```

## Elasticity

Population Growth Rate
```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/R/tex/elas-lorenzen/elasR-1.png"))
```

## Elasticity

Mean age at virgin and $F_{MSY}$, and $L_{opt}$
```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/R/tex/elas-lorenzen/elasGt-1.png"))
```

## Elasticity

Species
```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/R/tex/elas-lorenzen/comp-1.png"))
```

# Length v Catch Methods

## Scenarios
Stock trends 

```{r fig.height=5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/meetings/wklifeiiiv/maite-l-scen.png"))
```

## Evaluation

```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/meetings/wklifeiiiv/maite-cl.png"))
```

# Length Based Methods

## Observation Error Model
Selection pattern

```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/meetings/wklifeiiiv/maite-l-sel.png"))
```

## Evaluation 
```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/meetings/wklifeiiiv/maite-l.png"))
```

# Turbot Example


## Operating Model
```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/tasks/task4/tex/om/turbot-ts-1.png"))
```

## Category 1: Age based

```{r fig.height=5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/tasks/task4/tex/simtest/vpa-xsa-turbot-1.png"))
```

## Category 1: Biomass based

```{r fig.height=5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/tasks/task4/tex/simtest/bd-turbot-1.png"))
```

## Category 3: Catch only

```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/tasks/task4/tex/simtest/bdsra-turbot-plot-1.png"))
```

## LBSPR

Fishing Mortality 

```{r fig.height=4.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/tasks/task4/tex/simtest/lbspr-turbot-fm-1.png"))
```


## MLZ
```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/project/tasks/task4/tex/simtest/mlz-turbot-z-1.png"))
```

# MSE

## Performance Measures 
### **Safety** 
+ Probability of avoiding limits

### **Status** 
+ Probability of achieving targets, recovery and long-term

### **Yield** 
+ MSY

### **Variability** 
+ Annual variability in yield

## Cat 1; Aged based ICES AR

```{r fig.height=5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/meetings/wklifeiiiv/mp-a.png"))
```

## Cat 1; Biomass based ICES AR

```{r fig.height=5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/meetings/wklifeiiiv/mp-b.png"))
```

## Cat 1;  Comparison

```{r fig.height=5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/meetings/wklifeiiiv/papers-2018/mp-c1.png"))
```

## Empirical HCRs
Index Relative to Reference

```{r fig.height=5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/meetings/wklifeiiiv/mp-p.png"))
```

## Empirical HCRs
Trend in Index 

```{r fig.height=5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/meetings/wklifeiiiv/mp-d.png"))
```

## Compare  Performance

```{r fig.height=5.5,echo=FALSE}
grid.raster(readPNG("/home/laurence/Desktop/sea++/mydas/meetings/wklifeiiiv/papers-2018/mp-c.png"))
```


# Conclusions
## Conclusions
### **Risk**
An uncertainty that matters, what matters are management objectives

### **Management Procedures**
Consider the data along with the assumptions, estimator and management and feedback between the various elements

### **Value of infomation**
Models are cheap, but data is expensive

### **Diagnostics**
Compare across species, stocks, fisheries and advice rules

## R Packages

+ FLR
    + FLife
    + mydas
    + mpb
+ R Packages
    + LBSPR
    + MLZ
    + ...
    