---
title: "Time Series Analysis"
subtitle: "VPA"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
vignette: >
  %\VignetteIndexEntry{FLife}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
github_document:
    mathjax: TRUE
tags: FLife
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---


```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(cache     =TRUE,
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=10,
               fig.width =8,
               cache.path="../cache/spectra",
               fig.path  ="../tex/spectra-")

options(digits=3)

iFig=0
```
```{r pkgs}
library(ggplot2)
library(reshape)
library(plyr)
library(dplyr)
library(FLCore)
library(ggplotFL)

library(FLBRP)
library(FLAssess)
library(FLife)
library(mydas)

library(RPostgreSQL)
library(DBI)
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat=file.path(dirMy,"data")
```

```{r, db}
drv  =dbDriver("PostgreSQL")

conLK=dbConnect(drv, 
               host    ='wklife.csrzweaa3tbm.eu-west-2.rds.amazonaws.com',
               dbname  ='wklife',
               port    =5432,
               user    ='mydas',
               password='Yes_Meski')
#dbListTables(conLK)

xsa=dbReadTable(conLK,"mydas_xsa")
ref=subset(dbReadTable(conLK,"om"),year==40)

## query="SELECT * FROM 'EastMC' WHERE n IN (2) AND a IN ('a','b') LIMIT 10"
#ref=dbGetQuery(conLK, "select * from om WHERE year==40")

xsa=merge(xsa,ref[,c("spp","iter","ssb","sln","fbar","catch","rec")],by=c("spp","iter"))

xsa=subset(xsa,year>60)
```

```{r, ts, fig.height=8}
ggplot(ddply(xsa,.(spp,year), with, data.frame(ssb=mean(ssb/msy_ssb))))+
  geom_line(aes(year,ssb))+
  geom_line(aes(year,ssb/msy_ssb,col=iter),data=subset(xsa,iter%in%10:13))+
  facet_wrap(~spp,scale="free_y",ncol=2)+
  theme(legend.position="none")+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Time series

```{r, spectra}
res=ddply(xsa,.(spp,iter), with, FLife:::spectra(FLQuant(ssb/msy_ssb)))
res=ddply(subset(res,f>0.01), .(spp,f),    with, data.frame(mx=mean(mx)))
res=ddply(res, .(spp),                     with, data.frame(f=f,m=mx/max(mx)))
ggplot(res)+
  geom_errorbar(aes(f,ymin=0,ymax=m))+
  facet_wrap(~spp,ncol=2,scale="free")+
  xlab("Frequency")+ylab("")+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Spectra

```{r, ar}
res=ddply(xsa,.(spp,iter), with, {
  rtn=acf(ssb,plot=FALSE)
  data.frame(acf=rtn$acf,lag=rtn$lag)})
dat=ddply(res,.(spp,lag), with, data.frame(val=mean(acf)))
ggplot(dat)+
  geom_errorbar(aes(lag,ymin=0,ymax=val))+
  facet_wrap(~spp,ncol=2)+
  scale_x_continuous(breaks=seq(-12,0))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Autocorrelation

```{r, rc}
res=ddply(xsa,.(spp,iter), with, {
            rtn=ccf(rec,catch,plot=FALSE)
            data.frame(acf=rtn$acf,lag=rtn$lag)})
dat=ddply(res,.(spp,lag), with, data.frame(val=mean(acf)))
ggplot(subset(dat,lag<0))+
  geom_errorbar(aes(lag,ymin=0,ymax=val))+
  facet_wrap(~spp,ncol=2)+
  scale_x_continuous(breaks=seq(-12,0))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Crosscorrelations between recruitment and catch

```{r, fr}
fl=ddply(xsa,.(spp,iter), with, {
  rtn=ccf(fbar,sln,plot=FALSE)
  data.frame(acf=rtn$acf,lag=rtn$lag)})
fl=ddply(fl,.(spp,lag), with, data.frame(val=mean(acf)))
rl=ddply(xsa,.(spp,iter), with, {
  rtn=ccf(rec,sln,plot=FALSE)
  data.frame(acf=rtn$acf,lag=rtn$lag)})
rl=ddply(rl,.(spp,lag), with, data.frame(val=mean(acf)))

dat=rbind(cbind("type"="rec",rl),cbind("type"="F",fl))
ggplot(subset(dat,lag<0))+
  geom_errorbar(aes(lag,ymin=0,ymax=val,col=type))+
  facet_wrap(~spp,ncol=2)+
  scale_x_continuous(breaks=seq(-12,0))+
  theme_bw()
```


```{r}
pid<-function(x,yr,n){
  yr=ac(yr)
  p=x[,yr]
  d=x[,yr]-x[,ac(as.numeric(yr)-1-1)]
  i=apply(x[,ac(as.numeric(yr)-seq(n)-1)],6,mean)

  model.frame(FLQuants(p=p,i=i,d=d),drop=TRUE)}

pd=ddply(xsa,.(spp,iter), with, {
                res=as.FLQuant(data.frame(year=year,data=(ssb.x-ssb.y)/ssb.y))
                pid(res,80,10)             
                })

ggplot(melt(pd,id=c("spp","iter")))+
  geom_histogram(aes(pmax(pmin(value,5),-1)))+
  geom_vline(aes(xintercept=0),col="red")+
  facet_grid(spp~variable,scale="free")

```

**Figure `r iFig=iFig+1; iFig`.** Crosscorrelations between recruitment and F and length


## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLife:     `r packageVersion('FLife')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLAssess:  `r packageVersion('FLAssess')`
* FLXSA:     `r packageVersion('FLXSA')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

\newpage
## Session Info

```{r}
sessionInfo()
```
