---
title: "Time Series Analysis"
subtitle: "WKLife"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
vignette: >
  %\VignetteIndexEntry{FLife}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
github_document:
    mathjax: TRUE
tags: FLife
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(cache     =TRUE,
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=10,
               fig.width =8,
               cache.path="../cache/spectra/simon/",
               fig.path  ="../tex/spectra/simon-")

options(digits=3)

iFig=0
```
```{r pkgs}
library(ggplot2)
library(reshape)
library(plyr)
library(dplyr)
library(FLCore)
library(ggplotFL)

library(FLBRP)
library(FLAssess)
library(FLife)
library(mydas)

library(RPostgreSQL)
library(DBI)
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat=file.path(dirMy,"data")
```

```{r, db}
lh=readRDS("/home/laurence/Desktop/sea++/mydas/meetings/wklifeiiiv/papers-2018/data/lhpars.rds")
om=readRDS("/home/laurence/Desktop/sea++/mydas/meetings/wklifeiiiv/papers-2018/data/stk.rds")
eq=readRDS("/home/laurence/Desktop/sea++/mydas/meetings/wklifeiiiv/papers-2018/data/brp.rds")
eq=propagate(eq,50)

names(dimnames(refpts(eq)))[2]="quant"
smry=subset(cbind(spp="1",omSmry(om,eq,lh)),year>120)  
```
```{r}
#' @export omSmry

omStock<-function(object){
  sage<-function(object) apply(stock.n(object)%*%ages(stock.n(object)),2:6,sum)%/%
                           apply(stock.n(object),2:6,sum)
  cage<-function(object) apply(catch.n(object)%*%ages(catch.n(object)),2:6,sum)%/%
                           apply(catch.n(object),2:6,sum) 
  swt<-function(object) apply(stock.n(object)%*%stock.wt(object),2:6,sum)%/%
    apply(stock.n(object),2:6,sum)
  cwt<-function(object) apply(catch.n(object)%*%catch.wt(object),2:6,sum)%/%
    apply(catch.n(object),2:6,sum) 
  hvt   <-function(object) catch(object)/stock(object)
  
  recs  <-function(object) {res=rec(object)
                            dimnames(res)[[1]]="all"
                            res}
  
  catchJuv<-function(object) apply(catch.n(object)%*%(1-mat(object))%*%catch.wt(object),2:6,sum)

  res=FLQuants(object,"ssb"=ssb,"stock"=FLCore:::stock,"rec"=recs,"catch"=FLCore:::catch,"catchjuv"=catchJuv,
                      "fbar"=fbar,
                      "swt"=swt,"cwt"=cwt,"sage"=sage,"cage"=cage)
  
  model.frame(mcf(res),drop=TRUE)}

omRefs<-function(object){
  
  refs=rbind(as.data.frame(object["crash",c("harvest")]),
             as.data.frame(object["virgin",c("rec","ssb")]),
             as.data.frame(object["msy",c("yield","ssb","harvest")]))
  refs=cast(refs,iter~refpt+quant,value="data")

  refs}


omSmry<-function(x,y="missing",z="missing"){
  
  nms=c("iter","year","ssb","stock","rec","catch","catchjuv","fbar",
        "crash_harvest","virgin_rec","virgin_ssb","msy_harvest","msy_ssb","msy_yield","rec_hat",
        "swt","cwt","sage","cage","sln","cln") 
  
  res=omStock(x)
  
  if ("FLBRP" %in% is(y)){
    res=merge(res,omRefs(refpts(y)))
    rec=as.data.frame((params(y)["a"]%*%ssb(x))%/%(params(y)["b"]%+%ssb(x)),drop=T)
    
    names(rec)[(seq(dim(rec)[2]))[names(rec)=="data"]]="rec_hat"
    res=merge(res,rec)
    }
  else if ("FLPar" %in% is(y))  
    res=merge(res,omRefs(y))
  
  if ("FLPar" %in% is(z))
    if (all(c("a","b") %in% dimnames(z)$params))
      res=merge(res,lenFn(x,z))

  res=res[,names(res)[names(res)%in%nms]]
  
  res=res[do.call(order,res[,c("iter","year")]),]

  return(res)}

lenFn<-function(x,y){
  sln<-function(object) apply(stock.n(object)%*%exp(log(stock.wt(object)%/%y["a"])%/%y["b"]),2:6,sum)%/%
    apply(stock.n(object),2:6,sum)
  cln<-function(object) apply(catch.n(object)%*%exp(log(catch.wt(object)%/%y["a"])%/%y["b"]),2:6,sum)%/%
    apply(catch.n(object),2:6,sum) 
  
  model.frame(FLQuants(x,"sln"=sln,"cln"=cln),drop=TRUE)}

```

```{r, ts, fig.height=8}
ggplot(ddply(smry,.(spp,year), with, data.frame(ssb=mean(ssb/msy_ssb))))+
  geom_line(aes(year,ssb))+    
  geom_line(aes(year,ssb/msy_ssb,col=iter),data=subset(smry,iter%in%10:13))+   
  facet_wrap(~spp,scale="free_y",ncol=2)+  
  theme(legend.position="none")+
  theme_bw()     
```

**Figure `r iFig=iFig+1; iFig`.** Time series

```{r, spectra}
res=ddply(smry,.(spp,iter), with, FLife:::spectra(FLQuant(ssb/msy_ssb)))
res=ddply(subset(res,f>0.01), .(spp,f),    with, data.frame(mx=mean(mx)))
res=ddply(res, .(spp),                     with, data.frame(f=f,m=mx/max(mx)))
ggplot(res)+
  geom_errorbar(aes(f,ymin=0,ymax=m))+
  facet_wrap(~spp,ncol=2,scale="free")+
  xlab("Frequency")+ylab("")+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Spectra

```{r, ar}
res=ddply(smry,.(spp,iter), with, {
  rtn=acf(ssb,plot=FALSE)
  data.frame(acf=rtn$acf,lag=rtn$lag)})
dat=ddply(res,.(spp,lag), with, data.frame(val=mean(acf)))
ggplot(dat)+
  geom_errorbar(aes(lag,ymin=0,ymax=val))+  
  facet_wrap(~spp,ncol=2)+
  scale_x_continuous(breaks=seq(-12,0))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Autocorrelation

```{r, rc}
res=ddply(smry,.(spp,iter), with, {
            rtn=ccf(rec,catch,plot=FALSE)
            data.frame(acf=rtn$acf,lag=rtn$lag)})
dat=ddply(res,.(spp,lag), with, data.frame(val=mean(acf)))
ggplot(subset(dat,lag<0))+
  geom_errorbar(aes(lag,ymin=0,ymax=val))+
  facet_wrap(~spp,ncol=2)+
  scale_x_continuous(breaks=seq(-12,0))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Crosscorrelations between recruitment and catch

```{r, fr}
fl=ddply(smry,.(spp,iter), with, {
  rtn=ccf(fbar,sln,plot=FALSE)
  data.frame(acf=rtn$acf,lag=rtn$lag)})
fl=ddply(fl,.(spp,lag), with, data.frame(val=mean(acf)))
rl=ddply(smry,.(spp,iter), with, {
  rtn=ccf(rec,sln,plot=FALSE)
  data.frame(acf=rtn$acf,lag=rtn$lag)})
rl=ddply(rl,.(spp,lag), with, data.frame(val=mean(acf)))

dat=rbind(cbind("type"="rec",rl),cbind("type"="F",fl))
ggplot(subset(dat,lag<0))+
  geom_errorbar(aes(lag,ymin=0,ymax=val,col=type))+
  facet_wrap(~spp,ncol=2)+
  scale_x_continuous(breaks=seq(-12,0))+
  theme_bw()
```


**Figure `r iFig=iFig+1; iFig`.** Crosscorrelations between recruitment and F and length



## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLife:     `r packageVersion('FLife')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLAssess:  `r packageVersion('FLAssess')`
* FLXSA:     `r packageVersion('FLXSA')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

\newpage
## Session Info

```{r}
sessionInfo()
```
