---
title: "MyDas: Elasticty Analysis"
subtitle: "Lorenzen M"
author: "Laurie Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r dir, echo=FALSE}
source('~/Desktop/flr/FLife/R/getScriptPath.R')

dirMy=dirname(dirname(getScriptPath()))
dirInp=file.path(dirMy,"inputs")
getdirDat=file.path(dirMy,"data")
```

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)

## Global options
opts_chunk$set(echo       =FALSE,
               eval       =TRUE,
               prompt     =FALSE,
               comment    =NA,
               message    =FALSE,
               warning    =FALSE,
               tidy       =FALSE,
               fig.height =6,
               fig.width  =8,
               fig.path   ="tex/elas-lorenzen/",
               cache      =TRUE,
               cache.path="cache/elas-lorenzen/")

iFig=0
iTab=0
```

```{r, pkgs, message=FALSE}
library(ggplot2)
library(GGally)

library(plyr)
library(dplyr)
library(reshape)

library(RPostgreSQL)
library(popbio)

library(FLBRP)
library(FLife)

library(numDeriv)
```

```{r, theme, echo=FALSE}
theme_set(theme_bw())
options(digits=3)
```

```{r}
ProdFn<-function(x){
  res=lhPar(FLPar(x))
  eql=lhEql(res,m=function(wt,params){
                          res=wt%^%params["m2"] 
                          res=params["m1"]%*%res
                          res})
    
  c(log(lambda(leslie(eql,fbar=c(refpts(eql)["crash","harvest"]))[drop=TRUE])),
    log(lambda(leslie(eql,fbar=c(refpts(eql)["msy",  "harvest"]))[drop=TRUE])))}

rFn=function(x){
    eql=lhEql(lhPar(FLPar(x)),m=function(wt,params){
                          res=wt%^%params["m2"] 
                          res=params["m1"]%*%res
                          res})
    
    c("r"  =log(lambda(leslie(eql,fbar=c(refpts(eql)["crash","harvest"]))[drop=TRUE])),
      "r.c"=log(lambda(leslie(eql,fbar=c(refpts(eql)["msy","harvest"]))[drop=TRUE])))}

refFn<-function(x){
  
  rf=refpts(lhEql(lhPar(FLPar(x)),m=function(wt,params){
                          res=wt%^%params["m2"] 
                          res=params["m1"]%*%res
                          res}))
    
  res=c(hmsy  =c(rf["msy","yield"]/rf["msy","ssb"]),
        fcrash=c(rf["crash","harvest"]),
        fmsy  =c(rf["msy","harvest"]),
        bmsy  =c(rf["msy","ssb"]),
        msy   =c(rf["msy","yield"]),
        shape =c(rf["msy","ssb"]/rf["virgin","ssb"]))
    
  res}

my_smooth <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
  geom_point(...,size=.5)+
  geom_smooth(...,method="lm",se=FALSE)}

my_density <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
  geom_density(...,lwd=1)}
```

```{r}
#source('~/Desktop/flr/FLife/R/sim.R')
data(wklife)
```

```{r, lifepar, fig.height=6, fig.width=6}
lh=wklife[-13,c("species","linf","k","t0","a","b","l50")]

ggpairs(transform(lh,linf=log(linf),winf=log(a*linf^b),
                  k=log(k),lmat=log(l50))[,c("b","linf","k","t0","lmat","winf")],
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Correlation between between life history parameters

Fill in missing values
```{r, par}
lh=wklife[-13,c("species","linf","k","t0","a","b","l50")]
lh[lh[,"t0"]>0&!is.na(lh[,"t0"]),"t0"]=NA

lh=lhPar(lh)[c("k","linf","t0","a50","a","b","bg","s","a1","sl","sr"),]  
lh=rbind(lh,propagate(FLPar(m1=0.3,m2=-0.288),dim(lh)[1]))
lh=lhPar(lh)
```

\newpage
#Tables

**Table `r iTab=iTab+1; iTab`** Population growth rate at low population size (r) and at $B_{MSY}$ (r.c).

```{r r2}
fn=function(x){
  res=rFn(x)
  names(res)=c("r","r.c")

  res}

r=aaply(lh,2,fn)
dimnames(r)=list(species=wklife[-13,"species"],params=c("r","r.c"))

r
```

**Table `r iTab=iTab+1; iTab`** Population doubling time at low population size (r) and at $B_{MSY}$ (r.c).

```{r r-double}
log(2)/r[,"r"]
```

```{r jacobian-r}
fn=function(x){
  res=jacobian(rFn,x)
  dimnames(res)=list(var=c("r","r.c"),params=dimnames(x)$params)
  
  res}

jacR=aaply(lh,2,fn)
dimnames(jacR)$params=dimnames(lh)$params
jacR=FLPar(aperm(jacR,c(2:3,1)))
```

```{r, jacobian-r2}
#dimnames(jacR)=list(var=c("r","r.c"),params=dimnames(res)$params,spp=lh[,"species"])
save(jacR,file="/home/laurence/Desktop/tmp/jacR.RData")  
```

**Table `r iTab=iTab+1; iTab`** Elasticity of parameters with respect to productivity at low population size (r) and at $B_{MSY}$ (r.c).

```{r, elasticity-r}
res  =FLPar(t(aaply(lh,2,rFn)))
elasR=FLPar(sweep(jacR,c(1,3),res,"/"))
```

```{r jacobian-refs}
fn=function(x){
  
  res=jacobian(refFn,x)
  dimnames(res)=list(var=c("hmsy","fcrash","fmsy","bmsy","msy","shape"),params=dimnames(x)$params)
  
  res}

jacRef=aaply(lh,2,fn)
jacRef=FLPar(aperm(jacRef,c(2:3,1)))
dimnames(jacRef)$params=dimnames(lh)$params
```

```{r}
save(jacRef,file="/home/laurence/Desktop/tmp/jacRef.RData")
```

**Table `r iTab=iTab+1; iTab`** Elasticity of parameters with respect to productivity at low population size (r) and at $B_{MSY}$ (r.c).
```{r}
elasRef=sweep(jacRef,c(1,3), FLPar(t(aaply(lh,2,refFn))), "/")
```

# Figures

```{r, params, fig.height=6, fig.width=6, eval=FALSE}
dat=cbind(lh,log(2)/pr)

ggpairs(transform(dat[,-1],linf=log(linf),k=log(k),lmat=log(l50))[,c("r","r.c","linf","k","t0","l50")],
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Correlation between population growth rate at low population size (r) and at $B_{MSY}$ (r.c).


```{r, elasR, fig.height=4}
theme_set(theme_bw())
dat=subset(melt(model.frame(elasR,id=c("params","iter"))),
         params%in%c("k","linf","t0","a50","s","b","m1","m2"))
dat$species=wklife[dat$iter,"species"]
dat$params=factor(dat$params,level=c("linf","k","t0","b","a50","m1","m2","s"))

ggplot(dat)+
  geom_boxplot(aes(params,abs(value)))+
  facet_grid(variable~.,scale="free")
```

**Figure `r iFig=iFig+1; iFig`** Elasticity analysis (r) and at $B_{MSY}$ (r.c).


```{r, elasRef}
theme_set(theme_bw())

dat=subset(melt(model.frame(elasRef,id=c("params","iter"))),
         params%in%c("k","linf","t0","a50","s","b","m1","m2"))
dat$species=wklife[dat$iter,"species"]
dat$params=factor(dat$params,level=c("linf","k","t0","b","a50","m1","m2","s"))
dat$variable=factor(dat$variable,level=c("msy","bmsy","fmsy","hmsy","shape","fcrash"))

ggplot(dat)+
  geom_boxplot(aes(params,abs(value)))+
  facet_grid(variable~.,scale="free")
```

**Figure `r iFig=iFig+1; iFig`** Elasticity analysis

```{r, comp, fig.height=8}
save(dat,file="/home/laurence/Desktop/tmp/dat.RData") 
theme_set(theme_bw())

dat=subset(dat,params%in%c("m1","m2","s","k"))
dat$species=factor(dat$species,level=unique(wklife[order(wklife[,"k"]),"species"]))
ggplot(ddply(dat,.(variable,params), with, 
             data.frame(spp=species,rel=abs(value)/mean(abs(value)))))+
  geom_boxplot(aes(spp,rel,fill=spp))+
  facet_grid(variable~.)+
  theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=1))
```
**Figure `r iFig=iFig+1; iFig`** Elasticity analysis

```{r, eval=FALSE}
vc=diag(13)
diag(vc)=(res[,10]*0.1)^2

j =jacP@.Data[,,10]
# The variance of our estimate is the cross product of the jacobian and the model's
# variance-covariance matrix

vcov =j %*% vc %*% t(j)
```

```{r}
lh=lhPar(lh)
vr=c("linf","k","t0","b","a50")
cr=cov2cor(var(model.frame(lh[vr])[,-6]))

J=apply(jacRef,1:2,mean)

vc=J[,vr,drop=T]%*%cr[vr,vr,drop=T]%*%t(J[,vr,drop=T])

cov2cor(vc)
```

