---
title: "Proxy $MSY$ Reference Points for data poor stocks"
subtitle: "Power of length based indicators to detect overfishing."
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

# Introduction

To provide advice on the status of data poor stocks ICES uses $MSY$ proxy reference points as part of a Precautionary Approach.

Data poor stocks include those for which only trends such as lpue,  cpue,  and  mean  length  in  the  catch  are available (**Category 3**), and stocks for which only reliable catch data are available (**Category 4**).

Methods currently approved by ICES for calculation of $MSY$ reference points for these stocks are 

+ Length based indicators 
+ Z derived from mean length 
+ Length based spawner per recruit; and
+ Surplus Production models

Many approaches have emerged over the last few decades, for example Where length data are available methods include Length Based Spawning Potential Ratio (LBSPR), Length-Based Integrated Mixed Effects (LIME), and Length-Based Bayesian (LBB). While where only catch data are available methods include Catch-Maximum Sustainable Yield (Catch-MSY), State-Space Catch-Only Model (SSCOM), Depletion Based Stock Reduhction Analysis (DBSRA), and Simple Stock Synthesis (SSS) an extension of Catch-MSY (CMSY).

Empirical indicators and reference points can also be used to monitor stocks and these include

+ $L_{max5\%}$ mean length of largest 5\%
+ $L_{95\%}$ $95^{th}$ percentile
+ $P_{mega}$ Proportion of individuals above $L_{opt} + 10\%$
+ $L_{25\%}$ $25^{th}$ percentile of length distribution
+ $L_{c}$ Length at $50\%$ of modal abundance
+ $L_{mean}$ Mean length of individuals $> L_c$
+ $L_{max_{y}}$ Length class with maximum biomass in catch
+ $L_{mean}$ Meanlength of individuals $> L$

where potential  **reference points** include

+ $L_{opt} = L_{\infty}\frac{3}{3+\frac{M}{K}}$, assuming $M/K = 1.5$ gives $\frac{2}{3}L_{\infty}$
+ $L_{F=M} =  0,75l_c+0.25l_{\infty}$

# Methods

## Simulation

Run scenarios with an increasing trend in F that leads to overfishing, then implement a recovery plan that brings fishing to the $F_{MSY}$ level then screen potential empirical MPs by

   - Generating length, catch and CPUE indicators using an OEM 
   - Compare indicators to OM using Reciever Operating Characteristics (ROCs) 

## Receiver Operating Characteristics

Sort the observed outcomes by their predicted scores with the highest scores first, then calculate cumulative True Positive Rate (TPR) and True Negative Rate (TNR) for the ordered observed outcomes

<!-- + **Methods** Run scenarios with an increasing trend in F that leads to overfishing, then implement a recovery plan that brings fishing to the $F_{MSY}$ level then screen potential empirical MPs by -->
<!--   - Generating length, catch and CPUE indicators using an OEM -->
<!--   - Fit indices using LBSPR, SRA and a biomass dynamic model -->
<!--   - Compare indicators to OM, both trends and status relative to reference points using Reciever Operating Characteristics (ROCs) -->

<!-- + **Analysis**  Compare indicators to OM -->
<!--   - Compare ability to estimate stock status relative to reference points using Reciever Operating Characteristics (ROCs) -->
<!--   - Calculate MSY reference points and proxies -->
<!--   - Generate indicators relative to reference points -->
<!--   - Evaluate the power of the various indicators to detect stock status using Reciever Operating Characteristics -->

<!-- + Receiver Operating Characteristics for parameter tuning -->
<!--   - Chose best HCR parameters -->
<!--   - Run MSE -->


<!-- ## Prediction Skill -->

<!-- + Screen model based MPs -->
<!--   - Perform 1,2,3, step ahead projections using LBSPR, SRA and a biomass dynamic model -->
<!--   - Use MASE to identify assessment models with prediction skill -->

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =6, 
               fig.height=6,
               cache     =TRUE, 
               fig.path  ="tex/indicators-",
               cache.path="cache/indicators/")

iFig=0
iTab=0
```

\newpage
```{r, pkgs} 
library(FLCore)
library(FLBRP)
library(FLasher)
library(FLife)
library(mydas)
library(ggplotFL)

library(plyr)
library(dplyr)
library(reshape)
library(popbio)
library(spatstat)
```

```{r, params}

par=lhPar(FLPar(c(linf= 59.1,  k=0.28, t0=-0.4,
           a=0.01111,b=3.15,a50=4.0, l50=43.25),units="NA"))
par["m1"]=.03
eq=lhEql(par)
fbar(eq)=refpts(eq)["msy","harvest"]%*%FLQuant(c(rep(0.1,60),
                                                 seq(0.1,2,length.out=40)[-40],
                                                 seq(2,1,length.out=11),rep(1,20)))

set.seed(234)
srDev=rlnoise(100,fbar(eq)%=%0,0.3,0)

om=as(eq,"FLStock")
om=window(fwd(propagate(om,dim(srDev)[6]),fbar=fbar(eq)[,-1],sr=eq,residuals=srDev),
          start=41)
```

```{r, ts}
plot(FLQuants(om, 
          "f" =   function(x) fbar(x)%/%refpts(eq)["msy","harvest"], 
          "ssb" = function(x) ssb(x)%/%refpts( eq)["msy","ssb"], 
          "catch"=function(x) landings(x)%/%refpts(eq)["msy","yield"],
          "rec" = function(x) rec(x)%/%refpts( eq)["msy","rec"])) + 
  geom_hline(aes(yintercept=1),col="red",linetype=2)+
  theme_bw() 
```

**Figure `r iFig=iFig+1; iFig`** Time series relative to MSY benchmarks.


\newpage
## Mean length indicators
```{r, indicators}
ind=mydas:::omSmry(om,par)
```


```{r, refpts}
refs=mydas:::popdyn(par,eq)
```

```{r, echo=FALSE}
quad=data.frame(x=c(40,80, 80, 40,  80,90,90,80, 90,105,105,90, 105,110,110,105, 110,130,130,110), 
                y=rep(c(-Inf,-Inf,Inf,Inf),5),
                f=c(rep("green",4),rep("amber",4),rep("red",4),rep("amber2",4),rep("green2",4)))
```

\newpage
## Length Frequencies
```{r}
source('~/Desktop/sea++/mydas/pkg/R/oemLn.R')

## Matrix with P(len) by age for each set of params
agLs=alk(par,cv=0.1)

## Simulate length frequencies by year
lfd=lenSample(catch.n(om),iter(agLs,i),nsample=100)
lfd=subset(as.data.frame(lfd),data>0)
```

```{r}
library(spatstat)

rln=ddply(subset(lfd,year%in%c(60,100,120)), .(year),  
          with,mydas:::lenInd(len,data,lopt=c(refs["lopt"]))[-5])
```

```{r, echo=FALSE}
ggplot(subset(lfd,year%in%c(60,100,120)&iter==1))+    
  geom_histogram(aes(len,weight=data),binwidth=1)+
  geom_vline(aes(xintercept=value,col=variable),data=melt(rln,id="year"))+
  facet_grid(year~.)+
  xlab("Length (cm)")+ylab("")+
  scale_color_manual("Indicator",values=rainbow(4))

save(lfd,file="/home/laurence/tmp/t.RloadData")   
```

**Figure `r iFig=iFig+1; iFig`.** Simulated length frequencies distributions with indicators.

```{r}   
save(lfd,refs,eq,par,file="/home/laurence/tmp/t.RData")    
```

```{r}
source('~/Desktop/sea++/mydas/pkg/R/oemLn.R')
inds=ddply(lfd, .(year,iter), with, lenInd(len,data,lopt=c(refs["lopt"])))

rf=FLQuants(  
  f    =window(fbar(eq)/c(refs["fmsy"]),start=41),
  lbar =as.FLQuant(transmute(inds,year=year,iter=iter,data=lbar))/c(par["l50"]),
  lfm  =as.FLQuant(transmute(inds,year=year,iter=iter,data=lfm)),
  pmega=as.FLQuant(transmute(inds,year=year,iter=iter,data=pmega)),
  l95  =as.FLQuant(transmute(inds,year=year,iter=iter,data=l95/c(par["linf"]))),
  l25  =as.FLQuant(transmute(inds,year=year,iter=iter,data=l25/c(par["linf"]))))
```

```{r, echo=FALSE}
p=plot(rf)+       
  facet_grid(qname~.,scale="free")+
  geom_polygon(aes(x,y,fill=f),data=quad,alpha=0.2)+
  geom_vline(aes(xintercept=x),data=data.frame(y="2FMSY",x=c( 90,105)),col="red")+
  geom_vline(aes(xintercept=x),data=data.frame(y="2FMSY",x=c( 80,110)),col="orange")+
  scale_fill_manual(values=c("orange","orange","green","green","red","blue"))

p5=p$layers[[5]]
p$layers[[5]]=p$layers[[1]]
p$layers[[1]]=p5
p
```

**Figure `r iFig=iFig+1; iFig`.** Time series of indicators compared to $F:F_{MSY}$, vertical lines indicate 1 (green), 1.5 (orange) and 2 (red) times $F_{MSY}$.

\newpage
## Receiver Operating Characteristics

### Detection of overfishing

```{r, fig.height=4, fig.width=4}
simple_roc <- function(labels, scores){
  labels <- labels[order(scores, decreasing=TRUE)]
  data.frame(TPR=cumsum(labels)/sum(labels), 
             FPR=cumsum(!labels)/sum(!labels),
             labels,
             scores=sort(scores))}
 ```


```{r, fig.height=4, fig.width=4}
ind=ldply(rf[-1],function(x) as.data.frame(window(x,start=70,end=100),drop=T))  
ind=ddply(ind,.(.id),transform,overfished=as.numeric(!(year%in%90:105)))
ind=ddply(ind,.(.id),with, simple_roc(overfished,data))

tab=ddply(ind,.(.id), with, { 
                 best=max(TPR*(1-FPR))==TPR*(1-FPR);   
                 data.frame(TPR=TPR[best],FPR=FPR[best],scores=scores[best])})

ggplot(ind)+ 
  geom_point(aes(FPR,TPR,col=.id))+
  geom_line(aes(x,y),data.frame(x=seq(0,1,0.01),y=seq(0,1,0.01)))+
  geom_point(aes(FPR,TPR),data=tab,size=2)+
  xlab("False Negative Rate")+ylab("True Positive Rate")+
  scale_color_manual("Indicator",values=rainbow(5))+
  theme(legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`.** ROC curve of the three indicators of overfishing, points indicate the optimum value of the indicator.

```{r}
tab    
```

### Detection of recovery

```{r, fig.height=4, fig.width=4}
ind=ldply(rf[-1],function(x) as.data.frame(window(x,start=105),drop=T)) 
ind=ddply(ind,.(.id),transform,overfished=as.numeric((year>105)))
ind=ddply(ind,.(.id),with, simple_roc(overfished,data))

tab=ddply(ind,.(.id), with, { 
                 best=max(TPR*(1-FPR))==TPR*(1-FPR);   
                 data.frame(TPR=TPR[best],FPR=FPR[best],scores=scores[best])})

ggplot(ind)+      
  geom_point(aes(FPR,TPR,col=.id))+
  geom_line(aes(x,y),data.frame(x=seq(0,1,0.01),y=seq(0,1,0.01)))+
  geom_point(aes(FPR,TPR),data=tab,size=2)+
  xlab("False Negative Rate")+ylab("True Positive Rate")+
  scale_color_manual("Indicator",values=rainbow(5))+
  theme(legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`.** ROC curve of the three indicators of recovery, points indicate the optimum value of the indicator.

```{r}
tab
```

\newpage 
# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
``` 

