---
title: "Simulation Testing Data Limited Methods **mydas**"
subtitle: "LBSPR"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
github_document:
  mathjax: TRUE
pdf_document:
  fig_width: 6 
  fig_height: 4 
tags: [FLR]
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---
 
```{r, ini, echo=FALSE, results='hide', message=FALSE, warnings=FALSE, cache=FALSE,eval=!TRUE}
library(knitr)
source("R/ini.R")
```

```{r knitr_init, echo=FALSE, results="hide", eval=!FALSE}
library(knitr)  
## Global options
opts_chunk$set(cache     =TRUE,
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=4,
               fig.width =6,
               fig.path  ="tex/lbsprV2-",
               cache.path="cache/lbsprV2/")
```

```{r}
options(digits=3)

iFig=0
```


# Introduction

This vignette shows how to use `FLR` to simulation test second party length based stock assessment packages. To follow the examples you need to install 

- FLR package [FLife](http://www.flr-project.org/FLife/), [mydas](https://github.com/laurieKell/mydas/wiki)
- [LBSPR](https://github.com/AdrianHordyk/LBSPR) as an example

```{r, pkgs}
library(FLife)
library(mydas)

library(LBSPR)
```

# Length Based Methods

Based on Beverton and Holt  $L_{F} = \frac{L\infty +\frac{F+M}{K}L_c}{1+\frac{F+M}{K}}$

+ $L_{current}/L_{F=M}$ 
+ $M/(Z_{current}-M)$
+ $F_{0.1}/(Z_{current}-M)$
+ $LBSPR$ Length-based spawning potential ratio (Hordyk et al. 2015) 
+ $Lime$ (Rudd and Thorson, 2018) mixed effects non-equilibrium

## LB-SPR

[LBSPR](https://cran.r-project.org/web/packages/LBSPR/vignettes/LBSPR.html)
is a R package for simulation and estimation using life-history ratios and length composition data


# Operating Model

Turbot

```{r, om}
lh=FLPar(c(linf=58.684, k  =0.2868,t0=-0.4194737,
           a   =0.02038,b  =2.925,
           a50 =4.23741,l50= 43.25),units="NA")
lh=lhPar(lh)
eq=lhEql(lh)
lh=rbind(lh,FLPar(gTime=c(round(gt(eq)))))
f =FLQuant(c(rep(0.1,60),seq(0.1,2.5,length.out=40)[-40],
            seq(2.5,1,length.out=11),rep(1,20)))
fbar(eq)=refpts(eq)["msy","harvest"]%*%f
om=as(eq,"FLStock")
om=fwd(om,f=fbar(om)[,-1], sr=eq)
```

```{r, ts}
plot(FLQuants(om, 
          "f" =   function(x) fbar(x)%/%refpts(eq)["msy","harvest"], 
          "ssb" = function(x) ssb(x)%/%refpts( eq)["msy","ssb"], 
          "catch"=function(x) landings(x)%/%refpts(eq)["msy","yield"],
          "rec" = function(x) rec(x)%/%refpts( eq)["msy","rec"])) + 
  geom_hline(aes(yintercept=1),col="red",linetype=2)+
  theme_bw() 
```

**Figure `r iFig=iFig+1; iFig`** Time series relative to MSY benchmarks.


```{r, alk}
source('~/Desktop/sea++/mydas/pkg/R/oemLn.R')

ak=invAlk(lh,cv=0.1)    
```

```{r, lfd}
lfd=lenSample(catch.n(om)[,50:125],ak,nsample=500)
```

```{r, oem}
ggplot(melt(lfd[,as.character(seq(50,125,25))]))+
  geom_histogram(aes(len,weight=value),binwidth=1)+
  facet_grid(year~iter,scale="free")+
  xlab("Length (cm)")+ylab("Frequency")+
  coord_cartesian(xlim=c(25,mean(lh["linf"])*1.5))
```
**Figure `r iFig=iFig+1; iFig`** Observation error model for turbot. 


```{r, sa}
source('~/Desktop/sea++/mydas/pkg/R/lbspr.R')

prior=popdyn(lh)
lb=lbspr(lfd,prior)
```

```{r}
plot(lb)+
  xlab("Year")
```

**Figure `r iFig=iFig+1; iFig`** Estimates. 

```{r, fm}
plot(mcf(FLQuants(
              Estimate=lb[["fm"]],
              OM      =window(fbar(om)%/%apply(m(om),c(2,6),mean),start=50,end=125))))+
  scale_x_discrete(breaks=seq(20,100,20))+
  ylab("F+M")+xlab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of $F+M$. 

```{r, spr}
plot(mcf(FLQuants(
              Estimate=lb[["spr"]],
              OM      =window(ssb(om)%/%rec(om),start=50,end=125))))+
  scale_x_discrete(breaks=seq(20,100,20))+
  ylab("SPR")+xlab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of $SPR$. 

## Monte Carlo Simulation

```{r, om-mc, eval=FALSE, echo=TRUE}
lh=FLPar(c(linf=58.684, k  =0.2868,t0=-0.4194737,
           a   =0.02038,b  =2.925,
           a50 =4.23741,l50= 43.25),units="NA")
lh=lhPar(lh)
eq=lhEql(lh)
f =FLQuant(c(rep(0.1,60),seq(0.1,2.5,length.out=40)[-40],
             seq(2.5,1,length.out=11),rep(1,20)))
fbar(eq)=refpts(eq)["msy","harvest"]%*%f

om=as(eq,"FLStock")
```

```{r}
prior
```

```{r, mc}
source('~/Desktop/sea++/mydas/pkg/R/lbspr.R')

srDev=rlnoise(100,rec(om)%=%0,0.3)
om=fwd(propagate(om,100), fbar=fbar(om)[,-1], sr=eq, residuals=srDev)

ak =invAlk(lh,cv=0.1)    
lfd=lenSample(catch.n(om)[,50:125],ak,nsample=500)
lb =lbspr(lfd,prior)
```

```{r}
plot(mcf(FLQuants( 
  Estimate=lb[["fm"]],
  OM      =window(fbar(om)%/%apply(m(om),c(2,6),mean),start=50,end=125))))+
  scale_x_discrete(breaks=seq(20,100,20))+
  ylab("F+M")+xlab("Year")+
  theme_bw()
```

```{r,crossvalidate, eval=FALSE}
par=rbind(lh,prior["mk"])

fwd.lbspr(par,1)

fwd.lbspr(propagate(par,2),1)

plot(fbar(om)/m(om)["4"])

prior  =popdyn(lh)
effort=fbar(om)%/%apply(fbar(om),6,mean)

obs=as.FLQuant(ddply(melt(lfd),.(year,iter), with,data.frame(data=sum(as.numeric(len)*value)/sum(value))))
     
hat=maply(data.frame(year=30:65), function(year){
    lb=FLQuant(lbspr(window(lfd,end=year),prior))
    q=apply(lb["FM"]%/%effort[,dimnames(lb["FM"])$year],6,mean)
    hat=effort[,ac(iyr+1)]%*%q
    fwd.lbspr(par,c(hat))}) 
hat=as.FLQuant(transmute(melt(obs),year=year,params=params,data=value))
```


# References

# More information

* You can submit bug reports, questions or suggestions on this tutorial at <https://github.com/flr/doc/issues>.
* Or send a pull request to <https://github.com/flr/doc/>
* For more information on the FLR Project for Quantitative Fisheries Science in R, visit the FLR webpage, <http://flr-project.org>.

## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLasher: `r packageVersion('FLasher')`
* **Compiled**: `r date()`

## License

This document is licensed under the [Creative Commons Attribution-ShareAlike 4.0 International](https://creativecommons.org/licenses/by-sa/4.0) license.

## Author information

**Laurence KELL**. laurie@seaplusplus.co.uk


## Acknowledgements

This vignette and the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.
