---
title: "Stock Assessment"
subtitle: "LBSPR, length based assessment"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
vignette: >
  %\VignetteIndexEntry{FLife}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
github_document:
    mathjax: TRUE
tags: FLife
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(cache     =TRUE,
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=6,
               fig.width =8,
               fig.path  ="../tex/simtest/lbspr-",
               cache.path="../cache/simtest/lbspr/")

options(digits=3)

iFig=0
```
```{r pkgs}
library(plyr)
library(reshape)
library(ggplot2)
library(dplyr)

library(FLCore)
library(ggplotFL)
library(FLBRP)
library(FLife)
library(mydas)

library(LBSPR)

library(RPostgreSQL)
library(DBI)
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat=file.path(dirMy,"data")
```
```{r, sa}
source('~/Desktop/sea++/mydas/pkg/R/lbspr.R')
```


```{r, connection}
drv  =dbDriver("PostgreSQL")

con  =dbConnect(drv, host = 'postgresql-seascope.csffkpr9jjjn.eu-west-2.rds.amazonaws.com',
                dbname = 'mydasDev',
                port = 5432,
                user = 'MydasApplication',
                password = 'gmit2017!')  
```

```{r, data}
bio=dbGetQuery(con, paste0("SELECT year, speciesgp, fishlength_cm,  SUM(number*(60/hauldur_min)) 
                            AS number
                            FROM data_surveybio
                            WHERE speciesgp in ('TUR','BLL','POL','SKA','SPR')
                            GROUP BY year, speciesgp, fishlength_cm;"))

mnl=ddply(bio,.(speciesgp,year), with, data.frame(meanLn=sum(fishlength_cm*number)/sum(number)))
```

## Brill
```{r, brill, fig.height=4}
load("/home/laurence/Desktop/Dropbox/mydasOMs/data/brill.RData")
```
  
```{r, brill-lbspr}
lfd  =transmute(subset(bio, speciesgp=='BLL'),len=fishlength_cm,n=number,year=year)
len  =as.matrix(cast(lfd,len~year,value="n"))
attributes(len)$class="matrix"
len[is.na(len)]=0

params   =apply(prior,1,mean)
bll.lbspr=as.data.frame(lbsprFn(len,params))  
```

```{r, brill-lncomp, fig.height=4}
sl=melt(cbind(year=min(subset(bio, speciesgp=='BLL')$year)-1+seq(dim(bll.lbspr)[1]),bll.lbspr[,1:2]),id="year")
dat=data.frame(Quantity=c("Linf","L50","Lopt"),
           Value   =c(mean(lh["linf"]),mean(lh["l50"]),mean(prior["lopt"])))

ggplot(subset(bio, speciesgp=='BLL'), aes(fishlength_cm, number)) +
  geom_bar(stat="identity", fill="blue")+
  geom_vline(aes(xintercept=Value,col=Quantity),data=dat)+
  geom_vline(aes(xintercept=value,col=variable),data=sl)+
  theme_bw()+
  facet_grid(.~year,scale="free_y")+ 
  coord_flip()+
  scale_y_continuous(breaks=NULL)+
  ylab("Frequency")+xlab("Length (cm)")+
  theme(legend.position="bottom",strip.text.x=element_text(angle=90))
```

**Figure `r iFig=iFig+1; iFig`** Length distributions. 

```{r, fig.height=4}
ggplot(melt(cbind(year=min(subset(bio, speciesgp=='BLL')$year)-1+seq(dim(bll.lbspr)[1]),bll.lbspr[,3:4]),id="year"))+
  geom_line(aes(year,value))+
  facet_grid(variable~.,scale="free")+
  theme_bw()+xlab("Year")+ylab("F/M")
```
**Figure `r iFig=iFig+1; iFig`** Estimates of SPR and FM. 


## Turbot
```{r, fig.height=4}
load("/home/laurence/Desktop/Dropbox/mydasOMs/data/turbot.RData")

dat=data.frame(Quantity=c("Linf","L50","Lopt"),
           Value   =c(mean(lh["linf"]),mean(lh["l50"]),mean(prior["lopt"])))
```


```{r}
lfd  =transmute(subset(bio, speciesgp=='TUR'),len=fishlength_cm,n=number,year=year)
len  =as.matrix(cast(lfd,len~year,value="n"))
attributes(len)$class="matrix"
len[is.na(len)]=0

params=apply(prior,1,mean)

tur.lbspr=as.data.frame(lbsprFn(len,params))
```

```{r, fig.height=4}
sl=melt(cbind(year=min(subset(bio, speciesgp=='TUR')$year)-1+seq(dim(tur.lbspr)[1]),tur.lbspr[,1:2]),id="year")

ggplot(subset(bio, speciesgp=='TUR'), aes(fishlength_cm, number)) +
  geom_bar(stat="identity", fill="blue")+
  geom_vline(aes(xintercept=Value,col=Quantity),data=dat)+
  geom_vline(aes(xintercept=value,col=variable),data=sl)+
  theme_bw()+
  facet_grid(.~year,scale="free_y")+
  coord_flip()+
  scale_y_continuous(breaks=NULL)+
  ylab("Frequency")+xlab("Length (cm)")+
  theme(legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`** Plot of numbers at length.

```{r, fig.height=4}
ggplot(melt(cbind(year=min(subset(bio, speciesgp=='BLL')$year)-1+seq(dim(tur.lbspr)[1])
                  ,tur.lbspr[,3:4]),id="year"))+
  geom_line(aes(year,value))+
  facet_grid(variable~.,scale="free")+
  theme_bw()+xlab("Year")+ylab("F/M")
```
**Figure `r iFig=iFig+1; iFig`** Estimates of FM and SPR. 



\newpage
## Session Info

```{r}
sessionInfo()
```

## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLife:  `r packageVersion('FLife')`
* FLBRP:  `r packageVersion('FLBRP')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

