x`---
title: "FLife: Operating Model Conditioning"
subtitle: "Lobster"
author: "L Kell & A Tidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---
  
```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="../tex/om/lobster-",
               cache.path="../cache/om/lobster/")

iFig=0
iTab=0
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#sdirMy="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat=file.path(dirMy,"data")

nits=500
```
```{r, pkgs}
library(ggplot2)
library(plyr)
library(dplyr)
library(reshape)
library(GGally)

library(FLCore)
library(FLBRP)
library(FLasher)
library(ggplotFL)
library(FLife)
```
```{r devs}
set.seed(1233)
srDev=FLife:::rlnoise(nits,FLQuant(0,dimnames=list(year=1:105)),.3,b=0.0)
```

## Life history parameters

```{r, lh}
ab=cbind(a=c(0.00126,0.000919,0.0017,0.0004,0.001086,0.000447),
         b=c(3.36,2.922,2.797,3.123,2.896,3.01))
         
lh=read.csv("/home/laurence/Desktop/sea++/mydas/tasks/task4/inputs/lobsterGrw.csv")
lh=cbind(lh,rbind(ab,cbind(a   =rep(NA,dim(lh)[1]-dim(ab)[1]),
                           b   =rep(NA,dim(lh)[1]-dim(ab)[1]))))

lh=cbind(lh,cbind(a50=c( 6.0,rep(NA,dim(lh)[1]-1)),
                  l50=c(77.5,rep(NA,dim(lh)[1]-1)),
                  t0 =c(-0.1,rep(NA,dim(lh)[1]-1))))
```

```{r, par}
my_smooth <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_point(...,size=.5)+
    geom_smooth(...,method="lm",se=FALSE)}

my_density <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_density(...,lwd=1)}

theme_set(theme_bw(base_size=20))

ggpairs(transform(lh,linf=log(linf),k=log(k),a50=a50),
        lower = list(continuous = wrap(my_smooth)),
        diag=list(continuous=wrap(my_density,alpha=0.2)),
        title = "")+
  theme(legend.position ="none",
        panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.x      =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Pairwise scatter plots of life history parameters.


## Equilibrium dynamics

The parameters are then used by `lhEql` to simulate the equilibrium dynamics by combining the spawner/yield per recruit relationships with a stock recruiment relationship.

```{r, eqRun}
sim<-function(x,niters=500,se=0.3){
  
  mn=aaply(x,1,mean, na.rm=TRUE)
  sd=aaply(x,1,var,  na.rm=TRUE)^0.5
  n =aaply(x,1,function(x) sum(!is.na(x)))
  se=sd/n^0.5
  
  if (any(is.na(se))) se[is.na(se)]=se
  
  y=data.frame(mn=mn,se=se)
  y=mdply(y,function(mn,se) rnorm(niters,mn,se))[,-(1:2)]
  
  res=FLPar(array(unlist(c(y)),c(dim(x)[1],niters)))
  
  dimnames(res)$params=names(mn)
  
  res}

# create FLPar
lh=FLife:::mf2FLPar(lh)

lh=sim(lh,    niters=nits)

lh=lhPar(lh,s=0.8, sl=1)
eq=lhEql(lh,spwn=0)
```

```{r vectors}
sel<-function(x) 
  catch.sel(x)%/%fapex(catch.sel(x))

dat=FLQuants(eq,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Mass"=stock.wt)

res=ldply(dat,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")
```

**Figure `r iFig=iFig+1; iFig`** Vectors.


```{r, eq, fig.height=6,fig.width=8}
plot(iter(eq,1),refpts=FALSE)
```

**Figure `r iFig=iFig+1; iFig`** Example equilibrum Curve.


## Population dynamics

```{r om}
#http://www.fishbase.org/manual/Key%20Facts.htm

gTime=round(FLife:::genTime(FLPar(aaply(lh,1,mean))))

eq@fbar=refpts(eq)["msy","harvest"]%*%FLQuant(c(rep(.1,19),
                                              seq(.1,2,length.out=30),
                                              seq(2,.7,length.out=gTime)[-1],
                                              rep(.7,61)))[,1:105]

om=as(eq,"FLStock")
om=fwd(om,fbar=fbar(om)[,-1],sr=eq,residuals=srDev)
           
save(lh,eq,om,file=file.path(dirDat,"lobster.RData"),compress="xz")

plot(om)
```

**Figure `r iFig=iFig+1; iFig`** Time series.

```{r ts}
plot(FLQuants(om, 
          "ssb" = function(x) ssb(x)%/%refpts( eq)["msy","ssb"], 
          "f" =   function(x) fbar(x)%/%refpts(eq)["msy","harvest"], 
          "rec" = function(x) rec(x)%/%refpts( eq)["msy","rec"], 
          "catch"=function(x) landings(x)%/%refpts(eq)["msy","yield"])) + 
  geom_hline(aes(yintercept=1),col="red") 
```

**Figure `r iFig=iFig+1; iFig`** Time series relative to MSY benchmarks.

\newpage
## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLasher:   `r packageVersion('FLasher')`
* FLife:     `r packageVersion('FLife')`
* ggplotFL:  `r packageVersion('ggplotFL')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
```


