---
title: "Cross test using Operating Model based on Life History"
subtitle: "VPA"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
vignette: >
  %\VignetteIndexEntry{FLife}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
github_document:
    mathjax: TRUE
tags: FLife
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(cache     =TRUE,
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=10,
               fig.width =8,
               cache.path="../cache/simtest/vpa",
               fig.path  ="../tex/simtest/vpa-")

options(digits=3)

iFig=0
```
```{r pkgs}
library(ggplot2)
library(reshape)
library(plyr)
library(dplyr)
library(FLCore)
library(ggplotFL)

library(FLBRP)
library(FLAssess)
library(FLXSA)
library(mydas)

library(GGally)

library(doParallel)
library(foreach)
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat=file.path(dirMy,"data")

xsaCtrl=list("default"=FLXSA.control(
                         tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =1.0, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =10, 
                         tspower= 0,
                         vpa    =FALSE))
```

```{r, source}
#source("/home/laurence/Desktop/sea++/mydas/R/refpts4hcr.R")
#source("/home/laurence/Desktop/sea++/mydas/R/xsaTest.R")
#source("/home/laurence/Desktop/sea++/mydas/R/mydas:::my_ggpairs.R")
```

## Brill

```{r, xsa-brill}
load(file.path(dirDat,"brill.RData"))               

range(om)[c("minfbar","maxfbar")]=ceiling(mean(lh["a1"]))

xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =1.0, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =10, 
                         tspower= 0,
                         vpa    =FALSE)

om=window(om,start=25,end=70)
mp=mydas:::xsaTest(om,ctrl=xsaControl)

plot(FLStocks(list("xsa"=mp,"om"=om)))

xsaCtrl["brill"]=xsaControl
save(xsaCtrl,file=file.path(dirDat,"xsaCtrl.RData"),compress="xz")
```

**Figure `r iFig=iFig+1; iFig`.** Cross test for brill.

```{r, xsa-brill-refpts-segreg}
eqS=mydas:::eqSegreg(om)
```
```{r}
#bug
dimnames(refpts(eqS))$refpt[3]="fcrash"
refpts(eqS)["fcrash","ssb"]=c(refpts(eqS)["fcrash","rec"])/c(params(eqS)["a"])
refpts(eqS)=computeRefpts(eqS)
dimnames(refpts(eqS))$refpt[3]="crash"
```
```{r}
#bug
dimnames(refpts(eqS))$refpt[3]="fcrash"
refpts(eqS)["fcrash","ssb"]=c(refpts(eqS)["fcrash","rec"])/c(params(eqS)["a"])
refpts(eqS)=computeRefpts(eqS)
dimnames(refpts(eqS))$refpt[3]="crash"
```
```{r, xsa-brill-refpts-bevholt}
eqB=mydas:::eqBevholt(om)
```
```{r, xsa-brill-refpts-geomean}
eqM=mydas:::eqGeomean(om)
```

```{r, refs-brill, fig.height=8, fig.width =8}
dat=rbind.fill(
  cbind("SRR"="SR",
    as.data.frame(refpts(eqS)[c("f0.1","virgin","crash"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="PR",
    as.data.frame(refpts(eqM)[c("f0.1","virgin"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="BH",
    as.data.frame(refpts(eqB)[c("msy","virgin","crash"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="SR",
        transform(as.data.frame(params(eqS)["b"]),refpt=params,quant="ssb")))[,-6]
dat=subset(dat,!is.na(data))

ggpairs(cast(subset(dat,quant=="ssb"),iter~SRR+refpt,value="data")[,-1],            
  #mapping = ggplot2::aes(color=SRR),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(mydas:::my_smooth,size=1)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

**Figure `r iFig=iFig+1; iFig`.** Cross test SSB reference points for brill.


```{r, refs2-brill, fig.height=8, fig.width =8}
#bug no fcrash for segreg
ggpairs(cast(subset(dat,quant=="harvest"&refpt!="virgin"),iter~SRR+refpt,value="data")[,-1],            
  #mapping = ggplot2::aes(color=SRR),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(mydas:::my_smooth,size=1)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

**Figure `r iFig=iFig+1; iFig`.** Cross test F reference points for brill.

## Turbot

```{r, xsa-turbot}
load(file.path(dirDat,"turbot.RData"))               

range(om)[c("minfbar","maxfbar")]=ceiling(mean(lh["a1"]))

xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =1.0, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =10, 
                         tspower= 0,
                         vpa    =FALSE)

om=window(om,start=25,end=70)
mp=mydas:::xsaTest(om,ctrl=xsaControl)

plot(FLStocks(list("xsa"=mp,"om"=om)))

xsaCtrl["turbot"]=xsaControl
save(xsaCtrl,file=file.path(dirDat,"xsaCtrl.RData"),compress="xz")
```

**Figure `r iFig=iFig+1; iFig`.** Simulation test for turbot.

```{r, xsa-turbot-refpts-segreg}
eqS=mydas:::eqSegreg(om)
```
```{r}
#bug
dimnames(refpts(eqS))$refpt[3]="fcrash"
refpts(eqS)["fcrash","ssb"]=c(refpts(eqS)["fcrash","rec"])/c(params(eqS)["a"])
refpts(eqS)=computeRefpts(eqS)
dimnames(refpts(eqS))$refpt[3]="crash"
```
```{r, xsa-turbot-refpts-bevholt}
eqB=mydas:::eqBevholt(om)
```
```{r, xsa-turbot-refpts-geomean}
eqM=mydas:::eqGeomean(om)
```

```{r, refs-turbot, fig.height=8, fig.width =8}
dat=rbind.fill(
  cbind("SRR"="SR",
    as.data.frame(refpts(eqS)[c("f0.1","virgin","crash"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="PR",
    as.data.frame(refpts(eqM)[c("f0.1","virgin"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="BH",
    as.data.frame(refpts(eqB)[c("msy","virgin","crash"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="SR",
        transform(as.data.frame(params(eqS)["b"]),refpt=params,quant="ssb")))[,-6]
dat=subset(dat,!is.na(data))

ggpairs(cast(subset(dat,quant=="ssb"),iter~SRR+refpt,value="data")[,-1],            
  #mapping = ggplot2::aes(color=SRR),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(mydas:::my_smooth,size=1)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

**Figure `r iFig=iFig+1; iFig`.** Cross test SSB reference points for turbot.


```{r, ref2-turbot, fig.height=8, fig.width =8}
#bug no fcrash for segreg
ggpairs(cast(subset(dat,quant=="harvest"&refpt!="virgin"),iter~SRR+refpt,value="data")[,-1],            
  #mapping = ggplot2::aes(color=SRR),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(mydas:::my_smooth,size=1)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

**Figure `r iFig=iFig+1; iFig`.** Cross test F reference points for turbot.

## Ray

```{r, xsa-ray}
load(file.path(dirDat,"ray.RData"))               

om=trim(om,age=3:40)
#om=FLCore:::iter(om,1:10)
range(om)[c("minfbar","maxfbar")]=ceiling(mean(lh["a1"]))

xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =1.0, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =10, 
                         tspower= 0,
                         vpa    =FALSE)

om=window(om,start=25,end=75)
mp=mydas:::xsaTest(om,ctrl=xsaControl,pg=20)

plot(FLStocks(list("xsa"=mp,"om"=om)))

xsaCtrl["ray"]=xsaControl
save(xsaCtrl,file=file.path(dirDat,"xsaCtrl.RData"),compress="xz")
```

**Figure `r iFig=iFig+1; iFig`.** Simulation test for ray.

```{r, xsa-ray-refpts-segreg}
eqS=mydas:::eqSegreg(om)
```
```{r}
#bug
dimnames(refpts(eqS))$refpt[3]="fcrash"
refpts(eqS)["fcrash","ssb"]=c(refpts(eqS)["fcrash","rec"])/c(params(eqS)["a"])
refpts(eqS)=computeRefpts(eqS)
dimnames(refpts(eqS))$refpt[3]="crash"
```

```{r, xsa-ray-refpts-bevholt}
eqB=mydas:::eqBevholt(om)
```
```{r, xsa-ray-refpts-geomean}
eqM=mydas:::eqGeomean(om)
```

```{r, ref-ray, fig.height=8, fig.width =8}
dat=rbind.fill(
  cbind("SRR"="SR",
    as.data.frame(refpts(eqS)[c("f0.1","virgin","crash"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="PR",
    as.data.frame(refpts(eqM)[c("f0.1","virgin"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="BH",
    as.data.frame(refpts(eqB)[c("msy","virgin","crash"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="SR",
        transform(as.data.frame(params(eqS)["b"]),refpt=params,quant="ssb")))[,-6]
dat=subset(dat,!is.na(data))

ggpairs(cast(subset(dat,quant=="ssb"),iter~SRR+refpt,value="data")[,-1],        
  #mapping = ggplot2::aes(color=SRR),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(mydas:::my_smooth,size=1)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

**Figure `r iFig=iFig+1; iFig`.** Cross test SSB reference points for ray.


```{r, ref2-ray, fig.height=8, fig.width =8}
#bug no fcrash for segreg
ggpairs(cast(subset(dat,quant=="harvest"&refpt!="virgin"),iter~SRR+refpt,value="data")[,-1],        
  #mapping = ggplot2::aes(color=SRR),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(mydas:::my_smooth,size=1)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

**Figure `r iFig=iFig+1; iFig`.** Cross test F reference points for ray.

## Pollack

```{r, xsa-pollack}
load(file.path(dirDat,"pollack.RData"))               

range(om)[c("minfbar","maxfbar")]=ceiling(mean(lh["a1"]))

xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =1.0, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =10, 
                         tspower= 3,
                         vpa    =FALSE)

om=window(om,start=25,end=70)
mp=mydas:::xsaTest(om,ctrl=xsaControl)

plot(FLStocks(list("xsa"=mp,"om"=om)))

xsaCtrl["pollack"]=xsaControl
save(xsaCtrl,file=file.path(dirDat,"xsaCtrl.RData"),compress="xz")
```

**Figure `r iFig=iFig+1; iFig`.** Simulation test for pollack.

```{r, xsa-pollack-refpts-segreg}
eqS=mydas:::eqSegreg(om)
```
```{r}
#bug
dimnames(refpts(eqS))$refpt[3]="fcrash"
refpts(eqS)["fcrash","ssb"]=c(refpts(eqS)["fcrash","rec"])/c(params(eqS)["a"])
refpts(eqS)=computeRefpts(eqS)
dimnames(refpts(eqS))$refpt[3]="crash"
```
```{r, xsa-pollack-refpts-bevholt}
eqB=mydas:::eqBevholt(om)
```
```{r, xsa-pollack-refpts-geomean}
eqM=mydas:::eqGeomean(om)
```

```{r, ref-pollack, fig.height=8, fig.width =8}
dat=rbind.fill(
  cbind("SRR"="SR",
    as.data.frame(refpts(eqS)[c("f0.1","virgin","crash"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="PR",
    as.data.frame(refpts(eqM)[c("f0.1","virgin"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="BH",
    as.data.frame(refpts(eqB)[c("msy","virgin","crash"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="SR",
        transform(as.data.frame(params(eqS)["b"]),refpt=params,quant="ssb")))[,-6]
dat=subset(dat,!is.na(data))

ggpairs(cast(subset(dat,quant=="ssb"),iter~SRR+refpt,value="data")[,-1],        
  #mapping = ggplot2::aes(color=SRR),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(mydas:::my_smooth,size=1)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

**Figure `r iFig=iFig+1; iFig`.** Cross test SSB reference points for pollack.


```{r, ref2-pollack,fig.height=8, fig.width =8}
#bug no fcrash for segreg
ggpairs(cast(subset(dat,quant=="harvest"&refpt!="virgin"),iter~SRR+refpt,value="data")[,-1],        
  #mapping = ggplot2::aes(color=SRR),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(mydas:::my_smooth,size=1)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

**Figure `r iFig=iFig+1; iFig`.** Cross test F reference points for pollack.

## Sprat

```{r, xsa-sprat}
load(file.path(dirDat,"sprat.RData"))               

range(om)[c("minfbar","maxfbar")]=ceiling(mean(lh["a1"]))
  
xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =1.0, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =10, 
                         tspower= 0,
                         vpa    =FALSE)

om=window(om,start=25,end=70)
mp=mydas:::xsaTest(om,ctrl=xsaControl)

plot(FLStocks(list("xsa"=mp,"om"=om)))

xsaCtrl["sprat"]=xsaControl
save(xsaCtrl,file=file.path(dirDat,"xsaCtrl.RData"),compress="xz")
```

**Figure `r iFig=iFig+1; iFig`.** Simulation test for sprat.

```{r, xsa-sprat-refpts-segreg}
eqS=mydas:::eqSegreg(om)  
```
```{r}
#bug
dimnames(refpts(eqS))$refpt[3]="fcrash"
refpts(eqS)["fcrash","ssb"]=c(refpts(eqS)["fcrash","rec"])/c(params(eqS)["a"])
refpts(eqS)=computeRefpts(eqS)
dimnames(refpts(eqS))$refpt[3]="crash"
```
```{r, xsa-sprat-refpts-bevholt}
eqB=mydas:::eqBevholt(om)   
```
```{r, xsa-sprat-refpts-geomean}
eqM=mydas:::eqGeomean(om)  
```

```{r, ref-sprat, fig.height=8, fig.width =8}
dat=rbind.fill(      
  cbind("SRR"="SR",
    as.data.frame(refpts(eqS)[c("f0.1","virgin","crash"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="PR",
    as.data.frame(refpts(eqM)[c("f0.1","virgin"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="BH",
     as.data.frame(refpts(eqB)[c("msy","virgin","crash"),
                             c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="SR",
        transform(as.data.frame(params(eqS)["b"]),refpt=params,quant="ssb")))[,-6]
dat=subset(dat,!is.na(data))

ggpairs(cast(subset(dat,quant=="ssb"),iter~SRR+refpt,value="data")[,c(2:8)],
  #upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  #lower = list(continuous = wrap(mydas:::my_smooth,size=1)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  #diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

**Figure `r iFig=iFig+1; iFig`.** Cross test SSB reference points for sprat.


```{r, ref2-sprat, fig.height=8, fig.width =8}
#bug no fcrash for segreg   
ggpairs(cast(subset(dat,quant=="harvest"&refpt!="virgin"),iter~SRR+refpt,value="data")[,-1],        
  #mapping = ggplot2::aes(color=SRR),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(mydas:::my_smooth,size=1)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

**Figure `r iFig=iFig+1; iFig`.** Cross test F reference points for sprat.



## Lobster

```{r, xsa-lobster}
load(file.path(dirDat,"lobster.RData"))            

om=trim(om,age=3:40)

range(om)[c("minfbar","maxfbar")]=ceiling(mean(lh["a1"]))

xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =1.0, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =10, 
                         tspower= 0,
                         vpa    =FALSE)

om=window(om,start=25,end=75)
mp=mydas:::xsaTest(om,ctrl=xsaControl,pg=20)

plot(FLStocks(list("xsa"=mp,"om"=om)))

xsaCtrl["lobster"]=xsaControl
save(xsaCtrl,file=file.path(dirDat,"xsaCtrl.RData"),compress="xz")
```

**Figure `r iFig=iFig+1; iFig`.** Simulation test for lobster.

```{r, xsa-lobster-refpts-segreg}
eqS=mydas:::eqSegreg(om)
```
```{r}
#bug
dimnames(refpts(eqS))$refpt[3]="fcrash"
refpts(eqS)["fcrash","ssb"]=c(refpts(eqS)["fcrash","rec"])/c(params(eqS)["a"])
refpts(eqS)=computeRefpts(eqS)
dimnames(refpts(eqS))$refpt[3]="crash"
```
```{r, xsa-lobster-refpts-bevholt}
eqB=mydas:::eqBevholt(om)
```
```{r, xsa-lobster-refpts-geomean}
eqM=mydas:::eqGeomean(om)
```

```{r, ref-lobster, fig.height=8, fig.width =8}
dat=rbind.fill(
  cbind("SRR"="SR",
    as.data.frame(refpts(eqS)[c("f0.1","virgin","crash"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="PR",
    as.data.frame(refpts(eqM)[c("f0.1","virgin"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="BH",
    as.data.frame(refpts(eqB)[c("msy","virgin","crash"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="SR",
        transform(as.data.frame(params(eqS)["b"]),refpt=params,quant="ssb")))[,-6]
dat=subset(dat,!is.na(data))

ggpairs(cast(subset(dat,quant=="ssb"),iter~SRR+refpt,value="data")[,-1],            
  #mapping = ggplot2::aes(color=SRR),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(mydas:::my_smooth,size=1)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

**Figure `r iFig=iFig+1; iFig`.** Cross test SSB reference points for lobster.


```{r, ref2-lobster, fig.height=8, fig.width =8}
#bug no fcrash for segreg
ggpairs(cast(subset(dat,quant=="harvest"&refpt!="virgin"),iter~SRR+refpt,value="data")[,-1],          
  #mapping = ggplot2::aes(color=SRR),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(mydas:::my_smooth,size=1)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

**Figure `r iFig=iFig+1; iFig`.** Cross test F reference points for lobster.


## Razors

```{r, xsa-razors}
load(file.path(dirDat,"razor.RData"))            

range(om)[c("minfbar","maxfbar")]=ceiling(mean(lh["a1"]))

xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =1.0, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =10, 
                         tspower= 0,
                         vpa    =FALSE)

om=window(om,start=25,end=70)
mp=mydas:::xsaTest(om,ctrl=xsaControl)

plot(FLStocks(list("xsa"=mp,"om"=om)))

xsaCtrl["razors"]=xsaControl
save(xsaCtrl,file=file.path(dirDat,"xsaCtrl.RData"),compress="xz")
```

**Figure `r iFig=iFig+1; iFig`.** Simulation test for razor.

```{r, xsa-razor-refpts-segreg}
eqS=mydas:::eqSegreg(om)
```
```{r}
#bug
dimnames(refpts(eqS))$refpt[3]="fcrash"
refpts(eqS)["fcrash","ssb"]=c(refpts(eqS)["fcrash","rec"])/c(params(eqS)["a"])
refpts(eqS)=computeRefpts(eqS)
dimnames(refpts(eqS))$refpt[3]="crash"
```
```{r, xsa-razor-refpts-bevholt}
eqB=mydas:::eqBevholt(om)
```
```{r, xsa-razor-refpts-geomean}
eqM=mydas:::eqGeomean(om)
```

```{r, ref-razor, fig.height=8, fig.width =8}
dat=rbind.fill(
  cbind("SRR"="SR",
    as.data.frame(refpts(eqS)[c("f0.1","virgin","crash"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="PR",
    as.data.frame(refpts(eqM)[c("f0.1","virgin"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="BH",
    as.data.frame(refpts(eqB)[c("msy","virgin","crash"),
                            c("ssb","biomass","rec","yield","harvest")])),
  cbind("SRR"="SR",
        transform(as.data.frame(params(eqS)["b"]),refpt=params,quant="ssb")))[,-6]
dat=subset(dat,!is.na(data))

ggpairs(cast(subset(dat,quant=="ssb"),iter~SRR+refpt,value="data")[,-1],            
  #mapping = ggplot2::aes(color=SRR),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(mydas:::my_smooth,size=1)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

**Figure `r iFig=iFig+1; iFig`.** Cross test SSB reference points for razor.


```{r, ref2-razor, fig.height=8, fig.width =8}
#bug no fcrash for segreg
ggpairs(cast(subset(dat,quant=="harvest"&refpt!="virgin"),iter~SRR+refpt,value="data")[,-1],            
  #mapping = ggplot2::aes(color=SRR),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(mydas:::my_smooth,size=1)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(mydas:::my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

**Figure `r iFig=iFig+1; iFig`.** Cross test F reference points for razors.

```{r, xsa-fwd, eval=FALSE}
registerDoParallel(4)

load(file.path(dirDat,"turbot.RData"))            
om=window(om,start=25)

xsaControl=FLXSA.control(tol    =1e-09, maxit   =150, 
                         min.nse=0.3,   fse     =1.0, 
                         rage   =1,     qage    =6, 
                         shk.n  =TRUE,  shk.f   =TRUE, 
                         shk.yrs=1,     shk.ages=4, 
                         window =10,    tsrange =10, 
                         tspower= 0,
                         vpa    =FALSE)

xsafwd=foreach(assYr=seq(75,40,-5), 
              .combine=list,
              .multicombine=TRUE,
              .packages=c("FLCore","FLAssess","FLXSA","FLasher","FLBRP","plyr")) %dopar%{

    mp =xsa(window(om,end=assYr),ctrl=xsaControl)
    sr =fmle(as.FLSR(mp,model="bevholt"),control=list(trace=FALSE))
    mp =fwdWindow(mp,end=assYr+10,FLBRP(mp))
          
    fwd(mp,catch=catch(om)[,assYr+0:10],sr=sr)
    }

xsafwd=as(xsafwd,"FLStocks")

theme_set(theme_bw())

names(xsafwd)=seq(75,40,-5)
plot(xsafwd)+
  guides(col=guide_legend(title="Assessment\n Year"))
```

**Figure `r iFig=iFig+1; iFig`.** Retrospective test


```{r, eval=FALSE}
theme_set(theme_bw())

plot(iter(xsafwd,67))+
  guides(col=guide_legend(title="Assessment\n Year"))
```

**Figure `r iFig=iFig+1; iFig`.** Single retrospective test


## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLife:     `r packageVersion('FLife')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLAssess:  `r packageVersion('FLAssess')`
* FLXSA:     `r packageVersion('FLXSA')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

\newpage
## Session Info

```{r}
sessionInfo()
```
