---
title: "Cross test using Operating Model based on Life History"
subtitle: "LBSPR, length based assessment"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
vignette: >
  %\VignetteIndexEntry{FLife}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
github_document:
    mathjax: TRUE
tags: FLife
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(cache     =TRUE,
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=6,
               fig.width =8,
               fig.path  ="../tex/simtest/lbspr-",
               cache.path="../cache/simtest/lbspr/")

options(digits=3)

iFig=0
```
```{r pkgs}
library(plyr)
library(reshape)
library(ggplot2)
library(dplyr)

library(FLCore)
library(ggplotFL)
library(FLBRP)
library(FLife)
library(mydas)

library(LBSPR)
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat=file.path(dirMy,"data")
```

```{r}
#source('~/Desktop/flr/FLife/R/oemLn.R') 
#source('~/Desktop/flr/FLife/R/lbspr.R') 
```

## Turbot
```{r, turbot-om}
load(file.path(dirDat,"turbot.RData"))

om=iter(om,1:500)
lh=iter(lh,1:500)
prior=iter(prior,1:500)

plot(om)   
```
**Figure `r iFig=iFig+1; iFig`** Operating model for turbot. 

```{r}
source('~/Desktop/sea++/mydas/pkgs/mydas/R/oemLn.R')
```

```{r, turbot-alk}
alk=setALK(lh)  
```

```{r, turbot-lfd}
lfd=lenSample(catch.n(om)[,20:65],alk,nsample=500)
```

```{r, turbot-oemplot}
ggplot(melt(lfd[,seq(1,45,10),,,,1:4]))+
  geom_histogram(aes(length,weight=value),binwidth=1)+
  facet_grid(year~iter,scale="free")+
  xlab("Length (cm)")+ylab("Frequency")+
  coord_cartesian(xlim=c(0,mean(lh["linf"])))
```
**Figure `r iFig=iFig+1; iFig`** Observation error model for turbot. 




```{r, turbot-sa}
lbsprFn<-function(len,params,species="",units="cm"){
  
  pars        =new("LB_pars")
  pars@Linf   =c(params["linf"]) 
  pars@L50    =vonB(c(params["a50"]),params) 
  pars@L95    =pars@L50+vonB(c(params["ato95"]),params)
  pars@MK     =c(params["mk"])
  pars@Species=species
  pars@L_units=units
  
  #labs=dimnames(len)[[1]]
  #brks=cbind(lower = as.numeric( sub("\\((.+),.*", "\\1", labs) ),
  #           upper = as.numeric( sub("[^,]*,([^]]*)\\]", "\\1", labs) ))
  #mid=aaply(brks,1,mean)
  
  LBlen       =new("LB_lengths")
  LBlen@LMids =as.numeric(dimnames(len)[[1]])
  LBlen@LData =len
  LBlen@Years =as.numeric(dimnames(len)[[2]])
  LBlen@NYears=dim(len)[2] 
  
  res=LBSPRfit(pars,LBlen,verbose=FALSE)
  
  res@Ests}

lbspr<-function(object,params){
  
  nits=max(dim(object)[6],dim(params)[2])
  
  if (!(dim(object)[6]%in%c(1,nits)|(dim(params)[2]%in%c(1,nits))))
    stop("iters should be equal to n or 1")
  
  res=mdply(data.frame(iter=seq(nits)), function(iter)
    lbsprFn(iter(object,iter)[drop=T],iter(params,iter)))
  res=data.frame(year=dimnames(object)$year,res)
  
  rtn=FLPar(cast(melt(res,id=c("year","iter")),variable~year~iter),units="NA")
  
  rtn}


lb=lbspr(lfd,prior)  
```

```{r}
save(lb,file="/home/laurence/Desktop/tmp/lb.RData") 
```

```{r, turbot-spr}
ggplot(melt(sweep(lb["SPR"],c(1,3),lb["SPR","40"],"/")))+
  geom_boxplot(aes(ac(year),value))+
  scale_x_discrete(breaks=seq(20,60,10))+
  xlab("SPR")+ylab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of SPR for turbot. 

```{r, turbot-fm}
ggplot(melt(sweep(lb["FM"],c(1,3),lb["FM","40"],"/")))+
  geom_boxplot(aes(ac(year),value))+
  scale_x_discrete(breaks=seq(20,60,10))+
  xlab("F")+ylab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of $F/M$ for turbot. 

## Brill
```{r, brill-om}
load(file.path(dirDat,"brill.RData"))

om   =iter(om,1:500)
lh   =iter(lh,1:500)
prior=iter(prior,1:500)

plot(om)
```
**Figure `r iFig=iFig+1; iFig`** Operating model for Brill. 

```{r, brill-alk}
alk=setALK(lh)
```

```{r, brill-lfd}
lfd=lenSample(catch.n(om)[,20:65],alk,nsample=500)
```

```{r, brill-oemplot}
ggplot(melt(lfd[,seq(1,45,10),,,,1:4]))+
  geom_histogram(aes(length,weight=value),binwidth=1)+
  facet_grid(year~iter,scale="free")+
  xlab("Length (cm)")+ylab("Frequency")+
  coord_cartesian(xlim=c(0,mean(lh["linf"])))
```
**Figure `r iFig=iFig+1; iFig`** Observation error model for Brill. 


```{r, brill-sa}
lb=lbspr(lfd,prior)
```


```{r, brill-spr}
ggplot(melt(sweep(lb["SPR"],c(1,3),lb["SPR","40"],"/")))+
  geom_boxplot(aes(ac(year),value))+
  scale_x_discrete(breaks=seq(20,60,10))+
  xlab("SPR")+ylab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of SPR for brill. 

```{r, brill-fm}
ggplot(melt(sweep(lb["FM"],c(1,3),lb["FM","40"],"/")))+
  geom_boxplot(aes(ac(year),value))+
  scale_x_discrete(breaks=seq(20,60,10))+
  xlab("F")+ylab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of $F/M$ for brill. 

## Ray
```{r, ray-om}
load(file.path(dirDat,"ray.RData"))

om=iter(om,1:500)
lh=iter(lh,1:500)
prior=iter(prior,1:500)

plot(om)
```
**Figure `r iFig=iFig+1; iFig`** Operating model for ray. 

```{r, ray-alk}
alk=setALK(lh)
```

```{r, ray-lfd}
lfd=lenSample(catch.n(om)[,20:65],alk,nsample=500)
```

```{r, ray-oemplot}
ggplot(melt(lfd[,seq(1,45,10),,,,1:4]))+
  geom_histogram(aes(length,weight=value),binwidth=1)+
  facet_grid(year~iter,scale="free")+
  xlab("Length (cm)")+ylab("Frequency")+
  coord_cartesian(xlim=c(0,mean(lh["linf"])))
```
**Figure `r iFig=iFig+1; iFig`** Observation error model for ray. 


```{r, ray-sa}
lb=lbspr(lfd,prior)
```

```{r, ray-spr}
ggplot(melt(sweep(lb["SPR"],c(1,3),lb["SPR","40"],"/")))+
  geom_boxplot(aes(ac(year),value))+
  xlab("SPR")+ylab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of SPR for ray. 

```{r, ray-fm}
ggplot(ddply(melt(sweep(lb["FM"],c(1,3),lb["FM","40"],"/")),.(iter), 
             transform, val=value/mean(value)))+
  geom_boxplot(aes(ac(year),value))+
  scale_x_discrete(breaks=seq(20,60,10))+
  xlab("F")+ylab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of $F/M$ for ray. 

## sprat
```{r, sprat-om}
load(file.path(dirDat,"sprat.RData"))

om=iter(om,1:500)
lh=iter(lh,1:500)
prior=iter(prior,1:500)

plot(om)
```
**Figure `r iFig=iFig+1; iFig`** Operating model for sprat. 

```{r, sprat-alk}
alk=setALK(lh)
```

```{r, sprat-lfd}
lfd=lenSample(catch.n(om)[,20:65],alk,nsample=500)
```

```{r, sprat-oemplot}
ggplot(melt(lfd[,seq(1,45,10),,,,1:4]))+
  geom_histogram(aes(length,weight=value),binwidth=1)+
  facet_grid(year~iter,scale="free")+
  xlab("Length (cm)")+ylab("Frequency")+
  coord_cartesian(xlim=c(0,mean(lh["linf"])))
```
**Figure `r iFig=iFig+1; iFig`** Observation error model for sprat. 


```{r, sprat-sa}
lb=lbspr(lfd,prior)
```

```{r, sprat-spr}
ggplot(melt(sweep(lb["SPR"],c(1,3),lb["SPR","40"],"/")))+
  geom_boxplot(aes(ac(year),value))+
  xlab("SPR")+ylab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of SPR for pollack. 

```{r, sprat-fm}
ggplot(melt(sweep(lb["FM"],c(1,3),lb["FM","40"],"/")))+
  geom_boxplot(aes(ac(year),value))+
  scale_x_discrete(breaks=seq(20,60,10))+
  xlab("F")+ylab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of $F/M$ for pollack. 

## pollack
```{r, pollack-om}
load(file.path(dirDat,"pollack.RData"))

om=iter(om,1:500)
lh=iter(lh,1:500)
prior=iter(prior,1:500)

plot(om)
```
**Figure `r iFig=iFig+1; iFig`** Operating model for pollack. 

```{r, pollack-alk}
alk=setALK(lh)
```

```{r, pollack-lfd}
lfd=lenSample(catch.n(om)[,20:65],alk,nsample=500)
```

```{r, pollack-oemplot}
ggplot(melt(lfd[,seq(1,45,10),,,,1:4]))+
  geom_histogram(aes(length,weight=value),binwidth=1)+
  facet_grid(year~iter,scale="free")+
  xlab("Length (cm)")+ylab("Frequency")+
  coord_cartesian(xlim=c(0,mean(lh["linf"])))
```
**Figure `r iFig=iFig+1; iFig`** Observation error model for pollack. 


```{r, pollack-sa}
lb=lbspr(lfd,prior)
```

```{r, pollack-spr}
ggplot(melt(sweep(lb["SPR"],c(1,3),lb["SPR","40"],"/")))+
  geom_boxplot(aes(ac(year),value))+
  xlab("SPR")+ylab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of SPR for pollack. 

```{r, pollack-fm}
ggplot(melt(sweep(lb["FM"],c(1,3),lb["FM","40"],"/")))+
  geom_boxplot(aes(ac(year),value))+
  scale_x_discrete(breaks=seq(20,60,10))+
  xlab("F")+ylab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of $F/M$ for pollack. 

## razor
```{r, razor-om}
load(file.path(dirDat,"razor.RData"))

om=iter(om,1:500)
lh=iter(lh,1:500)
prior=iter(prior,1:500)

plot(om)
```
**Figure `r iFig=iFig+1; iFig`** Operating model for razor. 

```{r, razor-alk}
alk=setALK(lh)
```

```{r, razor-lfd}
lfd=lenSample(catch.n(om)[,20:65],alk,nsample=500)
```

```{r, razor-oemplot}
ggplot(melt(lfd[,seq(1,45,10),,,,1:4]))+
  geom_histogram(aes(length,weight=value),binwidth=1)+
  facet_grid(year~iter,scale="free")+
  xlab("Length (cm)")+ylab("Frequency")+
  coord_cartesian(xlim=c(0,mean(lh["linf"])))
```
**Figure `r iFig=iFig+1; iFig`** Observation error model for razor. 


```{r, razor-sa}
lb=lbspr(lfd,prior)
```

```{r, razor-spr}
ggplot(melt(sweep(lb["SPR"],c(1,3),lb["SPR","40"],"/")))+
  geom_boxplot(aes(ac(year),value))+
  xlab("SPR")+ylab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of SPR for razors. 


```{r, razor-fm}
ggplot(melt(sweep(lb["FM"],c(1,3),lb["FM","40"],"/")))+
  geom_boxplot(aes(ac(year),value))+
  scale_x_discrete(breaks=seq(20,60,10))+
  xlab("F")+ylab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of $F/M$ for razors. 


## lobster
```{r, lobster-om}
#load(file.path(dirDat,"lobster.RData"))

om=iter(om,1:500)
lh=iter(lh,1:500)
prior=iter(prior,1:500)

plot(om)
```
**Figure `r iFig=iFig+1; iFig`** Operating model for lobster. 

```{r, lobster-alk}
alk=setALK(lh,lmax=1.50,cv=0.1)[-1]  
```

```{r, lobster-lfd}
lfd=lenSample(catch.n(om)[-1,20:65],alk,nsample=1000) 
```

```{r, lobster-oemplot}
ggplot(melt(lfd[,seq(1,45,10),,,,1:4]))+   
  geom_histogram(aes(length,weight=value),binwidth=1)+
  facet_grid(year~iter,scale="free")+
  xlab("Length (cm)")+ylab("Frequency")+
  coord_cartesian(xlim=c(0,mean(lh["linf"])*1.5))  
```
**Figure `r iFig=iFig+1; iFig`** Observation error model for lobster. 


```{r, lobster-sa}
lb=lbspr(lfd,prior)        
```

```{r, lobster-spr}
ggplot(melt(sweep(lb["SPR"],c(1,3),lb["SPR","40"],"/")))+   
  geom_boxplot(aes(ac(year),value))+
  xlab("SPR")+ylab("Year")+theme_bw()  
```
**Figure `r iFig=iFig+1; iFig`** Estimates of SPR for lobster. 

```{r, lobster-fm}
ggplot(melt(sweep(lb["FM"],c(1,3),lb["FM","40"],"/")))+  
  geom_boxplot(aes(ac(year),value))+
  scale_x_discrete(breaks=seq(20,60,10))+
  xlab("F")+ylab("Year")+theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Estimates of $F/M$ for lobster. 


```{r, fm, eval=FALSE}
len=t(daply(lfq,.(year,length), with, sum(freq)))  
brl=lbspr(len,prior[,1])  

save(brl,file="/home/laurence/Desktop/tmp/brl.RData")
ggplot(data.frame("Year"=21:40,
               "MP"=brl@Ests[,"FM"],
               "OM"=c(apply(harvest(om[,ac(21:40)])%/%m(om[,ac(21:40)]),c(2),mean))))+
  geom_line(aes(Year,OM),col="red")+
  geom_line(aes(Year,MP))
```

```{r, spr, eval=FALSE}
ggplot(data.frame("Year"=21:100,    
               "MP"=brl@Ests[,"SPR"],
               "OM"=c(apply(ssb(om[,ac(21:100)])%/%rec(om[,ac(21:100)]),c(2),mean))/1000))+
  geom_line(aes(Year,OM),col="red")+
  geom_line(aes(Year,MP))
```


```{r, oem-old}
# Length frequency distribution
om1=window(iter(om,1),start=21,end=100)  

n  =catch.n(om1)
ln =vonB(ages(catch.n(om1)),iter(lh,1))
sd =ln*0.2
bin=0:ceiling(max(ln)*1.10)+0.5

### Create lengths-at-age 
lfq=ddply(model.frame(FLQuants(ln=ln,sd=sd,n=n)),.(age,year,unit,season,area,iter), 
           with, data.frame(length=bin,data=dnorm(bin,ln,sd)*n))
  
### sum up by length 
lfq=ddply(lfq,.(length,year,unit,season,area,iter), 
           with, data.frame(freq=sum(data)))
```

```{r, oemplot-old, eval=FALSE}
ggplot(subset(lfq,year %in% seq(50,100,5)))+  
  geom_histogram(aes(length,weight=freq),binwidth=1)+
  facet_grid(year~.,scale="free")+
  xlab("Length (cm)")+ylab("Frequency")
```



\newpage
## Session Info

```{r}
sessionInfo()
```

## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLife:  `r packageVersion('FLife')`
* FLBRP:  `r packageVersion('FLBRP')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

