---
title: "Cross test using Operating Model based on Life History"
subtitle: "Biomass Dynamic and Stock Reduction Analysis"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
vignette: >
  %\VignetteIndexEntry{FLife}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
github_document:
    mathjax: TRUE
tags: FLife
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(cache     =TRUE,
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=10,
               fig.width =8,
               fig.path  ="../tex/simtest/bdsra-",
               cache.path="../cache/simtest/bdsra/")

options(digits=3)

iFig=0
```
```{r pkgs}
library(ggplot2)
library(reshape)
library(plyr)
library(dplyr)
library(FLCore)
library(ggplotFL)

library(mpb)
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy ="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat=file.path(dirMy,"data")
```

### Brill

```{r, brill}
load(file.path(dirDat,"brill-bd.RData"))

dpl =stock(bd,0.5)%/%params(bd)["k"]
dpl[,ac(c(22:52))]=NA

control(bd)["q1",2:4]=c(100,1000,10000)

sra=fit(bd,dpl)
```


```{r, brill-plot}
plot(as(list("SRA"=sra,"OM"=bd),"biodyns"))
```

**Figure `r iFig=iFig+1; iFig`,** Brill stock Reduction Analysis


### Turbot

```{r, turbot}
load(file.path(dirDat,"turbot-bd.RData"))

dpl =stock(bd,0.5)%/%params(bd)["k"]
dpl[,ac(c(22:52))]=NA

control(bd)["q1",2:4]=c(100,1000,10000)

sra=fit(bd,dpl)
```


```{r, turbot-plot}
plot(as(list("SRA"=sra,"OM"=bd),"biodyns"),probs=c(0.25,0.75))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`,** Turbot stock Reduction Analysis


### Ray

```{r, ray}
load(file.path(dirDat,"ray-bd.RData"))

dpl =stock(bd,0.5)%/%params(bd)["k"]
dpl[,ac(c(22:52))]=NA

control(bd)["q1",2:4]=c(100,1000,10000)

sra=fit(bd,dpl)
```


```{r, ray-plot}
plot(as(list("SRA"=sra,"MP"=hat,"OM"=bd),"biodyns"))
```

**Figure `r iFig=iFig+1; iFig`,** Ray stock Reduction Analysis

### Pollack

```{r, Pollack}
load(file.path(dirDat,"pollack-bd.RData"))

dpl =stock(bd,0.5)%/%params(bd)["k"]
dpl[,ac(c(22:52))]=NA

control(bd)["q1",2:4]=c(100,1000,10000)

sra=fit(bd,dpl)
```


```{r, pollack-plot}
plot(as(list("SRA"=sra,"MP"=hat,"OM"=bd),"biodyns"))
```

**Figure `r iFig=iFig+1; iFig`,** Pollack stock Reduction Analysis


### Sprat

```{r, sprat}
load(file.path(dirDat,"sprat-bd.RData"))

dpl =stock(bd,0.5)%/%params(bd)["k"]
dpl[,ac(c(22:52))]=NA

control(bd)["q1",2:4]=c(100,1000,10000)

sra=fit(bd,dpl)
```

```{r, sprat-plot}
plot(as(list("SRA"=sra,"MP"=hat,"OM"=bd),"biodyns"))
```

**Figure `r iFig=iFig+1; iFig`,** Sprat stock Reduction Analysis


### Lobster

```{r, lobster}
load(file.path(dirDat,"lobster-bd.RData"))

dpl =stock(bd,0.5)%/%params(bd)["k"]
dpl[,ac(c(22:52))]=NA

control(bd)["q1",2:4]=c(100,1000,10000)

sra=fit(bd,dpl)
```


```{r, lobster-plot}
plot(as(list("SRA"=sra,"MP"=hat,"OM"=bd),"biodyns"))
```

**Figure `r iFig=iFig+1; iFig`,** Lobster stock Reduction Analysis



### Razor

```{r, razor}
load(file.path(dirDat,"razor-bd.RData"))

dpl =stock(bd,0.5)%/%params(bd)["k"]
dpl[,ac(c(22:52))]=NA

control(bd)["q1",2:4]=c(100,1000,10000)

sra=fit(bd,dpl)
```


```{r, razor-plot}
plot(as(list("SRA"=sra,"MP"=hat,"OM"=bd),"biodyns"))
```

**Figure `r iFig=iFig+1; iFig`,** Razor stock Reduction Analysis

```{r, bd-fwd, eval=FALSE}
bdfwd=mlply(seq(75,50,-5),function(x) {
          hat=window(bd,            end=x)
          u  =window(stock(hat,0.5),end=x)
          
          params(hat)=params(hat)[1:4]
          setParams(hat)=u
          setControl(hat)=params(hat)
          hat=fit(hat,u)
          
          fwd(hat,catch=catch(bd)[,dim(u)[2]+0:10])})

bdfwd=as(bdfwd,"biodyns")
```


\newpage
## Session Info

```{r}
sessionInfo()
```

## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLife:  `r packageVersion('FLife')`
* FLBRP:  `r packageVersion('FLBRP')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

