---
title: "Cross test using Operating Model based on Life History"
subtitle: "MLZ, Estimate Z from Mean Length"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
vignette: >
  %\VignetteIndexEntry{FLife}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
github_document:
    mathjax: TRUE
tags: FLife
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(cache     =TRUE,
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=6,
               fig.width =8,
               fig.path  ="../tex/simtest/mlz-",
               cache.path="../cache/simtest/mlz/")

options(digits=3)

iFig=0
```
```{r pkgs}
library(plyr)
library(reshape)
library(ggplot2)
library(dplyr)

library(FLCore)
library(ggplotFL)
library(FLBRP)
library(FLife)
library(mydas)

library(MLZ)
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat=file.path(dirMy,"data")
```

```{r}
source('~/Desktop/sea++/mydas/pkgs/mydas/R/mlz.R')
source('~/Desktop/sea++/mydas/pkgs/mydas/R/omOut.R')
```


## Brill
```{r, brill-om}
load(file.path(dirDat,"lobster.RData"))

om   =iter(om,   1:500)
prior=iter(prior,1:500)

plot(om)   
```
**Figure `r iFig=iFig+1; iFig`** Operating model for brill. 

```{r, brill-length}
ts   =omSmry(om,eq,lh)
mnLen=as.FLQuant(with(ts,data.frame(data=cln,year=year,iter=iter)))

plot(mnLen)
```
**Figure `r iFig=iFig+1; iFig`** Mean length of catch brill. 

```{r, brill-mlz}
source('~/Desktop/sea++/mydas/pkgs/mydas/R/mlz.R')

res=mlz(mnLen[,ac(40:60)],prior)
```

```{r, brill-z}
ggplot(melt(model.frame(res$z)))+ 
  geom_boxplot(aes(x=variable,as.numeric(as.character(value))),outlier.colour = NA)+
  xlab("Block")+ylab("Z")+
  scale_y_continuous(limits=c(0,1))
```
**Figure `r iFig=iFig+1; iFig`** Zs

```{r, brill-y}
ggplot(model.frame(res$year))+ 
  geom_histogram(aes(y))+
  xlab("Year")+ylab("Count")
```
**Figure `r iFig=iFig+1; iFig`** Break


## Turbot
```{r, turbot-om}
load(file.path(dirDat,"lobster.RData"))

om   =iter(om,   1:500)
prior=iter(prior,1:500)

plot(om)   
```
**Figure `r iFig=iFig+1; iFig`** Operating model for turbot. 

```{r, turbot-length}
ts   =omSmry(om,eq,lh)
mnLen=as.FLQuant(with(ts,data.frame(data=cln,year=year,iter=iter)))

plot(mnLen)
```
**Figure `r iFig=iFig+1; iFig`** Mean length of catch turbot. 

```{r, turbot-mlz}
source('~/Desktop/sea++/mydas/pkgs/mydas/R/mlz.R')

res=mlz(mnLen[,ac(40:60)],prior)
```

```{r, turbot-z}
ggplot(melt(model.frame(res$z)))+ 
  geom_boxplot(aes(x=variable,as.numeric(as.character(value))),outlier.colour = NA)+
  xlab("Block")+ylab("Z")+
  scale_y_continuous(limits=c(0,1))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Zs

```{r, turbot-y}
ggplot(model.frame(res$year))+ 
  geom_histogram(aes(y))+
  xlab("Year")+ylab("Count")
```
**Figure `r iFig=iFig+1; iFig`** Break


## Ray
```{r, ray-om}
load(file.path(dirDat,"lobster.RData"))

om   =iter(om,   1:500)
prior=iter(prior,1:500)

plot(om)   
```
**Figure `r iFig=iFig+1; iFig`** Operating model for ray. 

```{r, ray-length}
ts   =omSmry(om,eq,lh)
mnLen=as.FLQuant(with(ts,data.frame(data=cln,year=year,iter=iter)))

plot(mnLen)
```
**Figure `r iFig=iFig+1; iFig`** Mean length of catch ray. 

```{r, ray-mlz}
source('~/Desktop/sea++/mydas/pkgs/mydas/R/mlz.R')

res=mlz(mnLen[,ac(40:60)],prior)
```

```{r, ray-z}
ggplot(melt(model.frame(res$z)))+ 
  geom_boxplot(aes(x=variable,as.numeric(as.character(value))),outlier.colour = NA)+
  xlab("Block")+ylab("Z")+
  scale_y_continuous(limits=c(0,1))
```
**Figure `r iFig=iFig+1; iFig`** Zs

```{r, ray-y}
ggplot(model.frame(res$year))+ 
  geom_histogram(aes(y))+
  xlab("Year")+ylab("Count")
```
**Figure `r iFig=iFig+1; iFig`** Break


## Pollack
```{r, pollack-om}
load(file.path(dirDat,"lobster.RData"))

om   =iter(om,   1:500)
prior=iter(prior,1:500)

plot(om)   
```
**Figure `r iFig=iFig+1; iFig`** Operating model for pollack. 

```{r, pollack-length}
ts   =omSmry(om,eq,lh)
mnLen=as.FLQuant(with(ts,data.frame(data=cln,year=year,iter=iter)))

plot(mnLen)
```
**Figure `r iFig=iFig+1; iFig`** Mean length of catch pollack. 

```{r, pollack-mlz}
source('~/Desktop/sea++/mydas/pkgs/mydas/R/mlz.R')

res=mlz(mnLen[,ac(40:60)],prior)
```

```{r, pollack-z}
ggplot(melt(model.frame(res$z)))+ 
  geom_boxplot(aes(x=variable,as.numeric(as.character(value))),outlier.colour = NA)+
  xlab("Block")+ylab("Z")+
  scale_y_continuous(limits=c(0,1))
```
**Figure `r iFig=iFig+1; iFig`** Zs

```{r, pollack-y}
ggplot(model.frame(res$year))+ 
  geom_histogram(aes(y))+
  xlab("Year")+ylab("Count")
```
**Figure `r iFig=iFig+1; iFig`** Break


## Sprat
```{r, sprat-om}
load(file.path(dirDat,"lobster.RData"))

om   =iter(om,   1:500)
prior=iter(prior,1:500)

plot(om)   
```
**Figure `r iFig=iFig+1; iFig`** Operating model for sprat. 

```{r, sprat-length}
ts   =omSmry(om,eq,lh)
mnLen=as.FLQuant(with(ts,data.frame(data=cln,year=year,iter=iter)))

plot(mnLen)
```
**Figure `r iFig=iFig+1; iFig`** Mean length of catch sprat. 

```{r, sprat-mlz}
source('~/Desktop/sea++/mydas/pkgs/mydas/R/mlz.R')

res=mlz(mnLen[,ac(40:60)],prior)
```

```{r, sprat-z}
ggplot(melt(model.frame(res$z)))+ 
  geom_boxplot(aes(x=variable,as.numeric(as.character(value))),outlier.colour = NA)+
  xlab("Block")+ylab("Z")+
  scale_y_continuous(limits=c(0,1))
```
**Figure `r iFig=iFig+1; iFig`** Zs

```{r, sprat-y}
ggplot(model.frame(res$year))+ 
  geom_histogram(aes(y))+
  xlab("Year")+ylab("Count")
```
**Figure `r iFig=iFig+1; iFig`** Break


## Razors
```{r, razor-om}
load(file.path(dirDat,"lobster.RData"))

om   =iter(om,   1:500)
prior=iter(prior,1:500)

plot(om)   
```
**Figure `r iFig=iFig+1; iFig`** Operating model for razor. 

```{r, razor-length}
ts   =omSmry(om,eq,lh)
mnLen=as.FLQuant(with(ts,data.frame(data=cln,year=year,iter=iter)))

plot(mnLen)
```
**Figure `r iFig=iFig+1; iFig`** Mean length of catch razor. 

```{r, razor-mlz}
source('~/Desktop/sea++/mydas/pkgs/mydas/R/mlz.R')

res=mlz(mnLen[,ac(40:60)],prior)
```

```{r, razor-z}
ggplot(melt(model.frame(res$z)))+ 
  geom_boxplot(aes(x=variable,as.numeric(as.character(value))),outlier.colour = NA)+
  xlab("Block")+ylab("Z")+
  scale_y_continuous(limits=c(0,1))
```
**Figure `r iFig=iFig+1; iFig`** Zs

```{r, razor-y}
ggplot(model.frame(res$year))+ 
  geom_histogram(aes(y))+
  xlab("Year")+ylab("Count")
```
**Figure `r iFig=iFig+1; iFig`** Break


## Lobster
```{r, lobster-om}
load(file.path(dirDat,"lobster.RData"))

om   =iter(om,   1:500)
prior=iter(prior,1:500)

plot(om)   
```
**Figure `r iFig=iFig+1; iFig`** Operating model for lobster. 

```{r, lobster-length}
ts   =omSmry(om,eq,lh)
mnLen=as.FLQuant(with(ts,data.frame(data=cln,year=year,iter=iter)))

plot(mnLen)
```
**Figure `r iFig=iFig+1; iFig`** Mean length of catch lobster. 

```{r, lobster-mlz}
source('~/Desktop/sea++/mydas/pkgs/mydas/R/mlz.R')

res=mlz(mnLen[,ac(40:60)],prior)
```

```{r, lobster-z}
ggplot(melt(model.frame(res$z)))+ 
  geom_boxplot(aes(x=variable,as.numeric(as.character(value))),outlier.colour = NA)+
  xlab("Block")+ylab("Z")+
  scale_y_continuous(limits=c(0,1))
```
**Figure `r iFig=iFig+1; iFig`** Zs

```{r, lobster-y}
ggplot(model.frame(res$year))+ 
  geom_histogram(aes(y))+
  xlab("Year")+ylab("Count")
```
**Figure `r iFig=iFig+1; iFig`** Break



\newpage
## Session Info

```{r}
sessionInfo()
```

## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLife:  `r packageVersion('FLife')`
* FLBRP:  `r packageVersion('FLBRP')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

