---
title: "Simulation test using Operating Model based on Life History"
subtitle: "Biomass Dynamic"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
vignette: >
  %\VignetteIndexEntry{FLife}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
github_document:
    mathjax: TRUE
tags: FLife
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(cache     =TRUE,
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=9,
               fig.width =8,               
               cache.path="../cache/simtest/bd",
               fig.path  ="../tex/simtest/bd-")

options(digits=3)

iFig=0
```
```{r pkgs}
library(ggplot2)
library(reshape)
library(plyr)
library(dplyr)
library(FLCore)
library(ggplotFL)

library(mpb)
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy ="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat=file.path(dirMy,"data")
```

## Simulation tests

```{r, brill}
load(file.path(dirDat,"brill.RData"))

om=window(om,start=20,end=55)
bd=as(om,"biodyn")

params(bd)["r"] =0.5 
params(bd)["k"] =1000
params(bd)["b0"]=0.8 
params(bd)["p"] =median(c(mpb:::p(prior["bmsy"]/prior["v"])))

u               =stock(bd,0.5)
setParams(bd)   =u
setControl(bd)  =params(bd)

hat              =fit(bd,u)
```

```{r, brill-plot}
plot(as(list("MP"=hat,"OM"=bd),"biodyns"),probs=c(0.25,0.75))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`,** Simulation test of biomass dyanmic assessment for brill.

```{r}
save(bd,hat,prior,file=file.path(dirDat,"brill-bd.RData"),compress="xz")
```

### Turbot

```{r, turbot}
load(file.path(dirDat,"turbot.RData"))

om=window(om,start=20,end=55)
bd=as(om,"biodyn")

params(bd)["r"] =median(c(prior["r"]))
params(bd)["k"] =1000
params(bd)["b0"]=0.8 
params(bd)["p"] =median(c(mpb:::p(prior["bmsy"]/prior["v"])))

u               =stock(bd,0.5)
setParams(bd)   =u
setControl(bd)  =params(bd)

hat             =fit(bd,u)

plot(as(list("MP"=hat,"OM"=bd),"biodyns"),probs=c(0.25,0.75))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`,** Simulation test of biomass dyanmic assessment for turbot.

```{r}
save(bd,hat,prior,file=file.path(dirDat,"turbot-bd.RData"),compress="xz")
```

### Ray

```{r, ray}
load(file.path(dirDat,"ray.RData"))

om=window(om,start=20,end=55)
bd=as(om,"biodyn")

params(bd)["r"] =median(c(prior["r"]))
params(bd)["k"] =1000
params(bd)["b0"]=0.8 
params(bd)["p"] =median(c(mpb:::p(prior["bmsy"]/prior["v"])))

u               =stock(bd,0.5)
setParams(bd)   =u
setControl(bd)  =params(bd)

hat              =fit(bd,u)

plot(as(list("MP"=hat,"OM"=bd),"biodyns"),probs=c(0.25,0.75))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`,** Simulation test of biomass dyanmic assessment for ray.

```{r}
save(bd,hat,prior,file=file.path(dirDat,"ray-bd.RData"),compress="xz")
```

### Pollack

```{r, pollack}
load(file.path(dirDat,"pollack.RData"))

om=window(om,start=20,end=55)
bd=as(om,"biodyn")

params(bd)["r"] =median(c(prior["r"]))
params(bd)["k"] =1000
params(bd)["b0"]=0.8 
params(bd)["p"] =median(c(mpb:::p(prior["bmsy"]/prior["v"])))

u               =stock(bd,0.5)
setParams(bd)   =u
setControl(bd)  =params(bd)

hat              =fit(bd,u)

plot(as(list("MP"=hat,"OM"=bd),"biodyns"),probs=c(0.25,0.75))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`,** Simulation test of biomass dyanmic assessment for pollack.

```{r}
save(bd,hat,prior,file=file.path(dirDat,"pollack-bd.RData"),compress="xz")
```

### Sprat

```{r, sprat}
load(file.path(dirDat,"sprat.RData"))

om=window(om,start=20,end=55)
bd=as(om,"biodyn")

params(bd)["r"] =median(c(prior["r"]))
params(bd)["k"] =1000
params(bd)["b0"]=0.8 
params(bd)["p"] =median(c(mpb:::p(prior["bmsy"]/prior["v"])))

u               =stock(bd,0.5)
setParams(bd)   =u
setControl(bd)  =params(bd)

hat              =fit(bd,u)

plot(as(list("MP"=hat,"OM"=bd),"biodyns"),probs=c(0.25,0.75))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`,** Simulation test of biomass dyanmic assessment for sprat.

```{r}
save(bd,hat,prior,file=file.path(dirDat,"sprat-bd.RData"),compress="xz")
```

### Lobster

```{r, lobster}
load(file.path(dirDat,"lobster.RData"))

om=window(om,start=20,end=55)
bd=as(om,"biodyn")

params(bd)["r"] =median(c(prior["r"]))
params(bd)["k"] =1000
params(bd)["b0"]=0.8 
params(bd)["p"] =median(c(mpb:::p(prior["bmsy"]/prior["v"])))

u               =stock(bd,0.5)
setParams(bd)   =u
setControl(bd)  =params(bd)

hat              =fit(bd,u)

plot(as(list("MP"=hat,"OM"=bd),"biodyns"),probs=c(0.25,0.75))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`,** Simulation test of biomass dyanmic assessment for lobster.


```{r}
save(bd,hat,prior,file=file.path(dirDat,"lobster-bd.RData"),compress="xz")
```

### Razor

```{r, razor}
load(file.path(dirDat,"razor.RData"))

om=window(om,start=20,end=55)
bd=as(om,"biodyn")

params(bd)["r"] =median(c(prior["r"]))
params(bd)["k"] =1000
params(bd)["b0"]=0.8 
params(bd)["p"] =median(c(mpb:::p(prior["bmsy"]/prior["v"])))

u               =stock(bd,0.5)
setParams(bd)   =u
setControl(bd)  =params(bd)

hat              =fit(bd,u)

plot(as(list("MP"=hat,"OM"=bd),"biodyns"),probs=c(0.25,0.75))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`,** Simulation test of biomass dyanmic assessment for razor.

```{r}
save(bd,hat,prior,file=file.path(dirDat,"razor-bd.RData"),compress="xz")
```

```{r, prod, fig.height=6,fig.width=8}
plotProduction(iter(hat,1))+
  geom_path(aes(stock,catch),data=model.frame(mcf(FLQuants(iter(hat,1),"stock"=stock,"catch"=catch))))
```

**Figure `r iFig=iFig+1; iFig`,** Biomass dynamic production function.


```{r, bd-fwd, eval=FALSE}
bd=biodyn(window(om,start=25))

params(bd)["r"] =0.2 #mean(prior[c("r")])
params(bd)["b0"]=0.8 
params(bd)["k"] =1200
params(bd)["p"] =0.00000000001

bdfwd=mlply(seq(65,40,-5),function(x) {
          hat=window(bd,            end=x)
          u  =window(stock(hat,0.5),end=x)
          
          params(hat)=params(hat)[1:4]
          setParams(hat)=u
          setControl(hat)=params(hat)
          hat=fit(hat,u)
          
          fwd(hat,catch=catch(bd)[,dim(u)[2]+0:10])})

bdfwd=as(bdfwd,"biodyns")

plot(bdfwd)
```

**Figure `r iFig=iFig+1; iFig`,** Biomass dynamic


**Figure `r iFig=iFig+1; iFig`,** Biomass dynamic


\newpage
## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLife:  `r packageVersion('FLife')`
* FLBRP:  `r packageVersion('FLBRP')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

## Session Info

```{r}
sessionInfo()
```

