---
title: "Summary of OMs"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{FLife}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
github_document:
    mathjax: TRUE
tags: FLife
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(cache     =TRUE,
               cache.path="../cache/smry-om/",
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=12,
               fig.width =12,
               fig.path  ="../tex/smry-om")

options(digits=3)

iFig=0
```
```{r pkgs}
library(plyr)
library(reshape)
library(ggplot2)
library(dplyr)

library(FLCore)
library(ggplotFL)
library(FLBRP)
library(FLife)
library(mydas)
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat=file.path(dirMy,"data")
```

```{r, funcs}
library(GGally)
 
my_density <- function(data,mapping,...){
   ggplot(data=data,mapping=mapping)+
     geom_density(...,lwd=1)}
 
 my_smooth <- function(data,mapping,...){
   ggplot(data=data,mapping=mapping)+
     geom_smooth(...,method="lm",se=FALSE)+
     geom_point(...)}
```

## Turbot
```{r, turbot}
load(file.path(dirDat,"turbot.RData"))

#source('~/Desktop/flr/FLife/R/omOut.R')

res=omSmry(om,eq,lh)
res=transform(subset(res,year%in%20:90),increase=(year%in%20:49))
res=res[sample(seq(dim(res)[1]),100),]

ggpairs(res[,c(3:5,8,6:7,18:22)],
         mapping = ggplot2::aes(color=increase),
         upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
         lower = list(continuous = wrap(my_smooth,size=1)),
         #diag = list(continuous = wrap("densityDiag",alpha=.1)),
         diag=list(continuous=wrap(my_density,alpha=0.2)),
         title = "")+theme_bw(14)+
   theme(legend.position ="none", 
         panel.grid.major =element_blank(), 
         axis.ticks       =element_blank(), 
         axis.text.x      =element_blank(), 
         axis.text.y      =element_blank(),
         panel.border     =element_rect(linetype = 1, 
                                        colour="black", fill=NA))
```
**Figure `r iFig=iFig+1; iFig`** Operating model quantities for turbot. 

```{r,fig.height=5,fig.width=8}
ggduo(
  res,
  c(3:4,8), c(20:21),
  mapping = aes(color = increase),
  types = list(continuous = "smooth_lm",
      alpha = 0.7,
      line_color = "blue",
      line_size = 3))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Correlation with length for turbot. 


## Brill
```{r, brill}
load(file.path(dirDat,"brill.RData"))

res=omSmry(om,eq,lh)
res=transform(subset(res,year%in%20:90),increase=(year%in%20:49))
res=res[sample(seq(dim(res)[1]),100),]

ggpairs(res[,c(3:5,8,6:7,18:22)],
         mapping = ggplot2::aes(color=increase),
         upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
         lower = list(continuous = wrap(my_smooth,size=1)),
         #diag = list(continuous = wrap("densityDiag",alpha=.1)),
         diag=list(continuous=wrap(my_density,alpha=0.2)),
         title = "")+theme_bw(14)+
   theme(legend.position ="none", 
         panel.grid.major =element_blank(), 
         axis.ticks       =element_blank(), 
         axis.text.x      =element_blank(), 
         axis.text.y      =element_blank(),
         panel.border     =element_rect(linetype = 1, 
                                        colour="black", fill=NA))
```
**Figure `r iFig=iFig+1; iFig`** Operating model quantities for brill. 


```{r,fig.height=5,fig.width=8}
ggduo(
  res,
  c(3:4,8), c(20:21),
  mapping = aes(color = increase),
  types = list(continuous = "smooth_lm",
      alpha = 0.7,
      line_color = "blue",
      line_size = 3))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Correlation with length for brill. 


## Ray
```{r, ray}
load(file.path(dirDat,"ray.RData"))

res=omSmry(om,eq,lh)
res=transform(subset(res,year%in%20:90),increase=(year%in%20:49))
res=res[sample(seq(dim(res)[1]),100),]

ggpairs(res[,c(3:5,8,6:7,18:22)],
         mapping = ggplot2::aes(color=increase),
         upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
         lower = list(continuous = wrap(my_smooth,size=1)),
         #diag = list(continuous = wrap("densityDiag",alpha=.1)),
         diag=list(continuous=wrap(my_density,alpha=0.2)),
         title = "")+theme_bw(14)+
   theme(legend.position ="none", 
         panel.grid.major =element_blank(), 
         axis.ticks       =element_blank(), 
         axis.text.x      =element_blank(), 
         axis.text.y      =element_blank(),
         panel.border     =element_rect(linetype = 1, 
                                        colour="black", fill=NA))
```
**Figure `r iFig=iFig+1; iFig`** Operating model quantities for ray. 


```{r,fig.height=5,fig.width=8}
ggduo(
  res,
  c(3:4,8), c(20:21),
  mapping = aes(color = increase),
  types = list(continuous = "smooth_lm",
      alpha = 0.7,
      line_color = "blue",
      line_size = 3))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Correlation with length for ray. 


## Pollack
```{r, pollack}
load(file.path(dirDat,"pollack.RData"))

res=omSmry(om,eq,lh)
res=transform(subset(res,year%in%20:90),increase=(year%in%20:49))
res=res[sample(seq(dim(res)[1]),100),]

ggpairs(res[,c(3:5,8,6:7,18:22)],
         mapping = ggplot2::aes(color=increase),
         upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
         lower = list(continuous = wrap(my_smooth,size=1)),
         #diag = list(continuous = wrap("densityDiag",alpha=.1)),
         diag=list(continuous=wrap(my_density,alpha=0.2)),
         title = "")+theme_bw(14)+
   theme(legend.position ="none", 
         panel.grid.major =element_blank(), 
         axis.ticks       =element_blank(), 
         axis.text.x      =element_blank(), 
         axis.text.y      =element_blank(),
         panel.border     =element_rect(linetype = 1, 
                                        colour="black", fill=NA))
```
**Figure `r iFig=iFig+1; iFig`** Operating model quantities for pollack. 


```{r,fig.height=5,fig.width=8}
ggduo(
  res,
  c(3:4,8), c(20:21),
  mapping = aes(color = increase),
  types = list(continuous = "smooth_lm",
      alpha = 0.7,
      line_color = "blue",
      line_size = 3))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Correlation with length for pollack. 

## Sprat
```{r, sprat}
load(file.path(dirDat,"sprat.RData"))

res=omSmry(om,eq,lh)
res=transform(subset(res,year%in%20:90),increase=(year%in%20:49))
res=res[sample(seq(dim(res)[1]),100),]

ggpairs(res[,c(3:5,8,6:7,18:22)],
         mapping = ggplot2::aes(color=increase),
         upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
         lower = list(continuous = wrap(my_smooth,size=1)),
         #diag = list(continuous = wrap("densityDiag",alpha=.1)),
         diag=list(continuous=wrap(my_density,alpha=0.2)),
         title = "")+theme_bw(14)+
   theme(legend.position ="none", 
         panel.grid.major =element_blank(), 
         axis.ticks       =element_blank(), 
         axis.text.x      =element_blank(), 
         axis.text.y      =element_blank(),
         panel.border     =element_rect(linetype = 1, 
                                        colour="black", fill=NA))
```
**Figure `r iFig=iFig+1; iFig`** Operating model quantities for sprat. 


```{r,fig.height=5,fig.width=8}
ggduo(
  res,
  c(3:4,8), c(20:21),
  mapping = aes(color = increase),
  types = list(continuous = "smooth_lm",
      alpha = 0.7,
      line_color = "blue",
      line_size = 3))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Correlation with length for sprat. 


## Razor
```{r, razor}
load(file.path(dirDat,"razor.RData"))

res=omSmry(om,eq,lh)
res=transform(subset(res,year%in%20:90),increase=(year%in%20:49))
res=res[sample(seq(dim(res)[1]),100),]

ggpairs(res[,c(3:5,8,6:7,18:22)],
         mapping = ggplot2::aes(color=increase),
         upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
         lower = list(continuous = wrap(my_smooth,size=1)),
         #diag = list(continuous = wrap("densityDiag",alpha=.1)),
         diag=list(continuous=wrap(my_density,alpha=0.2)),
         title = "")+theme_bw(14)+
   theme(legend.position ="none", 
         panel.grid.major =element_blank(), 
         axis.ticks       =element_blank(), 
         axis.text.x      =element_blank(), 
         axis.text.y      =element_blank(),
         panel.border     =element_rect(linetype = 1, 
                                        colour="black", fill=NA))
```
**Figure `r iFig=iFig+1; iFig`** Operating model quantities for razor clams. 


```{r,fig.height=5,fig.width=8}
ggduo(
  res,
  c(3:4,8), c(20:21),
  mapping = aes(color = increase),
  types = list(continuous = "smooth_lm",
      alpha = 0.7,
      line_color = "blue",
      line_size = 3))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Correlation with length for razor clams. 


## Lobster
```{r, lobster}
load(file.path(dirDat,"lobster.RData"))

res=omSmry(om,eq,lh)
res=transform(subset(res,year%in%20:90),increase=(year%in%20:49))
res=res[sample(seq(dim(res)[1]),100),]

ggpairs(res[,c(3:5,8,6:7,18:22)],
         mapping = ggplot2::aes(color=increase),
         upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
         lower = list(continuous=wrap(my_smooth,size=1)),
         #diag = list(continuous = wrap("densityDiag",alpha=.1)),
         diag=list(continuous=wrap(my_density,alpha=0.2)),
         title = "")+theme_bw(14)+
   theme(legend.position ="none", 
         panel.grid.major =element_blank(), 
         axis.ticks       =element_blank(), 
         axis.text.x      =element_blank(), 
         axis.text.y      =element_blank(),
         panel.border     =element_rect(linetype = 1, 
                                        colour="black", fill=NA))
```
**Figure `r iFig=iFig+1; iFig`** Operating model quantities for lobster. 


```{r,fig.height=5,fig.width=8}
ggduo(
  res,
  c(3:4,8), c(20:21),
  mapping = aes(color = increase),
  types = list(continuous = "smooth_lm",
      alpha = 0.7,
      line_color = "blue",
      line_size = 3))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Correlation with length for lobster. 

\newpage
## Session Info

```{r}
sessionInfo()
```

## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLife:  `r packageVersion('FLife')`
* FLBRP:  `r packageVersion('FLBRP')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

