---
title: "Biodyn"
subtitle: "Biomass Dynamic"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{FLife}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
github_document:
    mathjax: TRUE
tags: FLife
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(cache     =TRUE,
               cache.path="../cache/spict/",
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=9,
               fig.width =8,
               fig.path  ="../tex/spict")

options(digits=3)

iFig=0
```
```{r pkgs}
library(ggplot2)
library(reshape)
library(plyr)
library(dplyr)
library(FLCore)
library(ggplotFL)

library(mpb)
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy ="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat=file.path(dirMy,"data")
```


```{r, brill}
load("/home/laurence/Desktop/sea++/mydas/tasks/task2/data/bio.RData")

dat=subset(bioCs,stock=="meg_rock_2016")

bd=biodyn(catch=as.FLQuant(transmute(subset(dat,fleet==1),data=obs,year=year)))
u =as.FLQuant(transmute(subset(dat,fleet!=1),data=obs,year=as.integer(year)))
u =window(u,end=2015)

params(bd)["k"]=20000
params(bd)["r"]=0.5
params(bd)["p"]=-0.5
params(bd)["b0"]=0.5

bd=fwd(bd,catch=catch(bd))
setParams(bd)   =u
setControl(bd)  =params(bd)

hat              =fit(bd,u)

plot(hat)
```

**Figure `r iFig=iFig+1; iFig`,** Biomass dyanmic assessment


\newpage
## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLife:  `r packageVersion('FLife')`
* FLBRP:  `r packageVersion('FLBRP')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

## Session Info

```{r}
sessionInfo()
```

