---
title: "Random Grid"
subtitle: "MSE"
author: "L Kell & A Tidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="../tex/rg-",
               cache.path="../cache/rg/")

iFig=0
iTab=0
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat="/home/laurence/Desktop/Dropbox/mydasOMs/data"
dirRes="/home/laurence/Desktop/Dropbox/mydasOMs/results"

nits=1000
```
```{r, pkgs}
library(ggplot2)
library(plyr)
library(dplyr)
library(reshape)
library(GGally)

library(FLCore)
library(FLBRP)
library(FLasher)
library(ggplotFL)
library(FLife)
```
```{r devs}
nits=500
set.seed(1233)
srDev=FLife:::rlnoise(nits,FLQuant(0,dimnames=list(year=1:105)),.3,b=0.0)
```

## Life history parameters

```{r, lh}
load(file.path(dirDat,"brill.RData"))
par=model.frame(lh)
nms=dimnames(par)$params
par=FLPar(apply(lh,1,mean)[nms])
load(file.path(dirDat,"turbot.RData"))
par=cbind(par,FLPar(apply(lh,1,mean)[nms]))
load(file.path(dirDat,"ray.RData"))
par=cbind(par,FLPar(apply(lh,1,mean)[nms]))
load(file.path(dirDat,"pollack.RData"))
par=cbind(par,FLPar(apply(lh,1,mean)[nms]))
load(file.path(dirDat,"sprat.RData"))
par=cbind(par,FLPar(apply(lh,1,mean)[nms]))
load(file.path(dirDat,"lobster.RData"))
par=cbind(par,FLPar(apply(lh,1,mean)[nms]))
load(file.path(dirDat,"razor.RData"))
par=cbind(par,FLPar(apply(lh,1,mean)[nms]))
dimnames(par)$iter=c("brill","turbot","ray","pollack","sprat","lobster","razor")

my_smooth <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_point(...,size=.5)+
    geom_smooth(...,method="lm",se=FALSE)}

my_density <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_density(...,lwd=1)}

theme_set(theme_bw(base_size=20))

p=ggpairs(model.frame(par[c(1:3,5,7)])[,-6],
        lower = list(continuous = wrap(my_smooth)),
        diag=list(continuous=wrap(my_density,alpha=0.2)),
        title = "")+
  theme(legend.position ="none",
        panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.x      =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
p
```

**Figure `r iFig=iFig+1; iFig`** Pairwise scatter plots of life history parameters.



## Equilibrium dynamics

The parameters are then used by `lhEql` to simulate the equilibrium dynamics by combining the spawner/yield per recruit relationships with a stock recruiment relationship.

```{r, eqRun}
eq=lhEql(par,spwn=0)
```


```{r vectors}
sel<-function(x) 
  catch.sel(x)%/%fapex(catch.sel(x))

dat=FLQuants(eq,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Mass"=stock.wt)

ggplot(subset(as.data.frame(dat),age<=10))+
  geom_line(aes(age,data,col=dimnames(par)$iter[iter]))+
  facet_wrap(~qname,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")+
  theme(legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`** Vectors.


```{r, eq}
plot(eq,refpts=FALSE)  
```

**Figure `r iFig=iFig+1; iFig`** Equilibrum Curves.

## Population dynamics

```{r om}
#http://www.fishbase.org/manual/Key%20Facts.htm

gTime=aaply(par,2,function(x) round(FLife:::genTime(FLPar(x))))

fbar=as.FLQuant(mdply(data.frame(iter=1:7), function(iter) 
                   data.frame(year=1:105,
                              data=c(rep(.1,19),seq(.1,2,length.out=30),
                                                seq(2.0,1,length.out=gTime[iter])[-1],
                                                rep(1,61))[1:105])))

eq@fbar=fbar%*%refpts(eq)["msy","harvest"]

om=as(eq,"FLStock")
om=fwd(om,f=fbar(om)[,-1],sr=eq)
lh=par
save(lh,eq,om,file=file.path(dirDat,"om7.RData"),compress="xz")

plot(om)
```

**Figure `r iFig=iFig+1; iFig`** Time series.

```{r ts}
plot(FLQuants(om, 
          "ssb" = function(x) ssb(x)%/%refpts( eq)["msy","ssb"], 
          "f" =   function(x) fbar(x)%/%refpts(eq)["msy","harvest"], 
          "rec" = function(x) rec(x)%/%refpts( eq)["msy","rec"], 
          "catch"=function(x) landings(x)%/%refpts(eq)["msy","yield"])) + 
  geom_hline(aes(yintercept=1),col="red") 
```

**Figure `r iFig=iFig+1; iFig`** Time series relative to MSY benchmarks.

```{r}
library(doParallel)
library(foreach)

registerDoParallel(2)

library(mydas)

mseStart=            c("brill"=54,"turbot"=54,"ray"=60,"pollack"=56,"sprat"=52,
                       "razor"=54,"lobster"=57)
scen=expand.grid(spp=c("brill",   "turbot",   "ray",   "pollack",   "sprat",   
                       "razor",   "lobster"),
                 stringsAsFactors=FALSE)

### Stochasticity
set.seed(12345)
nits=500

srDev=FLife:::rlnoise(nits,FLQuant(0,dimnames=list(year=1:105)),0.2,b=0.0)
uDev =FLife:::rlnoise(nits,FLQuant(0,dimnames=list(year=1:105)),0.3,b=0.0)

control=rbind(FLPar(k1   =runif(nits, 0.0, 1.0)),
              FLPar(k2   =runif(nits, 0.0, 1.0)),
              FLPar(gamma=runif(nits, 1, 1)))

empD=NULL
empD<-foreach(i=(seq(dim(scen)[1])), 
             .combine=rbind,
             .multicombine=TRUE,
             .packages=c("plyr","dplyr","reshape","ggplot2","FLCore","ggplotFL",
                         "FLasher","FLBRP","FLife")) %dopar%{

  om.=propagate(FLCore:::iter(om,i),nits)
  eq.=propagate(FLCore:::iter(eq,i),nits)
  lh.=propagate(FLCore:::iter(lh,i),nits)
  
  mse=mseSBTD(om.,eq.,
              control=control,
              srDev=srDev,uDev=uDev,
              start  =mseStart[scen[i,"spp"]]+5,end=mseStart[scen[i,"spp"]]+45,nyrs=5)
  res=cbind(spp=scen[i,"spp"],omSmry(mse,eq.,lh.))
  
  save(res,file=file.path(dirRes,paste("omd-2-",i,".RData",sep="")))
  
  res}

empD.=empD
empD$spp =ac(empD$spp)
empD     =subset(empD,year>=mseStart[empD$spp]&year<=mseStart[empD$spp]+45)
empD$year=empD$year-mseStart[empD$spp]

empd_pm=ddply(empD,.(spp,iter), smryStat)

save(empD,empd_pm,control,file=file.path(dirRes,"omd-results-2.RData"))
```

\newpage
## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLasher:   `r packageVersion('FLasher')`
* FLife:     `r packageVersion('FLife')`
* ggplotFL:  `r packageVersion('ggplotFL')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
```

