---
title: "Spectra"
author: "L Kell & A Tidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="../tex/rg-",
               cache.path="../cache/rg/")

iFig=0
iTab=0
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
#dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat="/home/laurence/Desktop/Dropbox/mydasOMs/data"
dirRes="/home/laurence/Desktop/Dropbox/mydasOMs/results"
```
```{r, pkgs}
library(ggplot2)
library(plyr)
library(dplyr)
library(reshape)
library(GGally)

library(FLCore)
library(FLBRP)
library(FLasher)
library(ggplotFL)
library(FLife)
```

```{r, lh}
load(file.path(dirDat,"brill.RData"))
oms=FLStocks("brill"=om)
load(file.path(dirDat,"turbot.RData"))
oms["turbot"]=om
load(file.path(dirDat,"ray.RData"))
oms["ray"]=om
load(file.path(dirDat,"pollack.RData"))
oms["pollack"]=om
load(file.path(dirDat,"sprat.RData"))
oms["sprat"]=om
load(file.path(dirDat,"lobster.RData"))
oms["lobster"]=om
load(file.path(dirDat,"razor.RData"))
oms["razor"]=om

plot(oms)
```

**Figure `r iFig=iFig+1; iFig`** 

```{r}
dat=ldply(oms,function(x) adply(ssb(window(x,start=65)),6,function(x) acf(x,plot=FALSE,max.lag=15)$acf))
#dat[,3:19]=scale(dat[,3:19])
dat=dat[,-(19:20)]

d<- dist(dat[,-(1:2)], method = "euclidean") # distance matrix
fit <- hclust(d, method="ward")
plot(fit) # display dendogram
groups <- cutree(fit, k=5) # cut tree into 5 clusters
# draw dendogram with red borders around the 5 clusters
rect.hclust(fit, k=5, border="red") 

dat=cbind(dat,group=groups)
dat=dat[,c(1,2,19,3:18)]

dt=melt(dat,id=c(".id","iter","group"))

dt=transform(dt,var=as.numeric(substr(ac(variable),2,nchar(ac(variable)))))

ggplot(dt)+
  geom_boxplot(aes(as.factor(var),value))+
  facet_grid(group~.)
```

```{r}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/empd-results.RData")

ctrl=rbind(cbind(j=1,model.frame(controlD[[1]])),
           cbind(j=2,model.frame(controlD[[2]])),
           cbind(j=3,model.frame(controlD[[3]])),
           cbind(j=4,model.frame(controlD[[4]])))
ctrl$iter=as.numeric(as.character(ctrl$iter))
emp=merge(empd_pm[,-(30:32)],ctrl,by=c("iter","j"))

grp=dat[,c(".id","iter","group")]
names(grp)[1]="spp"

dt3=merge(emp,grp,by=c("spp","iter"))
dt3=transform(dt3,k1.=cut(k1,breaks=seq(0,1,0.05)),
                  k2.=cut(k2,breaks=seq(0,1,0.05)))

minMax<-function(x,na.rm=TRUE) (x-min(x,na.rm=na.rm))/diff(range(x,na.rm=na.rm))

dt4=ddply(dt3,.(group,k1.,k2.), with, data.frame(kobe  =mean(kobe.n),
                                               safety=mean(safety),
                                               yield =mean(yield),
                                               aav   =(mean(yieldAav))))
dt4=melt(dt4,id=c("group","k1.","k2."))
dt4=ddply(dt4,.(variable), transform, value=minMax(value))

mycol=rev(c("navy","blue","cyan","lightcyan","yellow","red","red4"))
ggplot(dt4)+
  geom_tile(aes(k1.,k2.,fill=value))+
  scale_fill_gradientn(colours=mycol)+
  facet_grid(group~variable)

ggplot(dt4 , aes(x=k1., y=k2.)) +
  geom_raster(aes(fill=kb), interpolate=TRUE) +
  scale_fill_gradient2(high="navy", mid="white", low="red", 
                       midpoint=0.5, limits=range(dt4$kb))

dt5=ddply(dt3,.(spp,k1.,k2.), with, data.frame(kobe  =mean(kobe.n),
                                               safety=mean(safety),
                                               yield =mean(yield),
                                               aav   =(mean(yieldAav))))
dt5=melt(dt5,id=c("spp","k1.","k2."))
dt5=ddply(dt5,.(variable), transform, value=minMax(value))

ggplot(dt5)+
  geom_tile(aes(k1.,k2.,fill=value))+
  scale_fill_gradientn(colours=mycol)+
  facet_grid(spp~variable)
```


## Equilibrium dynamics

The parameters are then used by `lhEql` to simulate the equilibrium dynamics by combining the spawner/yield per recruit relationships with a stock recruiment relationship.

```{r, eqRun}
eq=lhEql(par,spwn=0)
```


```{r vectors}
sel<-function(x) 
  catch.sel(x)%/%fapex(catch.sel(x))

dat=FLQuants(eq,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Mass"=stock.wt)

ggplot(subset(as.data.frame(dat),age<=10))+
  geom_line(aes(age,data,col=dimnames(par)$iter[iter]))+
  facet_wrap(~qname,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")+
  theme(legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`** Vectors.


```{r, eq}
plot(eq,refpts=FALSE)  
```

**Figure `r iFig=iFig+1; iFig`** Equilibrum Curves.

## Population dynamics

```{r om}
#http://www.fishbase.org/manual/Key%20Facts.htm

gTime=aaply(par,2,function(x) round(FLife:::genTime(FLPar(x))))

fbar=as.FLQuant(mdply(data.frame(iter=1:7), function(iter) 
                   data.frame(year=1:105,
                              data=c(rep(.1,19),seq(.1,2,length.out=30),
                                                seq(2.0,1,length.out=gTime[iter])[-1],
                                                rep(1,61))[1:105])))

eq@fbar=fbar%*%refpts(eq)["msy","harvest"]

om=as(eq,"FLStock")
om=fwd(om,f=fbar(om)[,-1],sr=eq)
lh=par
save(lh,eq,om,file=file.path(dirDat,"om7.RData"),compress="xz")

plot(om)
```

**Figure `r iFig=iFig+1; iFig`** Time series.

```{r ts}
plot(FLQuants(om, 
          "ssb" = function(x) ssb(x)%/%refpts( eq)["msy","ssb"], 
          "f" =   function(x) fbar(x)%/%refpts(eq)["msy","harvest"], 
          "rec" = function(x) rec(x)%/%refpts( eq)["msy","rec"], 
          "catch"=function(x) landings(x)%/%refpts(eq)["msy","yield"])) + 
  geom_hline(aes(yintercept=1),col="red") 
```

**Figure `r iFig=iFig+1; iFig`** Time series relative to MSY benchmarks.

```{r}
library(doParallel)
library(foreach)

registerDoParallel(2)

library(mydas)

mseStart=            c("brill"=54,"turbot"=54,"ray"=60,"pollack"=56,"sprat"=52,
                       "razor"=54,"lobster"=57)
scen=expand.grid(spp=c("brill",   "turbot",   "ray",   "pollack",   "sprat",   
                       "razor",   "lobster"),
                 stringsAsFactors=FALSE)

### Stochasticity
set.seed(12345)
nits=500

srDev=FLife:::rlnoise(nits,FLQuant(0,dimnames=list(year=1:105)),0.2,b=0.0)
uDev =FLife:::rlnoise(nits,FLQuant(0,dimnames=list(year=1:105)),0.3,b=0.0)

control=rbind(FLPar(k1   =runif(nits, 0.0, 1.0)),
              FLPar(k2   =runif(nits, 0.0, 1.0)),
              FLPar(gamma=runif(nits, 1, 1)))

empD=NULL
empD<-foreach(i=(seq(dim(scen)[1])), 
             .combine=rbind,
             .multicombine=TRUE,
             .packages=c("plyr","dplyr","reshape","ggplot2","FLCore","ggplotFL",
                         "FLasher","FLBRP","FLife")) %dopar%{

  om.=propagate(FLCore:::iter(om,i),nits)
  eq.=propagate(FLCore:::iter(eq,i),nits)
  lh.=propagate(FLCore:::iter(lh,i),nits)
  
  mse=mseSBTD(om.,eq.,
              control=control,
              srDev=srDev,uDev=uDev,
              start  =mseStart[scen[i,"spp"]]+5,end=mseStart[scen[i,"spp"]]+45,nyrs=5)
  res=cbind(spp=scen[i,"spp"],omSmry(mse,eq.,lh.))
  
  save(res,file=file.path(dirRes,paste("omd-2-",i,".RData",sep="")))
  
  res}

empD.=empD
empD$spp =ac(empD$spp)
empD     =subset(empD,year>=mseStart[empD$spp]&year<=mseStart[empD$spp]+45)
empD$year=empD$year-mseStart[empD$spp]

empd_pm=ddply(empD,.(spp,iter), smryStat)

save(empD,empd_pm,control,file=file.path(dirRes,"omd-results-2.RData"))
```

\newpage
## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLasher:   `r packageVersion('FLasher')`
* FLife:     `r packageVersion('FLife')`
* ggplotFL:  `r packageVersion('ggplotFL')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
```

